### 2014-09-11 A1/writeup/writeup.tex
added writeup stuff

\documentclass[10pt]{article}

% amsmath package, useful for mathematical formulas
\usepackage{amsmath}
% amssymb package, useful for mathematical symbols
\usepackage{amssymb}

% graphicx package, useful for including eps and pdf graphics
% include graphics with the command \includegraphics
\usepackage{graphicx}

% cite package, to clean up citations in the main text. Do not remove.
\usepackage{cite}

\usepackage{color}

% Use doublespacing - comment out for single spacing
%\usepackage{setspace} 
%\doublespacing

% Text layout
\topmargin 0.0cm
\oddsidemargin 0.5cm
\evensidemargin 0.5cm
\textwidth 16cm 
\textheight 21cm

% Bold the 'Figure #' in the caption and separate it with a period
% Captions will be left justified
\usepackage[labelfont=bf,labelsep=period,justification=raggedright]{caption}

\bibliographystyle{abbrv}

% Remove brackets from numbering in List of References
\makeatletter
\renewcommand{\@biblabel}[1]{\quad#1.}
\makeatother

% Leave date blank
\date{}

\pagestyle{myheadings}

\begin{document}

% Title must be 150 characters or less
\begin{flushleft}
{\Large
\textbf{The Effect of Uniqueness on Review Helpfulness}
}
% Insert Author names, affiliations and corresponding author email.
\\
Jack Hessel, 
Matthew Milano, 
Maithra Raghu
\end{flushleft}

\section*{Introduction}
Testing this citation \cite{gilbert2010understanding}.

\section*{Data and Methods}

\section*{Reults}

\bibliography{refs}

\end{document}

### 2014-09-11 A1/writeup/writeup.tex
worked on the writeup

@@
 \section*{Introduction}
-Testing this citation \cite{gilbert2010understanding}.
+What types of information are helpful to communities?
+The answer to this question undoubtedly depends on community type, size, and structure.
+Gilbert and Karahlios address this question in the Amazon review setting \cite{gilbert2010understanding} in the context of repetitive reviews.
+According to the authors, \emph{deja reviews} constitute ``missed oppertunities'' because, when a user posts a review with little to no new content, ``the community [gains] little it did not already know.'' Their study includes interviews with amateur and experienced reviewers, and their findings indicate that, while amateur reviewers don't see the merit of a unique review, experienced reviewers take some personal pride in producing ``original'' content.
+They conclude with the sugguestion that review sites should encourage amateur reviewers to produce unique content by ``[asking] for particular pieces of information.''
+
+While it is clear that there is more unique information about the product contained in unique reviews, it is not obvious that unique reviews are truly more helpful and contribute more to review communities.
+For instance, it's plausable that a user, concerned with a primary feature of a product, would find an additional review echoing previous sentiments about that particular feature more helpful than a review about a secondary product feature she isn't interested in.
+Perhaps deja reviews, taken as a whole, are more helpful than reviews with unique content.
+This idea motivated our research question, ``are unique reviews \emph{actually} considered more helpful?''
+
+Questions about how uniquness relates to helpfulness have been addressed previously.
+For instance, Danescu-Niculescu-Mizil et al.
+find that reviews that give star ratings closer to the mean rating for the product are more likely to recieve ``helpful'' votes on Amazon \cite{danescu2009opinions}.
+In their most successful model, Soo-Min et al.
+\cite{kim2006automatically} use a set of unigram tfidf features in an SVM regression to predict Amazon review helpfulness, indicating that lexical features do have an effect on helpfulness voting (though they do not report whether or not uniqueness had a positive or negative effect on helpfulness).
 
 \section*{Data and Methods}
+For our analysis, we use a dataset consisting of 500k Amazon ``fine foods'' reviews taken from 2002 to 2012 \cite{mcauley2013amateurs}.
 
-\section*{Reults}
+\section*{Results}
+
+\section*{Conclusions}
+
+Notably, Mudambi et al.
+find that what makes a review helpful depends strongly on whether the product in question can be classified as a experience good, which cannot be truly evaluated until a consumer has \emph{experienced} it, or search good, which a customer can make most evaluations about prior to purchase \cite{mudambi2010makes}.
+Because our dataset consisted of the fine foods section of Amazon, most of the products in our dataset constitute experience goods.
+Consequently, our preliminary results might not extend to datasets that have a higher proportions of search goods.
 

### 2014-09-11 A1/writeup/writeup.tex
worked on the writeup a bit

@@
 For our analysis, we use a dataset consisting of 500k Amazon ``fine foods'' reviews taken from 2002 to 2012 \cite{mcauley2013amateurs}.
+The information of interest contained in a given review includes the product ID to which it corresponds, the number of helpful/unhelpful votes it has recieved, and the text of that review.
+We restrict our consideration to 300 reviews in our dataset with the most total helpful votes, summed over all reviews of that product.
 
+For each review, we remove all punctuation, captialization, and run each resulting token through a Porter stemmer.
+Next, we create a vector space representation of a review using unigram tfidf features, where idf is computed with respect to a given product, rather than the whole dataset.
+This interpretation treats a given products' reviews as a corpus.
+Stemmed tokens that appear less than (PUT SOMETHING HERE) times or in more than (PUT SOMETHING HERE) percent of the reviews for a given product are discarded.
+
+Next, the high-dimensional sparse per-document vectors are projected to an optimal linear subspace of (PUT PCA DIM HERE) dimensions using PCA.
+After the dimensionality reduction step, reviews are clustered using a modified k-means clustering algorithm.
+Because many clustering methods, including k-means, are highly sensitive to outliers (for instance, the k-means objective utilizes an $L_2$ norm, so points far from cluster centers are very influential) and our goal is to use clustering for outlier detection, we implemented a slightly modified version of k-means, \emph{constrained k-means}, that enforces a minimal number of points in each cluster.
+
+(MAYBE INPUT PICTURES ABOUT WHY CONSTRAINED K-MEANS IS REQUIRED?)
+
+Given $k$, the number of desired clusters, and $0 < p < \frac{n}{100k}$, the minimum proportion of the data that must be in each cluster, constrained k-means returns a reasonable clustering of the data that satisfies these parameters.
+To ensure that clusters are ``big enough,'' the method begins by running normal k-means, and checking cluster size.
+If the data is spread properly with respect to $p$, that clustering is returned.
+Otherwise, (k+1)-means is executed, and the two clusters with the closest centers are merged to produce k-means.
+If the (k+1)-means + 1 merge fails as well, (k+2)-means + 2 merges is executed, and so on.
+In this way, constrained k means consists of two steps: a flat clustering step, and a hirearchical clustering step.
+
+After executing constrained k-means, we assign a ``uniqueness'' score to each clustered review by finding the distance between its vector representation and the closest cluster center.
+Ideally, the clustering process allows for up to (NUM CLUSTERS) ``prototypial'' review types to not be considered unique.
+If a review is far from each of the cluster centers, it is assigned a high uniqueness score.
+
+Finally, for a given product, we run a logistic regression of uniquness on a new binary value ``helpfulness.'' We say a review is helpful if it has at least one helpful vote and more than $60\%$ of its helpful votes are positive.
+We are interested, in particular, in the resulting logistic regression coefficient on helpfulness.
+If this coefficient is generally positive over all products in our dataset, we conclude that uniqueness positively influences helpfulness.
+Conversely, if this coefficient is generally negative, uniqueness is a negative predictor of helpfulness.
 \section*{Results}
@@
 \section*{Conclusions}
+(DISCUSSION ABOUT RESULTS)
 
@@
 Because our dataset consisted of the fine foods section of Amazon, most of the products in our dataset constitute experience goods.
-Consequently, our preliminary results might not extend to datasets that have a higher proportions of search goods.
+Consequently, our preliminary results might not extend to datasets that have higher proportions of search goods.
+
+Finally, we recognize that our metric of uniqueness could be improved upon.
+For instance, it would be interesting to include bigram features in our vector space review representation.
+Also, our consideration is limited to extremely simple lexical review features only.
+A more complete analysis, for instance, might include a subset of the dozens of more complex potential review features used by Ghose and Ipeirotis \cite{ghose2011estimating}.
+Our analysis also doesn't control for reviewer characteristics, which, given the complex social structure potentially underlying review sites like Amazon, is a potential avenue for future exploration.
 

### 2014-09-11 A1/writeup/writeup.tex
small change

@@
 Also, our consideration is limited to extremely simple lexical review features only.
-A more complete analysis, for instance, might include a subset of the dozens of more complex potential review features used by Ghose and Ipeirotis \cite{ghose2011estimating}.
+A more complete analysis might include a subset of the dozens of more complex potential review features used by Ghose and Ipeirotis \cite{ghose2011estimating}.
 Our analysis also doesn't control for reviewer characteristics, which, given the complex social structure potentially underlying review sites like Amazon, is a potential avenue for future exploration.

### 2014-09-11 A1/reviews.py
updated reviews.py

@@ -125,7 +125,16 @@ def tokenize(myString, stemmer=None):
     if stemmer != None:
         myString = ' '.join([stemmer.stem(word) for word in myString.split(" ")])
     myString = re.sub(' +', ' ', myString)
-    return myString.split(' ')
+    curTokens = myString.split(' ')
+    returnTokens = []
+    for t in curTokens:
+        try:
+            float(t)
+            returnTokens.append("####")
+        except ValueError:
+            returnTokens.append(t)
+
+    return returnTokens
 
 
 def getTfidfMatrix(reviewList,
@@ -137,14 +146,14 @@ def getTfidfMatrix(reviewList,
     if stemObject is not None:
         tokenizeMethod = lambda s: tokenize(s, stemObject)
 
-    tfidfer = TfidfVectorizer(tokenizer = tokenizeMethod,
+    tfidfer = TfidfVectorizer(tokenizer = tokenizeMethod, max_df=.8, min_df = 3,
                                   stop_words = 'english',
                                   dtype = np.float32, decode_error = 'ignore')
     documentList = [r.text for r in reviewList]
     tfidfMatrix = tfidfer.fit_transform(documentList).toarray()
     if dimReduceObject is not None:
         tfidfMatrix = dimReduceObject.fit_transform(tfidfMatrix)
-    return tfidfMatrix
+    return tfidfMatrix, tfidfer
 
 def constrainedKMeans(numClusters, data, minPercent = .1):
     '''Given the number of clusters you want, and the minimum proportion of the data that is allowed to be in a single cluster, returns the cluster centers, assignments for each datapoint, and the distance of each point to each center.'''
@@ -249,12 +258,32 @@ def main():
         productIdFile.write(popItem + '\n')
         outFile = open("temp/" + str(itemCounter) + '.csv' , 'w')
 
-        tfidfMatrix = getTfidfMatrix(reviews[popItem], tokenizeMethod = tokenize,
-                                     stemObject = PorterStemmer(),
+        tfidfMatrix, tfidfObject = getTfidfMatrix(reviews[popItem], tokenizeMethod = tokenize,
+                                     stemObject = None,
                                      dimReduceObject = PCA(n_components=200))
 
-        centers, predictions, distances = constrainedKMeans(5, tfidfMatrix, minPercent=.05)
-        
+
+        rawtfidf = tfidfMatrix.copy()
+        centers, predictions, distances = constrainedKMeans(10, tfidfMatrix, minPercent=.03)
+        words = tfidfObject.get_feature_names()
[…]

### 2014-09-12 A1/writeup/writeup.tex
did more writing

@@
 Gilbert and Karahlios address this question in the Amazon review setting \cite{gilbert2010understanding} in the context of repetitive reviews.
-According to the authors, \emph{deja reviews} constitute ``missed oppertunities'' because, when a user posts a review with little to no new content, ``the community [gains] little it did not already know.'' Their study includes interviews with amateur and experienced reviewers, and their findings indicate that, while amateur reviewers don't see the merit of a unique review, experienced reviewers take some personal pride in producing ``original'' content.
-They conclude with the sugguestion that review sites should encourage amateur reviewers to produce unique content by ``[asking] for particular pieces of information.''
+According to the authors, \emph{deja reviews} constitute ``missed opportunities'' because, when a user posts a review with little to no new content, ``the community [gains] little it did not already know.'' Their study includes interviews with amateur and experienced reviewers, and their findings indicate that, while amateur reviewers don't see the merit of a unique review, experienced reviewers take some personal pride in producing ``original'' content.
+They conclude with the suggestion that review sites should encourage amateur reviewers to produce unique content by ``[asking] for particular pieces of information.''
 
 While it is clear that there is more unique information about the product contained in unique reviews, it is not obvious that unique reviews are truly more helpful and contribute more to review communities.
-For instance, it's plausable that a user, concerned with a primary feature of a product, would find an additional review echoing previous sentiments about that particular feature more helpful than a review about a secondary product feature she isn't interested in.
+For instance, it's plausible that a user, concerned with a primary feature of a product, would find an additional review echoing previous sentiments about that particular feature more helpful than a review about a secondary product feature she isn't interested in.
 Perhaps deja reviews, taken as a whole, are more helpful than reviews with unique content.
@@
 
-Questions about how uniquness relates to helpfulness have been addressed previously.
+Questions about how uniqueness relates to helpfulness have been addressed previously.
 For instance, Danescu-Niculescu-Mizil et al.
-find that reviews that give star ratings closer to the mean rating for the product are more likely to recieve ``helpful'' votes on Amazon \cite{danescu2009opinions}.
+find that reviews that give star ratings closer to the mean rating for the product are more likely to receive ``helpful'' votes on Amazon \cite{danescu2009opinions}.
 In their most successful model, Soo-Min et al.
@@
 For our analysis, we use a dataset consisting of 500k Amazon ``fine foods'' reviews taken from 2002 to 2012 \cite{mcauley2013amateurs}.
-The information of interest contained in a given review includes the product ID to which it corresponds, the number of helpful/unhelpful votes it has recieved, and the text of that review.
+The information of interest contained in a given review includes the product ID to which it corresponds, the number of helpful/unhelpful votes it has received, and the text of that review.
 We restrict our consideration to 300 reviews in our dataset with the most total helpful votes, summed over all reviews of that product.
 
-For each review, we remove all punctuation, captialization, and run each resulting token through a Porter stemmer.
+For each review, we remove all punctuation, capitalization, and map all numbers to a single token.
 Next, we create a vector space representation of a review using unigram tfidf features, where idf is computed with respect to a given product, rather than the whole dataset.
 This interpretation treats a given products' reviews as a corpus.
-Stemmed tokens that appear less than (PUT SOMETHING HERE) times or in more than (PUT SOMETHING HERE) percent of the reviews for a given product are discarded.
+Stemmed tokens that appear less than 2 reviews or in more than 80 percent of the reviews for a given product are discarded.
 
-Next, the high-dimensional sparse per-document vectors are projected to an optimal linear subspace of (PUT PCA DIM HERE) dimensions using PCA.
+Next, the high-dimensional sparse per-document vectors are projected to an optimal linear subspace of 100 dimensions using PCA.
 After the dimensionality reduction step, reviews are clustered using a modified k-means clustering algorithm.
-Because many clustering methods, including k-means, are highly sensitive to outliers (for instance, the k-means objective utilizes an $L_2$ norm, so points far from cluster centers are very influential) and our goal is to use clustering for outlier detection, we implemented a slightly modified version of k-means, \emph{constrained k-means}, that enforces a minimal number of points in each cluster.
-
-(MAYBE INPUT PICTURES ABOUT WHY CONSTRAINED K-MEANS IS REQUIRED?)
+Because many clustering methods, including k-means, are highly sensitive to outliers (for instance, the k-means objective utilizes an $L_2$ norm, so points far from cluster centers are very influential) and our goal is to use clustering for outlier detection, we implemented a slightly modified version of k-means, \emph{constrained k-means}, that enforces a minimal number of points in each cluster
 
@@
 If the (k+1)-means + 1 merge fails as well, (k+2)-means + 2 merges is executed, and so on.
-In this way, constrained k means consists of two steps: a flat clustering step, and a hirearchical clustering step.
+In this way, constrained k means consists of two steps: a flat clustering step, and a hierarchical clustering step.
 
 After executing constrained k-means, we assign a ``uniqueness'' score to each clustered review by finding the distance between its vector representation and the closest cluster center.
-Ideally, the clustering process allows for up to (NUM CLUSTERS) ``prototypial'' review types to not be considered unique.
+Because we choose $k$ to be 10, the clustering process allows for 10 ``prototypical'' review types.
 If a review is far from each of the cluster centers, it is assigned a high uniqueness score.
 
-Finally, for a given product, we run a logistic regression of uniquness on a new binary value ``helpfulness.'' We say a review is helpful if it has at least one helpful vote and more than $60\%$ of its helpful votes are positive.
+Finally, for a given product, we run a logistic regression of uniqueness on a new binary value ``helpfulness.'' We say a review is helpful if it has at least one helpful vote and more than $60\%$ of its helpful votes are positive.
 We are interested, in particular, in the resulting logistic regression coefficient on helpfulness.
@@
 Conversely, if this coefficient is generally negative, uniqueness is a negative predictor of helpfulness.
+
 \section*{Results}
+An interesting question to ask is how well our clustering scheme produces prototypical reviews, and what those reviews look like.
+Unfortunately, it is difficult to directly derive meaning from cluster centers, as the PCA projection to 100 dimensions removes feature meaning from the new vector space.
+However, it is possible to examine points assigned to each cluster and to determine words with high tfidf scores among those documents.
+For every review, we computed the top ten words associated with each cluster.
+For products with generally positive reviews, there were few apparent differences between clusters (see Table \ref{tab:clusterex}).
+However, it's possible that there are underlying patterns within this clustering not immediately obvious to a human reader; the ten prototypical reviews, while likely all positive, might highlight different aspects of the product.
+
+\begin{table}[h]
+\centering
+\begin{tabular}{lllll}
+Cluster 0 & Cluster 1 & Cluster 2 & ... & Cluster 9   \\
+coconut   & coconut   & (NUM)     &     & coconut     \\
+great     & cooking   & br        &     & dry         \\
+hair      & great     & coconut   &     & good        \\
+love      & oil       & face      &     & hair        \\
+oil       & price     & hair      &     & moisturizer \\
+skin      & product   & im        &     & oil         \\
+smells    & skin      & ive       &     & product     \\
+stuff     & taste     & oil       &     & really      \\
+use       & use       & skin      &     & skin        \\
+wonderful & uses      & use       &     & use           
+\end{tabular}
+\caption{Prototypical words for the clustering of ``Nature's Way Coconut Oil.'' It's unclear that they are any differences between clusters. The product has an average rating of 4.7/5 stars.}
+\label{tab:clusterex}
+\end{table}
+
+On the other hand, for products with mixed reviews, it's clear that our clustering method detected at least some customer sentiment.
+For instance, cluster 2 and cluster 9 in Table \ref{tab:clusterex2} clearly illustrate our method's capacity to identify prototypical reviews with different sentiments.
+
+\begin{table}[h]
+\centering
+\begin{tabular}{lllll}
+Cluster 0 & Cluster 1 & Cluster 2 & ... & Cluster 9 \\
+(NUM)     & (NUM)     & arent     &     & good      \\
+br        & just      & bad       &     & great     \\
+calories  & like      & fettucini &     & like      \\
+cook      & maybe     & flavor    &     & love      \\
+cooked    & miracle   & like      &     & noodles   \\
+minutes   & noodles   & noodles   &     & pasta     \\
+noodles   & product   & really    &     & product   \\
+rinse     & texture   & rubbery   &     & really    \\
+sauce     & tried     & texture   &     & taste     \\
+water     & try       & wasnt     &     & (NUM)    
+\end{tabular}
+\caption{Prototypical words for the clustering of ``Miracle Noodle Shirataki Angel Hair Pasta,'' a gluten free, diet pasta.
+It's clear that there are any differences between clusters.
+The product has an average rating of 3.6/5 stars.}
+\label{tab:clusterex2}
+\end{table}
+
+Figure \ref{fig:result} contains our primary findings.
+After analyzing the coefficient on uniqueness for each of the 300 product-level logistic regressions, we find that the average coefficient on uniqueness to be $-1.43$ ($p < 10^{-15}$).
+This is an indication that, based on our uniqueness and helpfulness metrics, lexical uniqueness has a negative influence on helpful voting.
+
+\begin{figure}[h!]
+  \centering
+  \includegraphics[width=0.8\textwidth]{influence.png}
+  \caption{Document by uniqueness coefficient plot.
+For each of the top 300 documents, a logistic regression was executed, and the resulting coefficient with 95\% confidence intervals are demonstrated here.
+The red solid line indicates the mean coefficient, while the dotted red lines indicate 95\% confidence intervals on that value.}
+  \label{fig:result}
+\end{figure}
+
+(WE SHOULD RUN REGRESSIONS WITH DEVIANCE FROM AVERAGE REVIEW SCORE -AND- UNIQUENESS AS PREDICTORS FOR REVIEW HELPFULNESS.
+IF SOMEONE WANTED TO ADD THIS AND MAYBE ANOTHER GRAPH, THAT WOULD BE REALLY GREAT.
+ESSENTIALLY, RUN A REGRESSION WITH BOTH HELPFULNESS -AND- REVIEW DEVIANCE FROM MEAN REVIEW SCORE.
+THIS WILL INVOLVE CHANGING THE OUTPUT OF THE PYTHON SCRIPT VERY SLIGHTLY, SO THAT THIS DATA IS WRITTEN PROPERLY INTO THE OUTPUT CSVs.)
 
 \section*{Conclusions}
-(DISCUSSION ABOUT RESULTS)
+Potentially in contrast to assumptions made by previous authors, we find that uniqueness is a negative predictor of review helpfulness.
+Though our methods are basic and could most definitely be improved upon, this preliminary result indicates that it is debatable as to whether or not unique reviews are truly more helpful to a community.
+We believe that the amount of useful information gained by repeating the same important idea again and again might outweigh the benefit of elaboration on secondary product features.
+We suspect this pattern emerges due to product simplicity.
+For instance, how many unique features of coconut oil require elaboration?
 

### 2014-09-12 A1/reviews.py
updated reviews

@@ -152,8 +152,10 @@ def getTfidfMatrix(reviewList,
     documentList = [r.text for r in reviewList]
     tfidfMatrix = tfidfer.fit_transform(documentList).toarray()
     if dimReduceObject is not None:
-        tfidfMatrix = dimReduceObject.fit_transform(tfidfMatrix)
-    return tfidfMatrix, tfidfer
+        tfidfMatrixCompressed = dimReduceObject.fit_transform(tfidfMatrix)
+    else:
+        tfidfMatrixCompressed = tfidfMatrix
+    return tfidfMatrixCompressed, tfidfMatrix, tfidfer
 
 def constrainedKMeans(numClusters, data, minPercent = .1):
     '''Given the number of clusters you want, and the minimum proportion of the data that is allowed to be in a single cluster, returns the cluster centers, assignments for each datapoint, and the distance of each point to each center.'''
@@ -247,7 +249,7 @@ def main():
     removeTextTimeDuplicates(reviews)
     
     n = 500 #number of top reviews to consider
-    helpratio = .5 #threshold required before considered "helpful"
+    helpratio = .6 #threshold required before considered "helpful"
 
     #Getting the top n most reviewed items...
     #get the item with the most "helpful" reviews
@@ -257,14 +259,15 @@ def main():
     for popItem in mostReviewed:
         productIdFile.write(popItem + '\n')
         outFile = open("temp/" + str(itemCounter) + '.csv' , 'w')
+        outFileTypicalWords = open("temp/" + str(itemCounter) + '.txt' , 'w')
 
-        tfidfMatrix, tfidfObject = getTfidfMatrix(reviews[popItem], tokenizeMethod = tokenize,
-                                     stemObject = None,
-                                     dimReduceObject = PCA(n_components=200))
+        compressed, rawtfidf, tfidfObject = getTfidfMatrix(reviews[popItem],
+                                                           tokenizeMethod = tokenize,
+                                                           stemObject = None,
+                                                           dimReduceObject = PCA(n_components=100))
 
 
-        rawtfidf = tfidfMatrix.copy()
-        centers, predictions, distances = constrainedKMeans(10, tfidfMatrix, minPercent=.03)
+        centers, predictions, distances = constrainedKMeans(10, compressed, minPercent=.03)
         words = tfidfObject.get_feature_names()
         #print words with highest average tfidf per cluster
         for i in range(10):
@@ -276,13 +279,10 @@ def main():
             for j in range(numTop):
[…]

### 2014-09-12 A1/writeup/writeup.tex
Updated things

@@
 Figure \ref{fig:result} contains our primary findings.
-After analyzing the coefficient on uniqueness for each of the 300 product-level logistic regressions, we find that the average coefficient on uniqueness to be $-1.43$ ($p < 10^{-15}$).
+After analyzing the coefficient on uniqueness for each of the 300 product-level logistic regressions, we find that the average coefficient on uniqueness to be $-1.52$ ($p < 10^{-15}$).
 This is an indication that, based on our uniqueness and helpfulness metrics, lexical uniqueness has a negative influence on helpful voting.
@@
 
-(WE SHOULD RUN REGRESSIONS WITH DEVIANCE FROM AVERAGE REVIEW SCORE -AND- UNIQUENESS AS PREDICTORS FOR REVIEW HELPFULNESS.
-IF SOMEONE WANTED TO ADD THIS AND MAYBE ANOTHER GRAPH, THAT WOULD BE REALLY GREAT.
-ESSENTIALLY, RUN A REGRESSION WITH BOTH HELPFULNESS -AND- REVIEW DEVIANCE FROM MEAN REVIEW SCORE.
-THIS WILL INVOLVE CHANGING THE OUTPUT OF THE PYTHON SCRIPT VERY SLIGHTLY, SO THAT THIS DATA IS WRITTEN PROPERLY INTO THE OUTPUT CSVs.)
+(PARAGRAPH ABOUT SENTIMENT/SCORING) $-1.50$ ($p < 10^{-15}$)
 

### 2014-09-12 A1/writeup/writeup.tex
hi
edited write up

@@
 
+\subsection{Rating differences and Uniqueness}
+
+The results so far indicate that uniqueness is perceived as not being helpful.
+One important factor for this might be that reviews that are more textually unique according to our analysis also rate the product differently from the majority of reviews.
+The lower score of helpfulness could then be readers disagreeing with the product rating, instead of the textual content of the review.
+
+We therefore reattempted logistic regression but with compensation for rating difference by subtracting the average rating of the product from the rating of the review that was being analysed.
+With this, the average coefficient did increase - becoming $-1.50$, but only very marginally.
+(The original value was $-1.52$.) This suggests that textual content perceived as different is still unhelpful to reviewers.
+
 (PARAGRAPH ABOUT SENTIMENT/SCORING) $-1.50$ ($p < 10^{-15}$)

### 2014-10-29 AltruisticLanguage/EDA.py
more work

@@ -1,11 +1,30 @@
 import cPickle as pickle
 from KickstarterParser import *
 import random
+import numpy as np
+import matplotlib.pyplot as plt
+import string
 
-def loadProjects(folderName, numFiles = None):
+class _GetchUnix:
+    def __init__(self):
+        import tty, sys
+
+    def __call__(self):
+        import sys, tty, termios
+        fd = sys.stdin.fileno()
+        old_settings = termios.tcgetattr(fd)
+        try:
+            tty.setraw(sys.stdin.fileno())
+            ch = sys.stdin.read(1)
+        finally:
+            termios.tcsetattr(fd, termios.TCSADRAIN, old_settings)
+        return ch
+getch = _GetchUnix()
+
+def loadProjects(folderName, fileRange = None):
     '''Given the name of the folder where the pickled project files are, return a list of the projects contained in those pickled files. Furthermore, if numFiles is not None, return the list containing data from only that number of files.'''
     validFiles = [x for x in os.listdir(folderName) if re.search("^\d+\.pickle$", x) is not None]
-    if numFiles is not None: validFiles = validFiles[:numFiles]
+    if fileRange is not None: validFiles = validFiles[fileRange[0]:fileRange[1]]
     projects = []
     for v in validFiles:
         fileName = folderName + "/" + v
@@ -15,14 +34,119 @@ def loadProjects(folderName, numFiles = None):
     
     return projects
 
-def main():
-    projects = loadProjects('output', numFiles = 1)
-    random.shuffle(projects)
+def getProjectsOfCategory(category, allProjects):
+    returnList = []
+    for p in allProjects:
+        if p.category == category:
+            returnList.append(p)
+
+    return returnList
+
+def getCategories(projects):
+    return set([x.category for x in projects])
+
+
+def printGroupStatistics(projects):
+    cats = getCategories(projects)
+    
+    print '{:>18}  {:>18}  {:>18}  {:>18}'.format("Category",
+                                                  "Num Projects",
+                                                  "Succ Ratio",
+                                                  "Ave Raised")
+    for c in cats:
+        if c is '': continue
+        catProjects = getProjectsOfCategory(c, projects)
+        succRatio = sum([1 for p in catProjects if p.result == 1])*1./len(catProjects)
+        aveRaised = sum([p.raised for p in catProjects])*1./len(catProjects)
[…]

### 2014-10-29 AltruisticLanguage/writing/paper.tex
removed junk

\def\year{2015}
%File: formatting-instruction.tex
\documentclass[letterpaper]{article}
\usepackage{aaai}
\usepackage{times}
\usepackage{helvet}
\usepackage{courier}
\frenchspacing
\setlength{\pdfpagewidth}{8.5in}
\setlength{\pdfpageheight}{11in}
\pdfinfo{
/Title Kickstarter Stuff
/Author Jack Hessel, Lillian Lee
/Keywords X,Y,Z}
\setcounter{secnumdepth}{0}  
 \begin{document}
% The file aaai.sty is the style file for AAAI Press 
% proceedings, working notes, and technical reports.
%
\title{Kickstarter Stuff}
\author{AAAI Press\\
Association for the Advancement of Artificial Intelligence\\
2275 East Bayshore Road, Suite 160\\
Palo Alto, California 94303\\
}
\maketitle
\begin{abstract}
\begin{quote}
ABS
\end{quote}
\end{abstract}

\noindent Blah

\section{Copyright}
Here's this. Thank you for reading these instructions carefully. We look forward to receiving your electronic files! \cite{rumelhart1988learning}.

\bibliographystyle{aaai} \bibliography{refs}

\end{document}

### 2014-10-29 AltruisticLanguage/EDA.py
more EDA

@@ -4,6 +4,8 @@ import random
 import numpy as np
 import matplotlib.pyplot as plt
 import string
+from collections import defaultdict
+from scipy.stats import chi2_contingency
 
 class _GetchUnix:
     def __init__(self):
@@ -134,8 +136,8 @@ def basicPlots(projects):
     plt.hist(sorted(prices)[10:-50], bins = 20)
     plt.savefig("prices.png")
 
-def main():
-    projects = loadProjects('output', fileRange = (4,14))
+def labelThings(projects):
+    '''Given a list of projects, have the user label items.'''
     vgs = [x for x in projects if x.category.lower()
            in ["technology","open hardware","board & card games","product design"]]
     toLabel = []
@@ -147,6 +149,61 @@ def main():
             toLabel.append(sortedRewards[1])
     
     rewardLabel(toLabel, "posTechOHBoardProd","negTechOHBoardProd", tokenFile = "tokTechOHBoardProd")
+
+def buildCategoryDictionary(projects):
+    '''Given a list of projects, builds a dictionary that maps from {category -> [p1, p2, p3]} for all projects in the input.'''
+    x = defaultdict(list)
+    for p in projects: x[p.category].append(p)
+    return x
+
+def categoryAltruisticPropTest(projects):
+    '''Given a list of projects, split on category. Then, conduct a proportion test for for each category for proportion of altruistic donations vs not altruistic donations split on success/failure.'''
+    catDict = buildCategoryDictionary(projects)
+    for cat, projectList in catDict.iteritems():
+        if len(cat) == 0: continue
+        success = [x for x in projectList if x.result and x.backers != 0]
+        fail = [x for x in projectList if not x.result and x.backers != 0]
+        sucAlt = sum([x.backers - sum([y.numBackers for y in x.rewards]) for x in success])
+        failAlt = sum([x.backers - sum([y.numBackers for y in x.rewards]) for x in fail])
+        sucTotal = sum([x.backers for x in success])
+        failTotal = sum([x.backers for x in fail])
+
+        chi2, p, dof, ex = chi2_contingency([[sucAlt, failAlt],[sucTotal-sucAlt, failTotal-failAlt]])
+
+        propSuc, propFail = float(sucAlt*1./sucTotal), float(failAlt*1./failTotal)
+        print cat, propSuc, propFail, p
+
+        if propSuc > propFail: print "Greater proportion with successful projects"
+        else: print "Greater proportion with failed projects"
+
[…]

### 2014-10-31 AltruisticLanguage/EDA.py
more work

@@ -4,8 +4,11 @@ import random
 import numpy as np
 import matplotlib.pyplot as plt
 import string
-from collections import defaultdict
+from collections import defaultdict, Counter
 from scipy.stats import chi2_contingency
+from nltk.corpus import stopwords
+import string
+from sklearn.linear_model import LogisticRegression
 
 class _GetchUnix:
     def __init__(self):
@@ -23,10 +26,10 @@ class _GetchUnix:
         return ch
 getch = _GetchUnix()
 
-def loadProjects(folderName, fileRange = None):
+def loadProjects(folderName, numFiles = None):
     '''Given the name of the folder where the pickled project files are, return a list of the projects contained in those pickled files. Furthermore, if numFiles is not None, return the list containing data from only that number of files.'''
     validFiles = [x for x in os.listdir(folderName) if re.search("^\d+\.pickle$", x) is not None]
-    if fileRange is not None: validFiles = validFiles[fileRange[0]:fileRange[1]]
+    if numFiles is not None: validFiles = validFiles[:numFiles]
     projects = []
     for v in validFiles:
         fileName = folderName + "/" + v
@@ -159,6 +162,11 @@ def buildCategoryDictionary(projects):
 def categoryAltruisticPropTest(projects):
     '''Given a list of projects, split on category. Then, conduct a proportion test for for each category for proportion of altruistic donations vs not altruistic donations split on success/failure.'''
     catDict = buildCategoryDictionary(projects)
+    
+    print '{:>18}  {:>18}  {:>18}  {:>18}'.format("Category",
+                                                  "Alt Ratio Succ",
+                                                  "Alt Ratio Fail",
+                                                  "p-val")
     for cat, projectList in catDict.iteritems():
         if len(cat) == 0: continue
         success = [x for x in projectList if x.result and x.backers != 0]
@@ -171,10 +179,11 @@ def categoryAltruisticPropTest(projects):
         chi2, p, dof, ex = chi2_contingency([[sucAlt, failAlt],[sucTotal-sucAlt, failTotal-failAlt]])
 
         propSuc, propFail = float(sucAlt*1./sucTotal), float(failAlt*1./failTotal)
-        print cat, propSuc, propFail, p
+        
+        print '{:>18}  {:>18.4f}  {:>18.4f}  {:>18.4f}'.format(cat, propSuc, propFail, p)
 
-        if propSuc > propFail: print "Greater proportion with successful projects"
-        else: print "Greater proportion with failed projects"
[…]

### 2014-10-31 AltruisticLanguage/KickstarterParser.py

@@ -26,8 +26,18 @@ class Project:
         self.shortText = ""
         self.text = ""
         self.comments = -1
-        #0 is not funded, 1 is funded
         self.result = -1
+        self.updates = -1
+        #this one needs to start at as F, because if a tag exists, then yes,
+        #if if it doesn't exist, then no. It's easier to just start it at 0.
+        self.creatorFacebookConnect = 0 
+        #same with this one
+        self.featured = 0
+
+        self.creatorNumBacked = -1
+
+        self.hasVideo = -1
+
         self.rewards = []
         self.faqs = []
 
@@ -128,7 +138,8 @@ def getRewardList(soup, project):
 
 def basicSanitize(inString):
     '''Returns a very roughly sanitized version of the input string.'''
-    return ' '.join(inString.encode('ascii', 'ignore').strip().split())
+    returnString = ' '.join(inString.encode('ascii', 'ignore').strip().split())
+    return returnString
 
 def getFaqList(soup, project):
     '''Given an input soup object and a parent object, return the faq list associated
@@ -198,8 +209,6 @@ def fillProjectInfo(soup, project):
                 project.name = basicSanitize(meta.get('content'))
             if 'og:description' in meta.get('property'):
                 project.shortText = basicSanitize(meta.get('content'))
-            else:
-                pass
 
     for div in soup.find_all('div'):
         if div.get('data-backers-count') is not None:
@@ -211,6 +220,11 @@ def fillProjectInfo(soup, project):
         if div.get('class') is not None and 'full-description' in div.get('class'):
             myText = ' '.join(div.findAll(text=True))
             project.text = basicSanitize(myText)
+        if div.get('data-has-video') is not None:
+            project.hasVideo = div.get('data-has-video') == 'true'
+        if div.get('id') is not None and "mentions" in div.get('id'):
+            if "Featured!" in div.text:
+                project.featured = 1
 
     for span in soup.find_all('span'):
         if span.get('data-duration') is not None:
@@ -219,6 +233,12 @@ def fillProjectInfo(soup, project):
             project.comments = int(span.get('data-comments-count').replace(',',''))
         if span.get('data-end_time') is not None:
             project.endDate = parse(span.get('data-end_time')).replace(tzinfo=None)
+        if span.get('data-updates-count') is not None:
+            project.updateCount = int(span.get('data-updates-count'))
[…]

### 2014-10-31 AltruisticLanguage/regression.R

@@ -1,0 +1,7 @@
+setwd("/home/jhessel/Desktop/NLP/git/AltruisticLanguage")
+myData <- read.csv("success.csv")
+install.packages("penalized")
+library(penalized)
+penalized(response = myData$success,
+          penalized = myData[,-match("success", colnames(myData))],
+          lambda2=1.0, model = "logistic")

### 2014-10-31 AltruisticLanguage/test.py

@@ -1,7 +1,0 @@
-import random
-
-myFile = open("kickscrape.sql")
-
-for line in myFile:
-    if random.random() < .00079:
-        print line

### 2014-11-18 AltruisticLanguage/writing/paper.tex
more EDA
udpated writeup

@@
 \usepackage{courier}
+\usepackage{url}
 \frenchspacing
@@
 \pdfinfo{
-/Title Kickstarter Stuff
-/Author Jack Hessel, Lillian Lee
+/Title Pre-orders or Philanthropy: An Analysis of Altruism on Kickstarter
+/Author Jack Hessel
 /Keywords X,Y,Z}
@@
 %
-\title{Kickstarter Stuff}
-\author{AAAI Press\\
-Association for the Advancement of Artificial Intelligence\\
-2275 East Bayshore Road, Suite 160\\
-Palo Alto, California 94303\\
-}
+\title{Pre-orders or Philanthropy: An Analysis of Altruism on Kickstarter}
+\author{Jack Hessel}
 \maketitle
@@
 \begin{quote}
-ABS
+Abstract
 \end{quote}
@@
 
-\noindent Blah
+\section{Introduction}
 
-\section{Copyright}
-Here's this. Thank you for reading these instructions carefully. We look forward to receiving your electronic files! \cite{rumelhart1988learning}.
+In recent years, crowdfunding websites have emerged as a popular method of fundraising for individuals looking to promote their ventures to online communities.
+The most popular of these sites, Kickstarter, provides a venue for entrepreneurs to connect with individuals who might be interested in financially supporting their project ideas, which range from artistic endevours to technology startups.
+To date, over \$1.4B has been invested in Kickstarter projects from more than 7.4M unique backers resulting in over 73K successfully funded projects.
+\footnote{ \url{www.kickstarter.com/help/stats}} Each project is associated with a set of creator-defined rewards that donors can choose from.
+Often, these rewards constitute pre-orders of a product that the project aims to bring to market.
+
+(PARAGRAPH ABOUT ACADEMIC INTEREST WITH CITATIONS)
+
+We argue that crowdfunding sites similar to Kickstarter occupy a unique space between a realm of pure salespersonship and a realm of pure altruism.
+A project that illustrates that Kickstarter is not purely altruistic nor purely commerical is ``Juicies.''\footnote{\url{http://tinyurl.com/juiciesproject}} In this project, the creators successfully attempted to create a company that sells multi-colored charging cables for various mobile devices, and offered cable preorders as rewards.
+The basic cable was associated with two rewards, one costing the suggested retail price of \$20, and the other charging users to ``pay what you can'' for the same cable costing \$1.
+While over 1K pay-what-you-can rewards were claimed, the \$20 reward was claimed 280 times.
+Users voluntarily paying more for an identical product sugguests that Kickstarter is not a community solely focused on commercialism.
+
+Furthermore, in our dataset consisting of 45810 completed Kickstarter projects, we are able to quantify the number of purely altruistic donation events and the total value given above and beyond the amount required for all reward claims.
+When a user backs a project on Kickstarter (which is impossible to do anonymously) they are able to select an option that allows them to claim no rewards.
+Because the total number of claims for each reward are displayed publically on the project page, along with the total number of backers, we are able to compute the total number of purely altruistic donation events for each project.
+Also, the site allows for users to give an amount exceeding the cost of a given reward, so we are able to compute the total amount donated to a project above and beyond the amount required for all the posted reward claims.
+Of the roughly 3.4M donation events, about 360K (10.59\%) resulted from users who selected no reward.
+Of the roughly \$246M pledged in our dataset, over \$53M (21.59\%) was given altruistically.
+
+The community and language of Kickstarter have been studied previously.
+Mitra and Gilbert analyze the language that predicts successful Kickstarter projects \cite{mitra2014language}.
+When compared their baseline regression trained on language-indepedent project features, their final classifier, which includes n-gram counts, is able to classify projects 15\% more accurately, resulting in a 97.8\% correct prediction rate in a 10-fold cross validation setting.
+Similar analyses that do not take language fully into account are not able to achieve such predictive accuracy.
+Studies that use of minimal textual information in conjunction with baseline project features are able to learn classifiers that reach 68\% accuracy using information available at launch time \cite{greenberg2013crowdfunding}.
+Even using post-launch information, however, does not improve accuracy as much as accounting for language; 85\% accuracy is achieved using information available after 15\% of the duration of the campaign has expired \cite{etter2013launch}.
+These findings sugguest that language is very important on Kickstarter, which is a primary motivation for making it a focus of our analysis.
+
+Altruism in online communities has also been studied as well.
+Althoff et al.
+examine a purely altruistic community wherein users request free pizza from other members \cite{althoff2014ask}.
+An advantage of their dataset is that all altruistic requests are made for the same service.
+MORE MORE MORE
+
+These observations and previous work motivate our research questions: how does the language used on Kickstarter differ from the language used in a purely commercial setting?
+Or a purely altruistic setting?
+What types of Kickstarter projects are donated to altruistically?
+Does the language of a project description predict the donation behavior of backers?
+
+\section{Previous Work}
+
+\section{Dataset and Methods}
+
+\section{Kickstarter vs. GoFundMe vs. Amazon}
+What language used on Kickstarter is altruistic?
+What language used on Kickstarter is commercial?
+To address these questions, it might be possible to derive stringent definitions of altruism and salespersonship.
+However, for our analysis, we resort to a more objective analysis by incorporating two additional data sets., one from Amazon and one from GoFundMe.
+Amazon is a very popular  To compare the language used on Kickstarter to purely commercial and purely altrustic
+
+\section{Prediction of Altruism on Kickstarter}
+
+\section{Conclusion}
 

### 2014-11-18 AltruisticLanguage/Comparison/addPrior.py
more updates

@@ -1,0 +1,13 @@
+import sys
+
+def main():
+    '''Command line argument should be [input file] [prior] [output file]'''
+    with open(sys.argv[-1], 'w') as out:
+        with open(sys.argv[1]) as fileIn:
+            writeStr = ""
+            for line in fileIn:
+                writeStr += line.strip() + ":" + sys.argv[2] + "\n"
+            out.write(writeStr[:-1])
+
+if __name__ == "__main__":
+    main()

### 2014-11-18 AltruisticLanguage/Comparison/bayesCompareLanguage.py

@@ -1,0 +1,129 @@
+import numpy as np
+import sys
+import cPickle as pickle
+from collections import Counter
+import sys
+import string
+exclude = set(string.punctuation)
+loadWidth = 30
+
+def setupLoadBar():
+    sys.stdout.write("[%s]" % (" " * loadWidth))
+    sys.stdout.flush()
+    sys.stdout.write("\b" * (loadWidth+1))
+
+def loadNGrams(ngramfile):
+    '''Given the name of an ngram:prior file, return the list of ngrams and the list of priors associated with those ngrams'''
+    ngrams = []
+    priors = []
+    with open(ngramfile) as f:
+        for line in f:
+            if len(line) != 0:
+                tokens = line.split(":")
+                ngram, prior = (tokens[0], float(tokens[1]))
+                ngrams.append(ngram)
+                priors.append(prior)
+
+    return ngrams, np.array(priors, dtype = np.float32)
+
+def getNGrams(stringIn, n):
+    '''Given an input string, an "n" in n-gram, return a list of strings representing those n-grams. Might contain repeats.'''
+    tokens = stringIn.split()
+    returnList = []
+    for i in range(len(tokens)-n+1): returnList.append(' '.join(tokens[i:i+n]))
+    return returnList
+
+
+def extractCounts(textList, ngrams, maxN):
+    '''Given a list of strings, a list of ngrams we care about, and the maximum number of n that we are interested in, return an array of length ngrams containing the counts of each ngram in textList where n <= maxN.'''
+    #dictionary mapping from ngram -> index
+    nGramMap = {}
+    for i in range(len(ngrams)): nGramMap[ngrams[i]] = i
+
+    returnMatrix = np.empty(len(ngrams), dtype = np.float32)
+    #map from {ngram -> count}
+    counter = Counter()
+
+    for n in range(1,maxN+1):
+        print "Extracting " + str(n) + "-grams"
+        setupLoadBar()
+        for i in range(len(textList)):
+            if i != 0 and i%(len(textList)/loadWidth) == 0:
+                sys.stdout.write("-")
+                sys.stdout.flush()
+            nGrams = getNGrams(textList[i], n)
+            counter.update(Counter(nGrams))
+        sys.stdout.write("\n")
+    for curNGram in ngrams:
[…]

### 2014-11-18 AltruisticLanguage/Comparison/nGramMerger.py

@@ -1,0 +1,38 @@
+import sys
+
+def unionNGrams(files):
+    '''Given a list of files, takes the union of the n grams contained in them'''
+    returnSet = set()
+    for fileName in files:
+        curNGrams = []
+        with open(fileName) as f:
+            for line in f:
+                if len(line) != 0:
+                    curNGrams.append(line.strip())
+        returnSet.update(set(curNGrams))
+    return returnSet
+
+def intersectNGrams(files):
+    '''Given a list of files, takes the intersection of the n grams contained in them'''
+    setList = []
+    for fileName in files:
+        curNGrams = []
+        with open(fileName) as f:
+            for line in f:
+                if len(line) != 0:
+                    curNGrams.append(line.strip())
+        setList.append(set(curNGrams))
+    return set.intersection(*setList)
+
+def main():
+    files = sys.argv[1:-1]
+    nGrams = intersectNGrams(files)
+    print "Writing " + str(len(nGrams)) + " to " + sys.argv[-1]
+    with open(sys.argv[-1], 'w') as f:
+        writeStr = ""
+        for n in nGrams:
+            writeStr += n + "\n"
+        f.write(writeStr[:-1])
+
+if __name__ == "__main__":
+    main()

### 2014-11-18 AltruisticLanguage/EDA.py

@@ -605,8 +605,9 @@ def compareMineToTheirs(projects):
 def main():
     projects = loadProjects('output')
     projects = [p for p in projects if len(p.category) != 0]
+    basicStats(projects)
     #texts = [p.text for p in projects]
-    extractTextFeatures(projects, minOccur = 50, nGram = 3)
+    #extractTextFeatures(projects, minOccur = 50, nGram = 3)
     #with open("KSText.pickle", 'w') as f: pickle.dump(texts, f, -1)
     #basicStats(projects)
     #compareMineToTheirs(projects)

### 2014-11-18 AltruisticLanguage/GoFundMe/GoFundMeParser.py

@@ -115,16 +115,12 @@ def extractTextFeatures(projects, minOccur = 10, nGram = 3):
 
     myGramFun = lambda x,y: getNGrams(x, y, toLower = True, removePunct = True)
 
-    #map from {project -> {gram -> count}}
-    docCounter = defaultdict(Counter)
-
     for n in range(1,nGram+1):
         print "Extracting " + str(n) + "-grams"
         for p in projects:
             nGrams = myGramFun(p.text, n)
             for g in nGrams:
                 nGramCounter[g] += 1
-                docCounter[p][g] += 1
             catGramDict[p.category].update(set(nGrams))
 
     validGrams = [x for x in proportionalIntersection(catGramDict.values(), proportion=.50)

### 2014-12-07 AltruisticLanguage/Amazon/getNGrams.py
Big Commit

@@ -1,0 +1,142 @@
+import re
+import cPickle as pickle
+import string
+from collections import defaultdict, Counter
+import numpy as np
+from nltk.corpus import stopwords
+
+exclude = set(string.punctuation)
+
+class Product:
+    def __init__(self):
+        self.ID = ""
+        self.description = ""
+        self.mainCats = []
+
+def basicSanitize(inString, removePunct = False, lower = False):
+    '''Returns a very roughly sanitized version of the input string.'''
+    returnString = ' '.join(inString.encode('ascii', 'ignore').strip().split())
+    if removePunct:
+        returnString = ''.join(ch for ch in returnString if ch not in exclude)
+    if lower: returnString = returnString.lower()
+    returnString = ' '.join(returnString.split())
+    return returnString
+
+def getNGrams(stringIn, n, toLower = True, removePunct = False):
+    '''Given an input string, an "n" in n-gram, whether or not we should lowercase, whether or not we should remove punct, and a list of stopwords (None of remove none), return a list of strings representing those n-grams. Might contain repeats.'''
+    if toLower: stringIn = stringIn.lower()
+    exclude = set(string.punctuation)
+    if removePunct: stringIn = ''.join(ch for ch in stringIn if ch not in exclude)
+    tokens = stringIn.split()
+    returnList = []
+    for i in range(len(tokens)-n+1): returnList.append(' '.join(tokens[i:i+n]))
+    return returnList
+
+def proportionalIntersection(setList, proportion = .5):
+    '''Given a list of sets, return the set of items that exist in at least floor(proportion*numSets)'''
+    candidates = set()
+    for l in setList:
+        candidates.update(l)
+    minNumSets = np.floor(proportion*len(setList))
+
+    c = Counter()
+    for s in setList:
+        for item in s: c[item] += 1
+
+    returnList = []
+    for k,v in c.iteritems():
+        if v >= minNumSets: returnList.append(k)
+
+    return returnList
+
+
+def extractTextFeatures(products, minOccur = 50, nGram = 3):
+    '''Given a list of products, a minimum number of occurances, and maximum sized n-gram of interest, return a |projects| x |features| n-gram count matrix and list of n-grams in the order represented, given that the selected features appear in a least minOccur projects and at least once in every category.'''
+    myGramFun = lambda x,y: getNGrams(x, y, toLower = True, removePunct = True)
+    validGrams = []
+
+    for n in range(1,nGram+1):
+        catGramDict = defaultdict(set)
+        nGramCounter = Counter()
[…]

### 2014-12-07 AltruisticLanguage/Comparison/rankingCompare.py

@@ -1,0 +1,41 @@
+from scipy.stats import spearmanr as spr
+import matplotlib.pyplot as plt
+
+file1 = "GFMvKSSW.result"
+file2 = "KSvAMASW.result"
+
+ngramToID = {}
+
+rank1 = []
+rank2 = []
+
+with open(file1) as f:
+    curId = 0
+    for line in f:
+        if len(line) == 0: continue
+        tokens = line.split()
+        nGram = ' '.join(tokens[:-1])
+        if len(tokens) != 2: continue
+        ngramToID[nGram] = curId
+        rank1.append(curId)
+        curId += 1
+
+idToNgram = {i:n for n,i in ngramToID.iteritems()}
+
+with open(file2) as f:
+    for line in f:
+        if len(line) == 0: continue
+        tokens = line.split()
+        if len(tokens) != 2: continue
+        nGram = ' '.join(tokens[:-1])
+        rank2.append(ngramToID[nGram])
+
+
+
+for nGram, ID in ngramToID.iteritems():
+    pass
+
+
+print len(rank1)
+print len(rank2)
+print spr(rank1, rank2)

### 2014-12-07 AltruisticLanguage/ContentModel/ContentModel.py

@@ -1,4 +1,4 @@
-from LanguageModel import BigramModel, ETCBigramModel
+from LanguageModel import BigramModel, ETCBigramModel, UniformModel
 import string
 from nltk import tokenize
 import nltk
@@ -6,11 +6,9 @@ import sys
 import cPickle as pickle
 from nltk import tokenize, ne_chunk
 from nltk.tokenize import WhitespaceTokenizer
-from sklearn.cluster import AgglomerativeClustering
 import warnings
 import re
-from sklearn.feature_extraction.text import CountVectorizer
-from sklearn.decomposition import TruncatedSVD
+from SentenceCluster import UnigramClusterer, BigramClusterer, ParagraphVectorClusterer
 from loadbar import LoadBar
 import numpy as np
 import random
@@ -18,10 +16,9 @@ from collections import Counter, defaultdict
 
 class ContentModel:
     def __init__(self, langModel = 'bigram',
-                 numClusters = 10,
-                 minProportion = .01,
-                 projectionDim = 100,
-                 clusterTrainProp = .004, 
+                 numClusters = 1275,
+                 minProportion = .007,
+                 clusterTrainProp = 1, 
                  d1 = .00001,
                  d2 = .001,
                  cleanSents = None,
@@ -31,7 +28,6 @@ class ContentModel:
         self.langModel = langModel
         self.numClusters = numClusters
         self.minProportion = minProportion
-        self.projectionDim = projectionDim
         self.clusterTrainProp = clusterTrainProp
         self.d1 = d1
         self.d2 = d2
@@ -60,68 +56,112 @@ class ContentModel:
                     pickle.dump(self.cleanSents, f, -1)
         print "There were " + str(len(self.cleanSents)) + " sentences."
         self.cleanSents = self.cleanSents[:int(np.floor(len(self.cleanSents)*self.clusterTrainProp))]
-        print "Finding bigram features"
-        myVectorizer = CountVectorizer(decode_error='ignore',ngram_range=(2,2))
-        bigramFeatures = myVectorizer.fit_transform([x[0] for x in self.cleanSents])
-        print "Executing LSA with " + str(self.projectionDim) + " dimensions"
-        myLSA = TruncatedSVD(n_components = self.projectionDim)
-        trainer = myLSA.fit_transform(bigramFeatures)
-        print "Clustering " + str(trainer.shape[0]) + " sentences for LM examples"
-        clusterer = AgglomerativeClustering(n_clusters = self.numClusters, affinity='cosine',
[…]

### 2014-12-07 AltruisticLanguage/ContentModel/Interpret.py

@@ -1,0 +1,151 @@
+import re
+from collections import defaultdict, Counter
+import operator
+import matplotlib.pyplot as plt
+
+
+def interpretClusters(clusterFileName):
+    #dict from {clusterNum -> [sentence1, sentence2]}
+    clusterMap = defaultdict(list)
+    with open(clusterFileName) as f:
+        curCluster = None
+        for line in f:
+            if line.strip() == "***":
+                continue
+            elif re.search("\d", line) is not None:
+                curCluster = int(line.split()[0])
+            else:
+                clusterMap[curCluster].append(line.strip())
+
+    for cluster, sents in clusterMap.iteritems():
+        print cluster, len(sents)
+    
+    for cluster, sents in clusterMap.iteritems():
+        counts = Counter()
+        for s in sents:
+            counts.update(set(getNGrams(s,n=3)))
+        topTen = sorted(counts.iteritems(), key=operator.itemgetter(1))[::-1][:20]
+        print cluster
+        for s in sents:
+            if 'in the hospital' in s:
+                pass#print s
+        print topTen
+
+def interpretPaths(pathsFile):
+    docSents = defaultdict(list)
+    with open(pathsFile) as f:
+        curDoc = 0
+        for line in f:
+            tokens = line.strip().split(")(")
+            tokens[0] = tokens[0][1:]
+            tokens[-1] = tokens[-1][:-1]
+            for t in tokens:
+                tokens2 = t.split(',')
+                docSents[curDoc].append((tokens2[0][1:-1], int(tokens2[1])))
+            curDoc += 1
+    lengths = Counter()
+    for doc, sents in docSents.iteritems():
+        lengths[len(sents)] += 1
+    popLen, num = max(lengths.iteritems(), key=operator.itemgetter(1))
+    print "The most popular length was " + str(popLen) + " with " + str(num) + " sentences"
+
+    clusterCounts = Counter()
+    seqDict = defaultdict(list)
+    clusterPosDict = defaultdict(list)
+    for doc, sents in docSents.iteritems():
+        seqDict[len(sents)].append([s[1] for s in sents])
+        for i in range(len(sents)):
+            clusterPosDict[s[1]].append(1.*i/len(sents))
+            clusterCounts[s[1]] += 1
+    stateSet = set()
+    for length, sequences in seqDict.iteritems():
[…]

### 2014-12-07 AltruisticLanguage/ContentModel/LanguageModel.py

@@ -123,6 +123,23 @@ class BigramModel(LanguageModel):
         self.d1 = parameters[0]
         self.V = parameters[1]
 
+
+class UniformModel(LanguageModel):
+    def train(self, sentencesIn):
+        self.vocab = set()
+        for s in sentencesIn:
+            self.vocab.update(set(s.split()))
+        self.vocabLen = len(self.vocab)
+
+    def logProb(self, sentence):
+        return -999999
+        return -np.log(self.vocabLen) - len(sentence.split()) * np.log(self.vocabLen+1)
+        
+    def setParams(self, parameters):
+        '''This model requires no parameters'''
+        pass
+
+
 def main():
     y = ['is jack is jack','is jack']
     x = BigramModel(y, parameters=(.001, 100000))

### 2014-12-07 AltruisticLanguage/ContentModel/SentenceCluster.py

@@ -1,0 +1,71 @@
+from sklearn.feature_extraction.text import CountVectorizer
+from sklearn.cluster import AgglomerativeClustering
+from collections import defaultdict
+from gensim.models.doc2vec import Doc2Vec, LabeledSentence, LabeledLineSentence
+import numpy as np
+
+class UnigramClusterer:
+    def __init__(self, k, top=None, show=False):
+        self.k = k
+        self.top = top
+        self.show = show
+    def cluster(self, sentences):
+        cv = CountVectorizer(max_features = self.top)
+        counts = cv.fit_transform(sentences).todense()
+        clusterer = AgglomerativeClustering(n_clusters = self.k, affinity='cosine',
+                                            linkage = 'complete')
+        clusters = clusterer.fit_predict(counts)
+        if self.show:
+            clustSent = defaultdict(list)
+            for i in range(len(sentences)): clustSent[clusters[i]].append(sentences[i])
+            for c, sents in clustSent.iteritems():
+                print c, len(sents)
+        return clusters
+
+class ParagraphVectorClusterer:
+    def __init__(self, k, dims=100, top=None, show=False):
+        self.k = k
+        self.top = top
+        self.show = show
+        self.dims = dims
+    def cluster(self, sentences):
+        vectorizer = Doc2Vec(size=self.dims, min_count = 5, window=8, workers=4)
+        newS = []
+        for i in range(len(sentences)):
+            newS.append(LabeledSentence(sentences[i].decode("UTF-8").split(), 
+                                        ["SENT" + str(i).decode("UTF-8")]))
+        vectorizer.build_vocab(newS)
+        vectorizer.train(newS)
+        data = np.empty([len(sentences), self.dims])
+        for i in range(len(sentences)):
+            data[i,:] = vectorizer["SENT" + str(i).decode("UTF-8")]
+        clusterer = AgglomerativeClustering(n_clusters = self.k, affinity='cosine',
+                                            linkage = 'complete')
+        clusters = clusterer.fit_predict(data)
+        if self.show:
+            clustSent = defaultdict(list)
+            for i in range(len(sentences)): clustSent[clusters[i]].append(sentences[i])
+            for c, sents in clustSent.iteritems():
+                print c, len(sents)
+                for s in sents[:5]:
+                    print s
+        return clusters
+
+class BigramClusterer:
+    def __init__(self, k, top=None, show=False):
+        self.k = k
+        self.top = top
+        self.show = show
+    
[…]

### 2014-12-07 AltruisticLanguage/ContentModel/loadbar.py

@@ -15,7 +15,9 @@ class LoadBar():
         return self
     
     def test(self, i, length):
-        return i!=0 and i%(length/self.width)==0
-            
+        try:
+            return i!=0 and i%(length/self.width)==0
+        except ZeroDivisionError:
+            return True
     def clear(self):
         sys.stdout.write("\n")

### 2014-12-07 AltruisticLanguage/EDA.py

@@ -13,6 +13,7 @@ from sklearn.linear_model import LogisticRegression
 from sklearn import preprocessing
 from scipy.sparse import csr_matrix
 from scipy.io import mmwrite
+import matplotlib.pyplot as plt
 
 class _GetchUnix:
     def __init__(self):
@@ -173,12 +174,22 @@ def buildSubCategoryDictionary(projects):
 
 def categoryAltruisticPropTest(projects):
     '''Given a list of projects, split on category. Then, conduct a proportion test for for each category for proportion of altruistic donations vs not altruistic donations split on success/failure.'''
+
     catDict = buildCategoryDictionary(projects)
-    
+    subcatDict = buildSubCategoryDictionary(projects)
+
+    catDict = dict(catDict.items() + subcatDict.items())
+
     print '{:>18}  {:>18}  {:>18}  {:>18}'.format("Category",
                                                   "Alt Ratio Succ",
                                                   "Alt Ratio Fail",
                                                   "p-val")
+
+    barVals = []
+    barColors = []
+    barLabels = []
+    curIndex = 0
+    barLefts = []
     for cat, projectList in catDict.iteritems():
         if len(cat) == 0: continue
         success = [x for x in projectList if x.result and x.backers != 0]
@@ -192,10 +203,24 @@ def categoryAltruisticPropTest(projects):
 
         propSuc, propFail = float(sucAlt*1./sucTotal), float(failAlt*1./failTotal)
         
+        barVals.append(propFail-propSuc)
+        barColors.append('b' if p < .01 else 'r')
+        barLabels.append(cat)
+        barLefts.append(curIndex)
+        curIndex += 1
+
         print '{:>18}  {:>18.4f}  {:>18.4f}  {:>18.4f}'.format(cat, propSuc, propFail, p)
 
         #if propSuc > propFail: print "Greater proportion with successful projects"
         #else: print "Greater proportion with failed projects"
+
+    plt.bar(barLefts, barVals, align='center', color = barColors)
+    plt.xticks([b+.5 for b in barLefts], barLabels, rotation=45, ha='right')
+    figure = plt.gcf() # get current figure
+    figure.set_size_inches(14, 4)
+    plt.xlim([-1.1, len(barLefts)+.1])
+    plt.ylim([min(barVals) - .002, max(barVals) + .002])
+    plt.savefig("failSuccess.png", dpi = 100, bbox_inches='tight')
 
 def categoryAltruisticMeanValueTest(projects):
[…]

### 2014-12-07 AltruisticLanguage/GoFundMe/GoFundMeParser.py

@@ -163,6 +163,13 @@ def getNGrams(stringIn, n, toLower = True, removePunct = False):
 
 def main():
     projects = set(loadProjects("output"))
+    catDict = defaultdict(list)
+    for p in projects: catDict[p.category].append(p)
+    
+    for k,v in catDict.iteritems():
+        with open("projectTexts/" + k + ".pickle", 'w+') as f:
+            pickle.dump([x.text for x in v], f, -1)
+
     myTexts = [p.text for p in projects]
     with open('GFMText.pickle','w') as f:
         pickle.dump(myTexts, f, -1)

### 2014-12-07 AltruisticLanguage/getDescriptions.py

@@ -1,29 +1,40 @@
 import cPickle as pickle
 from KickstarterParser import *
+from nltk.corpus import stopwords
 import string
 import re
 
 def main():
     '''Pickles a list of 3000 strings, each corresponding to a kickstarter project description. Also does some pre-processing.'''
-    numFiles = 3
+    numFiles = 46
     pickleNames = ["output/" + str(i+1) + ".pickle" for i in range(numFiles)]
     finalList = []
     for name in pickleNames:
         curProjectList = pickle.load(open(name, "rb"))
         for p in curProjectList:
-            finalList.append(cleanDescription(p.text, mapNumbers = True, removeURLs = True))
+            finalList.append(cleanDescription(p.text, mapNumbers = False,
+                                              removeURLs = True,
+                                              removeStops = True))
+            
 
-    myOut = open('3000.pickle', 'w')
+    myOut = open('KSProcessed.pickle', 'w')
     pickle.dump(finalList, myOut, -1)
     myOut.close()
 
-def cleanDescription(descIn, mapNumbers = False, removeURLs = False):
-    '''Given a description, '''
+def cleanDescription(descIn, mapNumbers = False,
+                     removeURLs = False, removeStops = False):
 
     if removeURLs:
-        urlRE = ur'(?i)\b((?:https?://|www\d{0,3}[.]|[a-z0-9.\-]+[.][a-z]{2,4}/)(?:[^\s()<>]+|\(([^\s()<>]+|(\([^\s()<>]+\)))*\))+(?:\(([^\s()<>]+|(\([^\s()<>]+\)))*\)|[^\s`!()\[\]{};:\'".,<>?\xab\xbb\u201c\u201d\u2018\u2019]))'
-        descIn = re.sub(urlRE, '', descIn)
-
+        urlRE = r"(?:\s|^)(\S*\.(?:com|org|net|be)\S*)(?:\s|$)"
+        desc = ' '.join(re.sub(urlRE, ' ', descIn).split())
+        #desc = ' '.join(x for x in descIn.split() if tokenTest(x))
+        #def tokenTest(token):
+        #    forbid = ["." + x for x in ["com", "net","be","org"]]
+        #    for f in forbid:
+        #        if f in token:
+        #            print token
+        #            return False
+        #    return True
     exclude = set(string.punctuation)
     desc = ''.join(ch for ch in descIn if ch not in exclude).lower()
     desc = ' '.join(desc.split())
[…]

### 2014-12-07 AltruisticLanguage/regressionAltruism.R

@@ -1,0 +1,53 @@
+setwd("/home/jhessel/Desktop/NLP/git/AltruisticLanguage")
+library('Matrix')
+library('glmnet')
+library('foreach')
+library('doParallel')
+
+topK <- 50
+rsort <- function(x) {
+  sort(x, decreasing = TRUE)
+}
+myResult <- read.csv("altBinaryTarget.csv", header = F)$V1
+myDataControl <- readMM("controlsWithSucc.mtx")
+myData <- readMM("allWithSucc.mtx")
+
+#NORMALS
+crossValid <- cv.glmnet(myData,
+                        myResult, type.measure = 'class',
+                        family="binomial", alpha=1, parallel=T)
+bestlambda<-crossValid$lambda.min
+mse.min <- crossValid$cvm[crossValid$lambda == bestlambda]
+myCoefs <- coef(crossValid, s=bestlambda)
+myCoefMatrix <- as.matrix(myCoefs)
+myPredictions <- predict(crossValid, myData, type = "class", s=bestlambda)
+colnames(myCoefMatrix) <- c("Beta")
+headers <- read.csv("allHeadersWithSucc.csv")
+rownames(myCoefMatrix) <- c("Intercept", colnames(headers))
+
+apply(myCoefMatrix, 2, sort)[1:topK,]
+apply(myCoefMatrix, 2, rsort)[1:topK,]
+
+#Just Controls
+crossValidControl <- cv.glmnet(myDataControl,
+                               myResult, type.measure = 'class',
+                               family="binomial", alpha=1, parallel=T)
+bestlambdaControl <-crossValidControl$lambda.min
+mse.minControl <- crossValidControl$cvm[crossValidControl$lambda == bestlambdaControl]
+myCoefsControl <- coef(crossValidControl, s=bestlambdaControl)
+myCoefMatrixControl <- as.matrix(myCoefsControl)
+myPredictionsControl <- predict(crossValidControl, myDataControl,
+                                type = "class", s=bestlambdaControl)
+colnames(myCoefMatrixControl) <- c("Beta")
+headersControl <- read.csv("controlHeadersWithSucc.csv")
+rownames(myCoefMatrixControl) <- c("Intercept", colnames(headersControl))
+
+apply(myCoefMatrixControl, 2, sort)[1:topK,]
+apply(myCoefMatrixControl, 2, rsort)[1:topK,]
+
+
[…]

### 2014-12-07 AltruisticLanguage/writing/paper.tex
added paper updates

@@
 \usepackage{url}
+\usepackage{array}
+\usepackage{graphicx}
+\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
+\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
+\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
+\newcommand{\specialcell}[2][l]{%
+  \begin{tabular}[#1]{@{}l@{}}#2\end{tabular}}
 \frenchspacing
@@
 
+\begin{table*}[t]
+\centering
+\scriptsize
+\begin{tabular}{|*{12}{c|}}  % repeats {c|} 18 times
+\hline
+\multicolumn{6}{|c}{GoFundMe vs. Kickstarter} & \multicolumn{6}{|c|}{Amazon vs. Kickstarter} \\ \hline
+\multicolumn{2}{|c}{Unigrams} & \multicolumn{2}{|c}{Bigrams} & \multicolumn{2}{|c}{Trigrams} & 
+\multicolumn{2}{|c}{Unigrams} & \multicolumn{2}{|c}{Bigrams} & \multicolumn{2}{|c|}{Trigrams} \\ \hline 
+Unigram & Z & Bigram & Z & Trigram & Z & Unigram & Z & Bigram & Z & Trigram & Z \\ \hline
+the & -77.74 & of the & -42.64 & check out the & -10.43 &
+project & -366.62 & thank you & -186.89 & be able to & -141.92 \\ \hline
+project & -57.09 & the story & -20.99 & a series of & -9.97 &
+film & -326.85 & want to & -185.62 & thank you for & -112.63 \\ \hline
+film & -48.74 & the book & -20.89 & in new york & -9.90 &
+help & -293.91 & to make & -168.24 & would like to & -100.47 \\ \hline
+music & -43.55 & to create & -20.33 & copy of the & -9.22 &
+us & -278.78 & able to & -159.11 & a part of & -94.38 \\ \hline
+of & -35.23 & the game & -18.85 & be used to & -9.13 &
+money & -252.97 & be able & -142.71 & in order to & -93.87 \\ \hline \hline
+she & 84.92 & thank you & 41.65 & to be able & 19.55 &
+university & 88.20 & variety of & 40.80 & a member of & 24.97\\ \hline
+her & 91.96 & i have & 52.57 & thank you for & 20.75 &
+title & 90.43 & comes with & 43.74 & member of the & 27.22 \\ \hline
+family & 98.57 & to help & 55.70 & to go to & 25.35 &
+author & 91.92 & available in & 43.94 & is one of & 27.58 \\ \hline
+my & 114.84 & and i & 60.22 & friends and family & 27.44 &
+features & 102.99 & designed to & 46.39 & a variety of & 29.95 \\ \hline
+i & 136.98 & i am & 81.20 & family and friends & 31.12 &
+text & 115.04 & university of & 62.84 & one of the & 30.92 \\ \hline
+\end{tabular}
+\caption{Summary of Bayesian analysis of language comparing Kickstarter to GoFundMe and Amazon. Negative Z-scores correspond to Kickstarter. Top ten most significant n-grams are presented.}
+\label{tab:pairwise}
+\end{table*}
+
 Furthermore, in our dataset consisting of 45810 completed Kickstarter projects, we are able to quantify the number of purely altruistic donation events and the total value given above and beyond the amount required for all reward claims.
-When a user backs a project on Kickstarter (which is impossible to do anonymously) they are able to select an option that allows them to claim no rewards.
-Because the total number of claims for each reward are displayed publically on the project page, along with the total number of backers, we are able to compute the total number of purely altruistic donation events for each project.
-Also, the site allows for users to give an amount exceeding the cost of a given reward, so we are able to compute the total amount donated to a project above and beyond the amount required for all the posted reward claims.
 Of the roughly 3.4M donation events, about 360K (10.59\%) resulted from users who selected no reward.
 Of the roughly \$246M pledged in our dataset, over \$53M (21.59\%) was given altruistically.
+Compared to previous analyses of altruism in online communities THIS IS A LOT OF MONEY.
 
@@
 
-\section{Dataset and Methods}
-
-\section{Kickstarter vs. GoFundMe vs. Amazon}
+\section{Kickstarter vs. GoFundMe and Amazon}
 What language used on Kickstarter is altruistic?
@@
 To address these questions, it might be possible to derive stringent definitions of altruism and salespersonship.
-However, for our analysis, we resort to a more objective analysis by incorporating two additional data sets., one from Amazon and one from GoFundMe.
-Amazon is a very popular  To compare the language used on Kickstarter to purely commercial and purely altrustic
+However, for our analysis, we resort to a more objective analysis by incorporating two additional data sets, one from Amazon and one from GoFundMe.
+
+Amazon is a very popular online marketplace, where users can purchase items from a wide range of categories.
+Each product is associated with a description and and a set of categories.
+Our dataset consists of just under 1.5M Amazon product descriptions \cite{mcauley2013hidden}.
+We believe that Amazon product descriptions can be considered as purely commercial.
+On the other hand, GoFundMe is a crowdfunding site similar to Kickstarter, but campaigns are generally more focused on charitable/personal ventures.
+For instance, a popular category on GoFundMe is ``Medical,'' wherein users create pages to raise money for medical expenses for family and friends.
+Our dataset consists of 7.7K GoFundMe project descriptions.
+In contrast to Kickstarter, in a vast majority of cases GoFundMe contributors don't have the option to select compensentory rewards, and we therefore regard our GoFundMe data as requests for purely altruistic actions.
+
+To compare the language used on Kickstarter to purely commercial and purely altrustic pitches, we adopt a Bayesian approach that has previously been successful in comparing the language used by two political parties on a specific issue \cite{monroe2008fightin}.
+This model has been used to compare word usage between two corpora in a princpled way.
+Under the model, language is modeled as a ``bag of words'' represented by a multinomial distribution over vocabulary items.
+For the two corpora in question, we assume that their language vectors are drawn from a Dirichlet prior.
+Though it is possible in this scenario to encode useful information in the prior, we find it sufficient to utilize an uninformative prior and set our Dirichlet hyperparameter to be $\alpha=.01$.
+Assuming this language model, it becomes possible to compute approximate differences in vocabulary usages, and approximate variances of those differences.
+
+In order to use this model, one must first define a vocabulary.
+Because we are interested in language rather than specific subject matter, we apply a cross-categorical filtering scheme in an attempt to control for topic.
+Recall that in each of our datasets, documents are associated with one or more categories.
+To control for topic, we extract all n-grams of interest that appear in some minimum proportion of all categories, as well as (optionally) a minimum number of times throughout the dataset.
+For each of our three datasets, we examine unigrams, bigrams, and trigrams, and choose such that each dataset is roughly equally represented.
+For our particular parameter filtrations, we derive 24K n-grams from Kickstarter, 24K n-grams from GoFundMe, and 28K n-grams from Amazon.
+Finally, an intersection of these sets provides the final 7K n-gram vocabulary of interest.
+
+The results of these analyses are summarized in Table \ref{tab:pairwise}.
+In general, our model and filtration scheme succeeds in controling for topic, though some artifacts remain.
+For instance, a majority of the Amazon reviews in our corpus are book reviews, which potentially obscures the intersting use of n-grams like ``university of,'' ``author,'' and ``title.'' Despite these artifacts, XXXXX.
+
+To emperically analyze these n-gram comparisons, we first rank the n-grams in each experiment by their z-scores and compute the Spearman correlation between the Kickstarter vs.
+Amazon and Kickstarter vs.
+GoFundMe analyses.
+The intuition behind this comparsion is as follows: if Kickstarter is more altruistic than Amazon, but less altruistic than GoFundMe, then we would expect altruistically-associated n-grams to be on opposite ends of each ranking.
+We compute rankings and correlation statistics for unigrams, bigrams, and trigrams seperately.
+
+For the 3391 unigrams, we find a negative correlation as expected, but the significance of this correlation could not be verified ($\rho = -.010, p = .55$).
+As we extend our analysis to more complex lingustic features such as bigrams and trigrams, which are less sensitive to unfiltered topical noise and likely carry more signal regarding the use of language, the negative correlation between these two rankings becomes more clear.
+For the 4195 bigrams, we see a significant negative correlation ($\rho = -.038, p < .02$) and for the 898 trigrams, we see a large significant negative correlation ($\rho = -.11, p < .002$).
+
+Overall, we argue this analysis demonstrates that discourse on Kickstarter is neither entirely Amazon-like, nor entirely GoFundMe-like, but rather lies in its own lingustic regime at the intersection of altruism and commercialism.
+
+\section{What do Altruistic Requests Look Like?}
+
+\begin{table}
+\centering
+\footnotesize
+\begin{tabular}{|l|l|L{2.8cm}|}
+\hline
+Cluster Name & Number of Sentences & Top 3 Trigrams \\\hline
+ & 551 & \specialcell{`one of the'\\`all of the'\\`is one of'} \\\hline
+ & 275 & \specialcell{`is too small'\\`you can help'\\`you can give'} \\\hline
+ & 288 & \specialcell{`thank you for'\\`you for your'\\`thank you so'}\\\hline
+ & 1190 & \specialcell{`be able to'\\`to be able'\\`\# year old'}\\\hline
+ & 708 & \specialcell{`to the hospital'\\`to the er'\\`him to the'}\\\hline
+ & 457 & \specialcell{`to help with'\\`would like to'\\`and his family'}\\\hline
+ & 641 & \specialcell{`in the hospital'\\`\# year old'\\`is in the'} \\\hline
+ & 437 & \specialcell{`was diagnosed with'\\`my name is'\\`\# years old'} \\\hline
+ & 498 & \specialcell{`we are asking'\\`are asking for'\\`family and friends'} \\\hline 
+ & 334 & \specialcell{`be greatly appreciated'\\`will be greatly'\\`will be a'} \\\hline
+ & 216 & \specialcell{`he is a'\\`he is in'\\`\# years old'} \\\hline
+Etcetera & 1520 & \specialcell{'to be a'\\`as well as'\\`to and from'} \\\hline
+\end{tabular}
+\caption{Clustering derived from the content model.}
+\label{tab:contentmodel}
+\end{table}
+
+To analyze the sequential structure of requests, we run a case study on a subset of data utilizing a content model \cite{barzilay2004catching} to produce a sentence clustering.
+A content model is an unsupervized learning algorithm that operates on the sentence level, takes information order into account, and learns transition probabilities between sentence types.
+Here we provide a brief description of the content model, along with its basic goals and limitations.
+
+BLAH
+
+We apply the content model to a small subset of the GoFundMe corpus (460 documents with a total of 7K sentences) corresponding to the campaigns listed in the ``Medical'' category.
+We utilize 11 content clusters and 1 etcetera cluster in our model.
+After our expectation maximization converged, we were left with the clusters displayed in Table \ref{tab:contentmodel}.
 
 \section{Prediction of Altruism on Kickstarter}
+\begin{table}
+\centering
+\begin{tabular}{|l|L{5cm}|}
+\hline
+Goal & Project funding goal (dollars) \\\hline
+Featured & Project was selected by Kickstarter staff and advertised as such\\\hline
+Duration & Project's duration (days) \\\hline
+Num Levels & Number of reward types \\\hline
+Minimum Pledge & Minimum pledge to get a reward (dollars)\\\hline
+Video & Indicates whether or not the project has an associated video \\\hline
+Num Updates & Number of ``updates'' projects owners have posted \\\hline
+Num Comments & Number of user comments posted \\\hline
+Facebook Connected & Indicates whether or not project owners have personal Facebook profiles associated with Kickstarter\\\hline
+Success & Indicates whether or not the project was successful\\
+\hline
+\end{tabular}
+\caption{Descriptions of the control features used in the regression tasks.}
+\label{tab:controls}
+\end{table}
+How does Altruism manifest on Kickstarter?
+When a user backs a project on Kickstarter (which is impossible to do anonymously) they are prompted to select a backer reward of value less than or equal to their donation amount.
+If a user does not want to claim a reward but, rather, donate altruistically, there exists an option that allows them to claim no rewards.
+Because the total number of claims for each non-altruistic reward are displayed publicly on the project page, along with the total number of backers (altruistic and non-altruistic alike) we are able to compute the total number of purely altruistic donation events for each project.
+Furthermore, the site allows for users to give an amount exceeding the cost of a given reward, so we are able to compute the total amount donated to a project above and beyond the amount required for all the posted reward claims.
+As previously noted, altruistic donation events
+
+In a similar vein to \cite{mitra2014language} we define a binary altruistic response variable and train two logistic regression classifiers to predict that variable.
+The response variable is defined as follows: if a project recieves any donations and the proportion of altruistic donations it recieves exceeds $10\%$, we assign it to the altruistic group, otherwise, it is assigned to the non-altruistic group.
+Defining this control variable partitions the dataset into 26733 altruistic projects and 19077 projects giving a constant prediction baseline of 58.34\% accuracy.
+
+Out first regression task consists of a controls-only baseline.
+The control variables we use mostly mirrors those used in Mitra and Gilbert's analysis, except we add their ``Success'' target as a control.
+The set of control variables consists of 49 binary variables, one for each Kickstarter project category (``Theater,'' ``Indie Rock,'' ``Open Software,'' etc.) and an additional 10 variables summarized in Table \ref{tab:controls}.
+
+We use glmnet \cite{friedman2010glmnet} for our regression tasks.
+
+Our textual features consist of unigrams, bigrams, and trigrams from the project descriptions, FAQ question/answers, and reward descriptions of our Kickstarter projects.
+We apply a category filter, forcing all n-grams to appear in all 49 categories.
+Applying this filtration process, we end up with 30784 topic-controlled n-grams.
+
+Our best controls only logistic regression model had a cross-validation accuracy of 65.27\%.
+
+When we incorporate lingustic features, our cross-validation accuracy XXXXX.
+
+\section{Failing Projects, More Donations?}
+
+\begin{figure*}
+\centering
+\includegraphics[width=.9\textwidth]{figures/failSuccess.png}                         
+\caption{temp}
+\label{fig:succfail}
+\end{figure*}
 

### 2014-12-16 AltruisticLanguage/EDA.py
updates

@@ -452,19 +452,21 @@ def extractTextFeatures(projects, minOccur = 50, nGram = 3, counts=False):
     validGrams = [v for v in validGrams if not
                   set.issubset(set(v.split()), set(stopwords.words('english')))]
 
-    print "Using {} n-grams".format(len(validGrams))
+    print "Found {} n-grams".format(len(validGrams))
 
     gramToVar = {}
     i = 1
+    print "Filtering..."
     for v in validGrams:
         if i % 1000 == 0: print i
         perDocList = []
         for cat, catCount in catCounter.iteritems():
             perDocList.append((gramCatCounter[cat][v]*.1)/catCount)
-        gramToVar[v] = np.var(perDocList)
+        gramToVar[v] = 1.0*(np.max(perDocList)-np.min(perDocList))/np.max(perDocList)
     validGrams = [x[0] for x in
-                  sorted(gramToVar.items(), key = operator.itemgetter(1))[:int(.75*len(gramToVar))]]
-    
+                  sorted(gramToVar.items(), key = operator.itemgetter(1))[:int(.9*len(gramToVar))]]
+
+    print "Using {} n-grams".format(len(validGrams))
     returnMatrix = np.zeros([len(projects),len(validGrams)], dtype = np.float32)
     for i in range(len(projects)):
         if i is not 0 and i % 100 == 0: print i
@@ -652,7 +654,7 @@ def main():
     #saveFeatureMatrixAndHeaders(projects, "dataBinaryTheirs.mtx",
     #                            "target.csv", "headersTheirs.csv", given="KS.predicts",
     #                            counts=False)
-    saveFeatureMatrixAndHeaders(projects, "all75Filter.mtx", "allHeaders75Filter.csv", control=False)
+    saveFeatureMatrixAndHeaders(projects, "all90Filter.mtx", "allHeaders90Filter.csv", control=False)
 
     #target = np.zeros([len(projects), 1], dtype=np.int)
     

### 2014-12-16 AltruisticLanguage/regressionAltruism.R

@@ -4,13 +4,17 @@ library('glmnet')
 library('foreach')
 library('doParallel')
 
+registerDoParallel()
+
 topK <- 50
 rsort <- function(x) {
   sort(x, decreasing = TRUE)
 }
-myResult <- read.csv("altBinaryTarget.csv", header = F)$V1
+myData <- readMM("all.mtx", header = F)$V1
+headers <- read
 myDataControl <- readMM("controlsWithSucc.mtx")
 myData <- readMM("allWithSucc.mtx")
+myResultContinuous <- read.csv("altContinuousTarget.csv", header = F)$V1
 
 #NORMALS
 crossValid <- cv.glmnet(myData,
@@ -51,3 +55,27 @@ dev2 <- deviance(crossValidControl$glmnet.fit)[crossValidControl$lambda == bestl
 df1 <- crossValid$glmnet.fit$df[crossValid$lambda == bestlambda]
 df2 <- crossValidControl$glmnet.fit$df[crossValidControl$lambda == bestlambdaControl]
 1-pchisq(dev2-dev1, df1-df2)
+
+
+#Experiments with 20 percent
+perc20Control <- cv.glmnet(myDataControl,
+                           myResult20, type.measure = 'class',
+                               family="binomial", alpha=1, parallel=T)
+bestlambda20Control <-perc20Control$lambda.min
+mse.min20Control <- perc20Control$cvm[perc20Control$lambda == bestlambda20Control]
+myCoefs20Control <- coef(perc20Control, s=bestlambda20Control)
+myCoefMatrix20Control <- as.matrix(myCoefs20Control)
+colnames(myCoefMatrix20Control) <- c("Beta")
+headers20Control <- read.csv("controlHeadersWithSucc.csv")
+rownames(myCoefMatrix20Control) <- c("Intercept", colnames(headers20Control))
+
+apply(myCoefMatrix20Control, 2, sort)[1:topK,]
+apply(myCoefMatrix20Control, 2, rsort)[1:topK,]
+plot(perc20Control)
+
+
+perc20 <- cv.glmnet(myData, myResult20, type.measure = 'class', family="binomial", alpha=1, parallel=T)
+bestlambda20 <- perc20$lambda.min
+mse.min20 <- perc20$cvm[perc20$lambda == bestlambda20]
+
+test <- cv.glmnet(myDataControl, myResultContinous > .1, family="binomial", type.measure = "class", parallel = T)

### 2014-12-16 AltruisticLanguage/EDA.py
yeahboy

@@ -449,9 +449,6 @@ def extractTextFeatures(projects, minOccur = 50, nGram = 3, counts=False):
     
     validGrams = [x for x in set.intersection(*catGramDict.values()) if nGramCounter[x] >= minOccur]
 
-    validGrams = [v for v in validGrams if not
-                  set.issubset(set(v.split()), set(stopwords.words('english')))]
-
     print "Found {} n-grams".format(len(validGrams))
 
     gramToVar = {}
@@ -466,7 +463,27 @@ def extractTextFeatures(projects, minOccur = 50, nGram = 3, counts=False):
     validGrams = [x[0] for x in
                   sorted(gramToVar.items(), key = operator.itemgetter(1))[:int(.9*len(gramToVar))]]
 
-    print "Using {} n-grams".format(len(validGrams))
+    
+    #print "Using {} n-grams".format(len(validGrams))
+    #with open('kickstarterSW.ngrams','w') as f:
+    #    words = ""
+    #    for v in validGrams:
+    #        words += v + "\n"
+    #    f.write(words[:-1])
+
+
+    #validGrams = [v for v in validGrams if not
+    #              set.issubset(set(v.split()), set(stopwords.words('english')))]
+
+    #print "Using {} n-grams".format(len(validGrams))
+    #with open('kickstarter.ngrams','w') as f:
+    #    words = ""
+    #    for v in validGrams:
+    #        words += v + "\n"
+    #    f.write(words[:-1])
+
+    #quit()
+
     returnMatrix = np.zeros([len(projects),len(validGrams)], dtype = np.float32)
     for i in range(len(projects)):
         if i is not 0 and i % 100 == 0: print i

### 2014-12-16 AltruisticLanguage/writing/paper.tex

@@
 \title{Pre-orders or Philanthropy: An Analysis of Altruism on Kickstarter}
-\author{Jack Hessel}
+\author{Jack Hessel \and Lillian Lee\\Cornell University}
 \maketitle
@@
 Num Comments & Number of user comments posted \\\hline
-Facebook Connected & Indicates whether or not project owners have personal Facebook profiles associated with Kickstarter\\\hline
-Success & Indicates whether or not the project was successful\\
+Facebook Connected & Indicates whether or not project owners have personal Facebook profiles associated with Kickstarter\\
 \hline
@@
 \end{table}
-How does Altruism manifest on Kickstarter?
+How does altruism manifest on Kickstarter?
 When a user backs a project on Kickstarter (which is impossible to do anonymously) they are prompted to select a backer reward of value less than or equal to their donation amount.
@@
 Furthermore, the site allows for users to give an amount exceeding the cost of a given reward, so we are able to compute the total amount donated to a project above and beyond the amount required for all the posted reward claims.
-As previously noted, altruistic donation events
+As previously noted, altruistic donation events constitute 10.59\% of all donation events and 21.59\% of all money donated in our dataset (over 53M dollars) was given away.
 
-In a similar vein to \cite{mitra2014language} we define a binary altruistic response variable and train two logistic regression classifiers to predict that variable.
+In a similar vein to \cite{mitra2014language} we define a binary altruistic response variable and train several logistic regression classifiers to predict that variable.
 The response variable is defined as follows: if a project recieves any donations and the proportion of altruistic donations it recieves exceeds $10\%$, we assign it to the altruistic group, otherwise, it is assigned to the non-altruistic group.
@@
 Out first regression task consists of a controls-only baseline.
-The control variables we use mostly mirrors those used in Mitra and Gilbert's analysis, except we add their ``Success'' target as a control.
-The set of control variables consists of 49 binary variables, one for each Kickstarter project category (``Theater,'' ``Indie Rock,'' ``Open Software,'' etc.) and an additional 10 variables summarized in Table \ref{tab:controls}.
+The set of control variables, which mostly mirrors Mitra and Gilbert's control set, consists of 49 binary variables, one for each Kickstarter project category (``Theater,'' ``Indie Rock,'' ``Open Software,'' etc.) and an additional 10 variables summarized in Table \ref{tab:controls}.
 
 We use glmnet \cite{friedman2010glmnet} for our regression tasks.
+glmnet is a software package that implements cyclic coordinate decent and is capable of performing penalized regression tasks on highly sparse datasets.
+For our experiments, we utilize an $L_1$ (lasso) regularization term in an attempt to enforce sparsity and derive a parsimonious model, and set glmnet to perform 10-fold cross validation to search for the optimal regularization coefficient.
+Notably, glmnet purposefully does not report standard errors on resulting feature coefficients because the regularization process intorudces substantial bias into the regression process.
 
-Our textual features consist of unigrams, bigrams, and trigrams from the project descriptions, FAQ question/answers, and reward descriptions of our Kickstarter projects.
-We apply a category filter, forcing all n-grams to appear in all 49 categories.
-Applying this filtration process, we end up with 30784 topic-controlled n-grams.
+Our best controls only logistic regression model had a cross-validation accuracy of 64.42\%, improving upon our constant prediction baseline by 6.08\%.
+The most important positive and negative predictive features were all Kickstarter category control variables.
+Dance, theater, public art, performance art, and classical music ($\vec{\beta} = \langle 1.84, 1.56, 1.24, 1.04, .930 \rangle$, respectively) were the categorical variables which were the strongest positive predictors, whereas board/card games, games, comics, video games, and product design ($\vec{\beta} = \langle -1.64, -1.23, -1.02, -.862, -.795 \rangle$, respectively) were the strongest negative predictors.
+This result indicates that product category is the most important factor in determining if a project will recieve altruistic donations, and perhaps that projects in artistic categories are more likely to recieve such Kickstarter backing.
+This result is fairly unsurprising -- artistic endevours are generally regarded as intrinsically valuable to society (CITECITECITE), and the negatively predictive categories tend to have concretely associated products with their projects (a video game, for instance).
+Some non-categorical positive predictors included
 
-Our best controls only logistic regression model had a cross-validation accuracy of 65.27\%.
+Our textual features consist of binary indicator variables for unigrams, bigrams, and trigrams in the project descriptions, FAQ question/answers, and reward descriptions of our Kickstarter projects.
+We apply both a category filter and a variance filter to determine our resulting n-gram set.
+Our category filter requires all n-grams to appear in all 49 categories.
+For our variance filter, we consider the usage of a given n-gram over all categories, and compute the variance of the resulting multinomial distribution.
+Finally, we remove from consideration the most variable 25\% of n-grams.
+Applying this two-part filtration process, we end up with 30784 category and variance filtered n-grams.
 
-When we incorporate lingustic features, our cross-validation accuracy XXXXX.
+The goal of this filtration process is to produce a set of n-grams that are independent of topic.
+For instance, because the term ``art project'' is used significantly more readily in artistic Kickstarter categories, its significance in regression is more topically meaningful than lingustically meaningful, as the corresponding covariate is highly colinear with the artistic category indicator variables.
+
+When we incorporate these particular lingustic features, our cross-validation accuracy XXXXX.
 

### 2014-12-17 AltruisticLanguage/writing/paper.tex
updated paper

@@
 Unigram & Z & Bigram & Z & Trigram & Z & Unigram & Z & Bigram & Z & Trigram & Z \\ \hline
-the & -77.74 & of the & -42.64 & check out the & -10.43 &
-project & -366.62 & thank you & -186.89 & be able to & -141.92 \\ \hline
-project & -57.09 & the story & -20.99 & a series of & -9.97 &
-film & -326.85 & want to & -185.62 & thank you for & -112.63 \\ \hline
-film & -48.74 & the book & -20.89 & in new york & -9.90 &
-help & -293.91 & to make & -168.24 & would like to & -100.47 \\ \hline
-music & -43.55 & to create & -20.33 & copy of the & -9.22 &
-us & -278.78 & able to & -159.11 & a part of & -94.38 \\ \hline
-of & -35.23 & the game & -18.85 & be used to & -9.13 &
-money & -252.97 & be able & -142.71 & in order to & -93.87 \\ \hline \hline
-she & 84.92 & thank you & 41.65 & to be able & 19.55 &
-university & 88.20 & variety of & 40.80 & a member of & 24.97\\ \hline
-her & 91.96 & i have & 52.57 & thank you for & 20.75 &
-title & 90.43 & comes with & 43.74 & member of the & 27.22 \\ \hline
-family & 98.57 & to help & 55.70 & to go to & 25.35 &
-author & 91.92 & available in & 43.94 & is one of & 27.58 \\ \hline
-my & 114.84 & and i & 60.22 & friends and family & 27.44 &
-features & 102.99 & designed to & 46.39 & a variety of & 29.95 \\ \hline
-i & 136.98 & i am & 81.20 & family and friends & 31.12 &
-text & 115.04 & university of & 62.84 & one of the & 30.92 \\ \hline
+the & -77.52 & of the & -42.74 & be used to & -9.05 &
+we & -685.35 & will be & -367.20 & be able to & -141.92 \\\hline
+of & -42.74 & to create & -20.17 & some of the & -8.26 &
+i & -525.09 & we are & -256.59 & tank you for & -112.63 \\\hline
+new & -26.01 & on the & -19.96 & will be a & -6.25 &
+will & -514.99 & we have & -218.54 & a part of & -94.38 \\\hline
+show & -25.24 & about the & -16.48 & be used for & -6.07 &
+our & -501.84 & we will & -193.24 & in order to & -93.87 \\\hline
+create & -23.99 & and the & -15.65 & to make the & -6.02 &
+be & -356.80 & thank you & -186.89 & to make this & -92.88 \\\hline \hline
+
+me & 80.57 & would be & 37.02 & take care of & 16.27 &
+perfect & 64.77 & is the & 48.67 & the united states & 2.88 \\\hline
+was & 82.01 & name is & 37.74 & to help with & 17.72 &
+has & 73.00 & and is & 54.69 & is a great & 3.75\\\hline
+am & 82.62 & family and & 40.60 & in need of & 19.04 &
+with & 78.24 & with a & 56.31 & is one of & 27.54\\\hline
+family & 98.81 & thank you & 41.80 & thank you for & 20.38 &
+includes & 81.00 & has a & 56.71 & of the most & 30.88\\\hline
+i & 136.42 & to help & 55.71 & friends and family & 27.25 &
+easy & 82.72 & out of & 71.67 & one of the & 30.97 \\\hline
 \end{tabular}
@@
 The results of these analyses are summarized in Table \ref{tab:pairwise}.
-In general, our model and filtration scheme succeeds in controling for topic, though some artifacts remain.
-For instance, a majority of the Amazon reviews in our corpus are book reviews, which potentially obscures the intersting use of n-grams like ``university of,'' ``author,'' and ``title.'' Despite these artifacts, XXXXX.
 
-To emperically analyze these n-gram comparisons, we first rank the n-grams in each experiment by their z-scores and compute the Spearman correlation between the Kickstarter vs.
+To emperically analyze these n-gram comparisons, we first rank the n-grams in each experiment by their z-scores and compute Kendall's tau correlation between the Kickstarter vs.
 Amazon and Kickstarter vs.
@@
 The intuition behind this comparsion is as follows: if Kickstarter is more altruistic than Amazon, but less altruistic than GoFundMe, then we would expect altruistically-associated n-grams to be on opposite ends of each ranking.
-We compute rankings and correlation statistics for unigrams, bigrams, and trigrams seperately.
 
-For the 3391 unigrams, we find a negative correlation as expected, but the significance of this correlation could not be verified ($\rho = -.010, p = .55$).
-As we extend our analysis to more complex lingustic features such as bigrams and trigrams, which are less sensitive to unfiltered topical noise and likely carry more signal regarding the use of language, the negative correlation between these two rankings becomes more clear.
-For the 4195 bigrams, we see a significant negative correlation ($\rho = -.038, p < .02$) and for the 898 trigrams, we see a large significant negative correlation ($\rho = -.11, p < .002$).
+For all 2077 n-grams, we observe a statistically significant negative correlation between the rankings ($\tau = -.035, p = .016$).
+In addition, we compute rankings and correlation statistics for our 1119 unigrams, 1101 bigrams, and trigrams seperately.
+As we shift our focus from unigrams ($\tau = -.024, p = .23$) to bigrams ($\tau = -.038, p = .061$) to trigrams ($\tau = -.041, p < .01$) the negative correlation between the rankings both becomes greater and more significant.
+This is likely because more lingustic signal can be carried by phrases of increasing length.
 

### 2014-12-18 AltruisticLanguage/writing/paper.tex
writing

@@
 \title{Pre-orders or Philanthropy: An Analysis of Altruism on Kickstarter}
-\author{Jack Hessel \and Lillian Lee\\Cornell University}
+\author{Jack Hessel}
 \maketitle
@@
 of & -42.74 & to create & -20.17 & some of the & -8.26 &
-i & -525.09 & we are & -256.59 & tank you for & -112.63 \\\hline
+i & -525.09 & we are & -256.59 & thank you for & -112.63 \\\hline
 new & -26.01 & on the & -19.96 & will be a & -6.25 &
@@
 Each product is associated with a description and and a set of categories.
-Our dataset consists of just under 1.5M Amazon product descriptions \cite{mcauley2013hidden}.
+Our dataset consists of just over 1M Amazon product descriptions \cite{mcauley2013hidden}.
 We believe that Amazon product descriptions can be considered as purely commercial.
@@
 Recall that in each of our datasets, documents are associated with one or more categories.
-To control for topic, we extract all n-grams of interest that appear in some minimum proportion of all categories, as well as (optionally) a minimum number of times throughout the dataset.
-For each of our three datasets, we examine unigrams, bigrams, and trigrams, and choose such that each dataset is roughly equally represented.
-For our particular parameter filtrations, we derive 24K n-grams from Kickstarter, 24K n-grams from GoFundMe, and 28K n-grams from Amazon.
-Finally, an intersection of these sets provides the final 7K n-gram vocabulary of interest.
+In a first attempt to control for topic, we first apply a filter that removes all n-grams that don't appear in all categories at least once.
+We found this simple filtration scheme to be inadequate -- the words ``book,'' ``publisher,'' and ``author,'' for instance, appear very frequently in the Amazon dataset because about 78\% of the products in the Amazon dataset are tagged under the Book category.
 
+To apply a more stringent topic controlling filter after removing n-grams that don't appear in all categories, for each n-gram $n$, we compute the intra-category document frequency denoted $f_n^c$ for all categories $c$.
+We then compute the ``normalized width'' $w_n$ for n-gram $n$ as...
+
+\begin{equation} \label{eq:spread}
+w_n = \frac{\max\limits_{c'}f_n^{c'} - \min\limits_{c'}f_n^{c'}}{\max\limits_{c'}f_n^{c'}}
+\end{equation}
+
+The intuition behind normalized width is as follows -- if a word appears in all categories with roughly the same frequency, the normalized spread will be small.
+If a word appears very frequently in a single category, the normalized width will be large.
+After computing all normalized widths, we filter out the 10\% of n-grams with highest normalized width.
+
+After this two-part filtration scheme is applied to all three datasets, we take an intersection of the resulting n-grams to form our final vocabulary, which contains 2077 n-grams.
 The results of these analyses are summarized in Table \ref{tab:pairwise}.
+
+These rankings clearly illustrate the commecial language used on Amazon and the altruistic language used on GoFundMe, when compared to Kickstarter.
+For instance, the most Amazon-like unigrams, ``easy,'' ``includes,'' ``with,'' ``has,'' and ``perfect,'' are highly sales oriented, whereas the most Kickstarter-like n-grams are more focused on personal appeals and promise of future improvement.
+Conversely, even a coursory examinination of the trigrams in the GoFundMe versus Kickstarter analysis reveals clear differences in lingustic content.
+Project curators in the more altruistic setting are clearly more focused on personal appeals when compared to Kickstarter.
 
@@
 The intuition behind this comparsion is as follows: if Kickstarter is more altruistic than Amazon, but less altruistic than GoFundMe, then we would expect altruistically-associated n-grams to be on opposite ends of each ranking.
+This phenomenon occurs
 
@@
 Overall, we argue this analysis demonstrates that discourse on Kickstarter is neither entirely Amazon-like, nor entirely GoFundMe-like, but rather lies in its own lingustic regime at the intersection of altruism and commercialism.
-
 \section{What do Altruistic Requests Look Like?}
@@
 \footnotesize
-\begin{tabular}{|l|l|L{2.8cm}|}
+\begin{tabular}{|l|L{2.8cm}|}
 \hline
-Cluster Name & Number of Sentences & Top 3 Trigrams \\\hline
- & 551 & \specialcell{`one of the'\\`all of the'\\`is one of'} \\\hline
- & 275 & \specialcell{`is too small'\\`you can help'\\`you can give'} \\\hline
- & 288 & \specialcell{`thank you for'\\`you for your'\\`thank you so'}\\\hline
- & 1190 & \specialcell{`be able to'\\`to be able'\\`\# year old'}\\\hline
- & 708 & \specialcell{`to the hospital'\\`to the er'\\`him to the'}\\\hline
- & 457 & \specialcell{`to help with'\\`would like to'\\`and his family'}\\\hline
- & 641 & \specialcell{`in the hospital'\\`\# year old'\\`is in the'} \\\hline
- & 437 & \specialcell{`was diagnosed with'\\`my name is'\\`\# years old'} \\\hline
- & 498 & \specialcell{`we are asking'\\`are asking for'\\`family and friends'} \\\hline 
- & 334 & \specialcell{`be greatly appreciated'\\`will be greatly'\\`will be a'} \\\hline
- & 216 & \specialcell{`he is a'\\`he is in'\\`\# years old'} \\\hline
-Etcetera & 1520 & \specialcell{'to be a'\\`as well as'\\`to and from'} \\\hline
+Number of Sentences & Top 3 Trigrams \\\hline
+551 & \specialcell{`one of the'\\`all of the'\\`is one of'} \\\hline
+275 & \specialcell{`is too small'\\`you can help'\\`you can give'} \\\hline
+288 & \specialcell{`thank you for'\\`you for your'\\`thank you so'}\\\hline
+1190 & \specialcell{`be able to'\\`to be able'\\`\# year old'}\\\hline
+708 & \specialcell{`to the hospital'\\`to the er'\\`him to the'}\\\hline
+457 & \specialcell{`to help with'\\`would like to'\\`and his family'}\\\hline
+641 & \specialcell{`in the hospital'\\`\# year old'\\`is in the'} \\\hline
+437 & \specialcell{`was diagnosed with'\\`my name is'\\`\# years old'} \\\hline
+498 & \specialcell{`we are asking'\\`are asking for'\\`family and friends'} \\\hline 
+334 & \specialcell{`be greatly appreciated'\\`will be greatly'\\`will be a'} \\\hline
+216 & \specialcell{`he is a'\\`he is in'\\`\# years old'} \\\hline
+1520* & \specialcell{'to be a'\\`as well as'\\`to and from'} \\\hline
 \end{tabular}
-\caption{Clustering derived from the content model.}
+\caption{Clustering derived from the content model. The asterisk indicates the etcetera cluster.}
 \label{tab:contentmodel}
@@
 A content model is an unsupervized learning algorithm that operates on the sentence level, takes information order into account, and learns transition probabilities between sentence types.
-Here we provide a brief description of the content model, along with its basic goals and limitations.
+Here we provide a brief overview of the content model algorithm; for a fuller description, consult the original paper.
 
-BLAH
+The goal of a content model is to learn a set of sentence clusters utilizing ordering information.
+Given a set of $N$ documents where document $n$ has $s_n$ sentences, sentences are first clustered into $k$ groups according to bigram features using complete-link clustering with a cosine distance metric.
+After sentences are clustered into these groups, we merge all clusters smaller than some threshold into an ``etcetera'' cluster.
+This etcetera cluster is a unique feature of the content model that allows it the flexibility to sort sentences that otherwise don't fit into an ``other'' cluster.
+After this merging process, we are left with $m$ clusters.
+
+For each of the resulting non-etcetera clusters, we train a smoothed bigram language model which is able to assign probabilities to input sentences.
+For the etcetera cluster, we train a ``complentary'' language model which assigns high probability to sentences that all other language models assign low probability to.
+
+After training these language models, we now treat each clustering as a state in a Hidden Markov Model, and all input documents as emissions from that Hidden Markov Model.
+We are able to compute the Viterbi path for each document, and we re-cluster sentences based on these most-likely paths.
+Finally, we retrain each of the language models based on the new clustering.
+This process of re-clustering, computing Viterbi paths, and re-training language models in an expectation maximization like fashion is executed until
 
@@
 We utilize 11 content clusters and 1 etcetera cluster in our model.
-After our expectation maximization converged, we were left with the clusters displayed in Table \ref{tab:contentmodel}.
+Though the original literature sugguests a larger number of clusters (30+) we opt for a smaller, interpretable analysis because our resulting model was not used for any information ordering or information extraction tasks, as in \cite{barzilay2004catching}.
+After our expectation maximization converged, we were left with the order-aware sentence clusters displayed in Table \ref{tab:contentmodel}.
 
@@
 The response variable is defined as follows: if a project recieves any donations and the proportion of altruistic donations it recieves exceeds $10\%$, we assign it to the altruistic group, otherwise, it is assigned to the non-altruistic group.
-Defining this control variable partitions the dataset into 26733 altruistic projects and 19077 projects giving a constant prediction baseline of 58.34\% accuracy.
+Defining this control variable partitions the dataset into 26733 altruistic projects and 19077 non-altruistic projects giving a constant prediction baseline of 58.34\% accuracy.
 

### 2014-12-18 AltruisticLanguage/failSucc.py
writing

@@ -1,0 +1,10 @@
+from KickstarterParser import *
+from EDA import loadProjects
+
+def main():
+    projects = loadProjects('output')
+    projects = [p for p in projects if len(p.category) != 0]
+    print len(projects)
+
+if __name__ == "__main__":
+    main()

### 2014-12-19 AltruisticLanguage/writing/paper.tex
updated wriiting

@@
 \usepackage{graphicx}
+\usepackage{amsmath}
+\usepackage{graphicx}
+\usepackage{subfig}
 \newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
@@
 %
-\title{Pre-orders or Philanthropy: An Analysis of Altruism on Kickstarter}
+\title{Pre-orders or Philanthropy: An Analysis of Altruism on Kickstarter and Other Crowdfunding Sites}
 \author{Jack Hessel}
@@
 
-\section{Previous Work}
+\section{Primary Dataset}
 
@@
 In contrast to Kickstarter, in a vast majority of cases GoFundMe contributors don't have the option to select compensentory rewards, and we therefore regard our GoFundMe data as requests for purely altruistic actions.
+As a general preprocessing step, in all of our analyses we remove punctuation from strings, and convert all characters to lower case.
 
@@
 
-\begin{equation} \label{eq:spread}
+\begin{equation} \label{eq:width}
 w_n = \frac{\max\limits_{c'}f_n^{c'} - \min\limits_{c'}f_n^{c'}}{\max\limits_{c'}f_n^{c'}}
@@
 
-The intuition behind normalized width is as follows -- if a word appears in all categories with roughly the same frequency, the normalized spread will be small.
+The intuition behind normalized width is as follows -- if a word appears in all categories with roughly the same frequency, the normalized width will be small.
 If a word appears very frequently in a single category, the normalized width will be large.
@@
 \footnotesize
-\begin{tabular}{|l|L{2.8cm}|}
+\begin{tabular}{|l|L{4cm}|}
 \hline
-Number of Sentences & Top 3 Trigrams \\\hline
-551 & \specialcell{`one of the'\\`all of the'\\`is one of'} \\\hline
-275 & \specialcell{`is too small'\\`you can help'\\`you can give'} \\\hline
-288 & \specialcell{`thank you for'\\`you for your'\\`thank you so'}\\\hline
-1190 & \specialcell{`be able to'\\`to be able'\\`\# year old'}\\\hline
-708 & \specialcell{`to the hospital'\\`to the er'\\`him to the'}\\\hline
-457 & \specialcell{`to help with'\\`would like to'\\`and his family'}\\\hline
-641 & \specialcell{`in the hospital'\\`\# year old'\\`is in the'} \\\hline
-437 & \specialcell{`was diagnosed with'\\`my name is'\\`\# years old'} \\\hline
-498 & \specialcell{`we are asking'\\`are asking for'\\`family and friends'} \\\hline 
-334 & \specialcell{`be greatly appreciated'\\`will be greatly'\\`will be a'} \\\hline
-216 & \specialcell{`he is a'\\`he is in'\\`\# years old'} \\\hline
-1520* & \specialcell{'to be a'\\`as well as'\\`to and from'} \\\hline
+Number of Sentences & Top 5 trigrams \\\hline
+178 & \specialcell{`would be greatly appreciated'\\`as you can imagine'\\`donation is too small'\\`no donation is too'\\`you can to help'}\\\hline
+254 & \specialcell{`thank you for your'\\`thank you so much'\\`for taking the time'\\`the time to read'\\`taking the time to'}\\\hline
+356 & \specialcell{`to be able to'\\`not be able to'\\`will be able to'\\`be able to work'\\`will not be able'}\\\hline
+192 & \specialcell{`to go to the'\\`to the er and'\\`back to the hospital'\\`rushed to the hospital'\\`go to the hospital'}\\\hline
+275 & \specialcell{`we are asking for'\\`are asking for help'\\`our friends and family'\\`my family and i'\\`help raise money for'}\\\hline
+243 & \specialcell{`in the middle of'\\`the middle of the'\\`a \# year old'\\`in the hospital and'\\`middle of the night'}\\\hline
+272 & \specialcell{`was diagnosed with stage'\\`diagnosed with stage \#'\\`she was diagnosed with'\\`has been diagnosed with'\\`was diagnosed with a'}\\\hline
+255 & \specialcell{`is one of the'\\`one of the most'\\`find it in your'\\`for all of the'\\`it in your heart'}\\\hline
+181 & \specialcell{`will be greatly appreciated'\\`will be a long'\\`long road to recovery'\\`update NAME had chemo'\\`him and his family'}\\\hline
+224 & \specialcell{`to help with medical'\\`will go directly to'\\`to raise money for'\\`during this difficult time'\\`if you would like'}\\\hline
+104 & \specialcell{`he is able to'\\`he is in a'\\`fighting for his life'\\`a good fight and'\\`of you may not'}\\\hline
 \end{tabular}
-\caption{Clustering derived from the content model. The asterisk indicates the etcetera cluster.}
+\caption{11 content clusters derived from the content model.}
 \label{tab:contentmodel}
@@
 Finally, we retrain each of the language models based on the new clustering.
-This process of re-clustering, computing Viterbi paths, and re-training language models in an expectation maximization like fashion is executed until
+This process of re-clustering, computing Viterbi paths, and re-training language models in an expectation maximization like fashion is executed until convergence or a maximum number of iterations is made.
 
@@
 Though the original literature sugguests a larger number of clusters (30+) we opt for a smaller, interpretable analysis because our resulting model was not used for any information ordering or information extraction tasks, as in \cite{barzilay2004catching}.
-After our expectation maximization converged, we were left with the order-aware sentence clusters displayed in Table \ref{tab:contentmodel}.
+After our expectation maximization converged after nine iterations, we were left with the order-aware sentence clusters displayed in Table \ref{tab:contentmodel} (etcetera cluster omitted).
 
@@
 \end{table}
+
 How does altruism manifest on Kickstarter?
@@
 The response variable is defined as follows: if a project recieves any donations and the proportion of altruistic donations it recieves exceeds $10\%$, we assign it to the altruistic group, otherwise, it is assigned to the non-altruistic group.
-Defining this control variable partitions the dataset into 26733 altruistic projects and 19077 non-altruistic projects giving a constant prediction baseline of 58.34\% accuracy.
+We can interpret this binary variable as ``recieved more than an average number of altruistic donations.'' Defining this control variable partitions the dataset into 26733 altruistic projects and 19077 non-altruistic projects giving a constant prediction baseline of 58.34\% accuracy.
 
@@
 glmnet is a software package that implements cyclic coordinate decent and is capable of performing penalized regression tasks on highly sparse datasets.
-For our experiments, we utilize an $L_1$ (lasso) regularization term in an attempt to enforce sparsity and derive a parsimonious model, and set glmnet to perform 10-fold cross validation to search for the optimal regularization coefficient.
+For our experiments, we utilize an $L_1$ (lasso) regularization term in an attempt to enforce sparsity and derive a parsimonious model, and set glmnet to perform 10-fold cross validation to search for the optimal regularization coefficient and prevent overfitting.
+In addition to training a model on all the data, as a seperate measure we also report test accuracy when spliting our data into a 40k project training set and a 5k project test set.
 Notably, glmnet purposefully does not report standard errors on resulting feature coefficients because the regularization process intorudces substantial bias into the regression process.
 
-Our best controls only logistic regression model had a cross-validation accuracy of 64.42\%, improving upon our constant prediction baseline by 6.08\%.
+Using a model consisting of controls only, we achieve a cross-validation accuracy of 64.53\% (6.19\% improvement over constant prediction) and a testing set accuracy of 63.80\% (5.46\% improvement).
 The most important positive and negative predictive features were all Kickstarter category control variables.
-Dance, theater, public art, performance art, and classical music ($\vec{\beta} = \langle 1.84, 1.56, 1.24, 1.04, .930 \rangle$, respectively) were the categorical variables which were the strongest positive predictors, whereas board/card games, games, comics, video games, and product design ($\vec{\beta} = \langle -1.64, -1.23, -1.02, -.862, -.795 \rangle$, respectively) were the strongest negative predictors.
+Dance, theater, public art, performance art, and classical music ($\vec{\beta} = \langle 1.84, 1.56, 1.24, 1.04, .930 \rangle$, respectively) were the categorical variables which were the strongest positive predictors, whereas board/card games, games, comics, video games, and product design ($\vec{\beta} = -\langle 1.64, 1.23, 1.02, .862, .795 \rangle$, respectively) were the strongest negative predictors.
 This result indicates that product category is the most important factor in determining if a project will recieve altruistic donations, and perhaps that projects in artistic categories are more likely to recieve such Kickstarter backing.
-This result is fairly unsurprising -- artistic endevours are generally regarded as intrinsically valuable to society (CITECITECITE), and the negatively predictive categories tend to have concretely associated products with their projects (a video game, for instance).
-Some non-categorical positive predictors included
+This result is fairly unsurprising -- artistic endevours are generally regarded as intrinsically valuable to society, as evidenced by the existance of organizations like the National Endowment of the Arts which has, to date, awarded more than 5B dollars for artistic endevours\footnote{\url{http://arts.gov/about-nea}}.
+The negatively predictive categories tend to have concretely associated products with their projects (a video game, for instance) and backers likely pre-order instead of donate, in general.
 
+The most important non-categorical positive predictor was having a video (binary variable, $\beta = .45$).
+On the other hand, being featured (binary variable, $\beta = -.183$) and having many comments on a project (interger variable, $\beta = -.00168$) were associated with less altruistic donations.
+
+\begin{table}[t]
+\centering
+\begin{tabular}{|l|l|}
+\hline
+Positive Predictors & Negative Predictor \\
+\hline
+universitys, .377 & people that are, -.384 \\
+the challenge of, .308 & we going, -.348\\
+so exciting, .296 & with international, -.278\\
+at the park, .293 & can walk, -.271\\
+taken off, .292 & ground the, -.260\\
+my senior, .284 & complement, -.259\\
+whatever you can, .277 & get in on, -.253\\
+to austin, .252 & 20 you, -.227\\
+to maintain a, .243 & must make, -.217\\
+500 you will, .238 & my website at, -.212\\
+underserved, .232 & use one, -.209 \\
+way your, .232 & other ways you, -.204\\
+recipient of, .230 & so we know, -.193\\
+small portion of, .226 & this project it, -.191\\
+was chosen, .224 & and rare, -.188\\
+\hline
+\end{tabular}
+\caption{The top 15 positive and negative lingustic predictors of the binary variable ``did this project recieve an above average proportion of altruistic donations'' in the controls + n-grams model.}
+\label{tab:regression}
+\end{table}
+
+Does accounting for linguistic content of a project increase our predictive accuracy?
 Our textual features consist of binary indicator variables for unigrams, bigrams, and trigrams in the project descriptions, FAQ question/answers, and reward descriptions of our Kickstarter projects.
-We apply both a category filter and a variance filter to determine our resulting n-gram set.
-Our category filter requires all n-grams to appear in all 49 categories.
-For our variance filter, we consider the usage of a given n-gram over all categories, and compute the variance of the resulting multinomial distribution.
-Finally, we remove from consideration the most variable 25\% of n-grams.
-Applying this two-part filtration process, we end up with 30784 category and variance filtered n-grams.
+We apply the same two-part filter that we use in our previous analysis to determine a set of topic-free n-grams, which forces selected n-grams to appear in every Kickstarter category and be relatively uniformly distributed between them (see Equation \ref{eq:width}).
+Applying this two-part filtration process on our Kickstarter dataset exclusively, we end up with 31281 filtered n-grams.
 
-The goal of this filtration process is to produce a set of n-grams that are independent of topic.
-For instance, because the term ``art project'' is used significantly more readily in artistic Kickstarter categories, its significance in regression is more topically meaningful than lingustically meaningful, as the corresponding covariate is highly colinear with the artistic category indicator variables.
+When we incorporate these particular lingustic features, our cross-validation accuracy increases to 67.02\% (2.49\% improvement over controls-only baseline) and our testing accuracy increases to 66.68\% (2.88\% improvement).
+The inclusion of lingustic features, therefore, causes our predictive accuracy to increase slightly but significantly.
 
-When we incorporate these particular lingustic features, our cross-validation accuracy XXXXX.
+Which n-grams are most predictive of greater-than-average donation frequency?
+The top 15 most significant positive and negative predictive lingustic features along with their corresponding regression coefficients are displayed in Table \ref{tab:regression}.
 
+Are there any discernable patterns among these n-grams?
+\begin{figure*}[hb]
+\centering
+\subfloat{
+  \includegraphics[width=.3\textwidth]{figures/Musicevents.png}
+}
+\subfloat{
+  \includegraphics[width=.3\textwidth]{figures/FilmVideoevents.png}
+}
+\subfloat{
+  \includegraphics[width=.3\textwidth]{figures/Artevents.png}
+}
+\hspace{0mm}
+\subfloat{
+  \includegraphics[width=.3\textwidth]{figures/Musicvals.png}
+}
+\subfloat{
+  \includegraphics[width=.3\textwidth]{figures/FilmVideovals.png}
+}
+\subfloat{
+  \includegraphics[width=.3\textwidth]{figures/Artvals.png}
+}
+\caption{Top row: event-based altruism distribution.
+x-axis represents the proportion of all donation events where contributors selected ``no reward'' when compared to all donation events for a project.
+Bottom row: dollar value-based altruism distribution.
+x-axis represents the proportion of all money raised that was given above-and-beyond the required value of the claimed rewards, when compared to the total amount raised for a given project.
+For both rows, dotted lines indicate means for successful and unsuccessful projects.
+The three columns represent projects from the most popular categories, ``Music,'' ``Film and Video,'' and ``Art,'' though similar patterns often emerge in categories like ``Technology'' and ``Games.''}
+\label{fig:failsuccgraphs}
+\end{figure*}
 \section{Failing Projects, More Donations?}
+What is the relationship between project success and the proportion of altruistic donations a project recieves?
+One might reasonably expect that successful projects, having higher quality pitches and commanding more donations on average, would also have a higher proportion of altruistic donations.
+In fact, the conclusions based on the analysis in this section find the \emph{opposite} to be true -- we find that, in fact, that there is a consistent negative association between project success and proportion of altruistic donations recieved.
 
-\begin{figure*}
-\centering
-\includegraphics[width=.9\textwidth]{figures/failSuccess.png}                         
-\caption{temp}
-\label{fig:succfail}
-\end{figure*}
+To address this question, we first run a new lasso penalized regression task where predictive variables consist of the control variables highlighted in Table \ref{tab:controls} plus two additional binary variables ``success,'' which indicates whether or not the funding goal of the project was reached, and ``numBackers,'' the total number of backers for a given project.
+The target of this new regression is the proportion of altruistic donations a project recieves.
+Because our target is a ratio that is highly sensitive to noise if the number of project backers is small, we restrict our consideration to the 30858 projects in our dataset with 10 or more backers (though the results presented here are robust to reasonable changes in this threshold).
+
+Surprisingly, our resulting regression assigns negative weights to both our new predictive variables.
+With respect to the number of backers, the negative weight assigned to this variable indicates that more popular projects are less likely to recieve altruistic donations, in general.
+More surprising, however, is that after controling for all variables in Table \ref{tab:controls} and project size, successful projects recieve \emph{less} altruistic donations than unsuccessful projects.
+
+To further investigate this result, we split all projects with more than ten backers into the 13 main categories on Kickstarter\footnote{Our previous analysis mentioned 49 categories, but this division takes into account subcategories of the main categories.
+For this analysis, we use only the main categories.}.
+Next, we compute the distribution of two statistics for each category: the proportion of altruistic donation events (i.e.
+the number of times a backer selected the ``no reward'' option divided by the total number of backers) and the proportion of total project funding resulting from above-and-beyond contribution which is given by
+\begin{equation} \label{eq:altruism}
+\frac{\sum\limits_{x \in \text{ Rewards of $p$}} \text{Backers}(x) \cdot \text{Cost}(x)}
+{\text{Amount Raised}(p)}
+\end{equation}
+for some project $p$.
+
+For the event donation frequencies, there is a clear pattern: in 12 of the 13 Kickstarter categories (the exception being ``Food'') failing projects recieve a higher proportion of altruistic donations, on average.
+In seven of the thirteen categories, this result is significant at the 5\% level.
+For categories with large numbers of projects, this result is often highly significant.
+For instance, in the two most popular Kickstarter categories, ``Music'' and ``Film and Video,'' we observe a that failed projects recieve, on average, significantly more altruistic donation events (Student's t-test, $p<<.001$ in both cases).
+Sample plots of the event distributions are presented in the first row of Figure FIG.
+
+When we change the focus of our analysis from events to dollar values, however, this pattern becomes less apparent, or reverses altogether.
+In the ``Film and Video'' category, for instance, we observe a total reversal, a significant result ($p << .001$) that states successful projects receive more dollars altruistically than failed projects.
+In the ``Music'' category, the test statistic is close to zero,  In fact, over all categories all statistically significant results ( state that successful projects.
+Sample plots of the dollar value distributions are presented in the second row of Figure FIG.
+
+What does this discrepency between events and dollar value mean?
+We suspect that the many significant results for our event-based analysis indicate that, indeed, failing projects recieve, on average, more altruistic donation events.
+However, the value of these donations is likely small, as many of these results don't hold when actual dollar values are considered.
+
+We believe that this result sugguests the following scenario is common across many categories: a Kickstarter user observes that a project is failing and makes a small donation, but requests no reward.
+It has been shown that feelings of sympathy can elicit prosocial behavior, even if the interaction can be easily avoided, as it would be by anonymously closing a browswer window \cite{eisenberg1989relation}.
+If the cost of such an altruistic action is too high, however, it has a lower probability of being taken \cite{batson1983influence}.
+Though an assignment of altruistic donations to values directly would be valuable to our analysis, given the data that Kickstarter makes public, there is no way to directly compute the value of the altruistic donation events themselves, and we leave a more detailed analysis to future work on a seperate dataset.
+
+Our hypothesis regarding low-cost donations fits very well into the framework established by previous psychological studies, assuming that feelings of sympathy are the driving force behind donation to failing projects.
+The existance and popularity of website entitled KickEnded\footnote{\url{http://kickended.com/about}} lends crediability to this theory.
+On KickEnded, finished Kickstarter projects with zero backers are archived so that they may ``live a second life...
+free from the pressure of money raising.'' The notion that commercial success does not equate to societial value is a highly sympathetic one.
+Though this evidence is rather indirect, it is a fairly strong indicator of the dynamics underlying our data.
+
+Assuming our hypothesis is correct, several interesting questions arise.
+Who are these low-cost altruistic donators?
+Are their motiviations sympathetic, as the psychology literature and Kickended's popularity sugguest?
+Are there sub-communities of altruistic users?
+Are there community-derived benefits to making altruistic donations on Kickstarter?
+These specific questions would be best answered by Kickstarter users themselves; interesting future work might include questionaires sent out to a specifically targeted user base.
 
 \section{Conclusion}
+
+Here, we presented several analyses relating to altruistic behavior on crowdfunding sites with a focus on language.
 

### 2014-12-19 AltruisticLanguage/Comparison/addPrior.py
update

@@ -1,13 +1,11 @@
 import sys
 
-def main():
-    '''Command line argument should be [input file] [prior] [output file]'''
-    with open(sys.argv[-1], 'w') as out:
-        with open(sys.argv[1]) as fileIn:
-            writeStr = ""
-            for line in fileIn:
-                writeStr += line.strip() + ":" + sys.argv[2] + "\n"
-            out.write(writeStr[:-1])
+myFile = open(sys.argv[1])
+outFile = open(sys.argv[2], 'w')
+prior = .01
 
-if __name__ == "__main__":
-    main()
+for line in myFile:
+    outFile.write(line.strip() + ":" + str(prior) + "\n")
+
+myFile.close()
+outFile.close()

### 2014-12-19 AltruisticLanguage/Comparison/rankingCompare.py

@@ -1,38 +1,59 @@
-from scipy.stats import spearmanr as spr
 import matplotlib.pyplot as plt
+import numpy as np
+import scipy.stats as sp
+from collections import Counter, defaultdict
 
-file1 = "GFMvKSSW.result"
-file2 = "KSvAMASW.result"
-
-ngramToID = {}
+file1 = "newNGrams/GFMvsKSSW.result"
+file2 = "newNGrams/AMAvsKSSW.result"
 
 rank1 = []
 rank2 = []
 
+ngrams = []
+
+skip = 4
+
+nGramCounter = Counter()
+ngramToVal = {}
+ngrams = []
+orderedNGram = defaultdict(list)
 with open(file1) as f:
-    curId = 0
     for line in f:
         if len(line) == 0: continue
         tokens = line.split()
         nGram = ' '.join(tokens[:-1])
-        if len(tokens) != 4: continue
-        ngramToID[nGram] = curId
-        rank1.append(curId)
-        curId += 1
+        if skip is not None:
+            if len(tokens) == skip: continue
+        orderedNGram[len(tokens)].append((nGram, float(tokens[-1])))
+        ngramToVal[nGram] = float(tokens[-1])
+        ngrams.append(nGram)
 
-idToNgram = {i:n for n,i in ngramToID.iteritems()}
-
+orderedNGram = defaultdict(list)
+ngramToVal2 = {}
 with open(file2) as f:
     for line in f:
         if len(line) == 0: continue
         tokens = line.split()
-        if len(tokens) != 4: continue
         nGram = ' '.join(tokens[:-1])
-        rank2.append(ngramToID[nGram])
+        if skip is not None:
+            if len(tokens) == skip: continue
+        orderedNGram[len(tokens)].append((nGram, float(tokens[-1])))
+        ngramToVal2[nGram] = float(tokens[-1])
 
-print [idToNgram[x] for x in rank1[:10]]
-print [idToNgram[x] for x in rank2[:10]]
+print len(ngrams)
 
-print len(rank1)
-print len(rank2)
-print spr(rank1, rank2)
+#for i in [2,3,4]:
+#    print i
+#    for x in orderedNGram[i][:5]:
+#        print x
+#    print
+#    for x in orderedNGram[i][-5:]:
+#        print x
+
+
+
+rank1 = [ngramToVal[n] for n in ngrams]
+rank2 = [ngramToVal2[n] for n in ngrams]
+
+tau, p_value = sp.stats.kendalltau(rank1, rank2)
+print tau, p_value

### 2014-12-19 AltruisticLanguage/ContentModel/ContentModel.py

@@ -19,7 +19,7 @@ class ContentModel:
                  numClusters = 1275,
                  minProportion = .007,
                  clusterTrainProp = 1, 
-                 d1 = .00001,
+                 d1 = .00000005,
                  d2 = .001,
                  cleanSents = None,
                  saveFile = None):

### 2014-12-19 AltruisticLanguage/ContentModel/Interpret.py

@@ -17,19 +17,22 @@ def interpretClusters(clusterFileName):
             else:
                 clusterMap[curCluster].append(line.strip())
 
-    for cluster, sents in clusterMap.iteritems():
-        print cluster, len(sents)
+    #for cluster, sents in clusterMap.iteritems():
+    #    print cluster, len(sents)
     
     for cluster, sents in clusterMap.iteritems():
+        if cluster == -1: continue
         counts = Counter()
         for s in sents:
-            counts.update(set(getNGrams(s,n=3)))
+            counts.update(set(getNGrams(s,n=4)))
         topTen = sorted(counts.iteritems(), key=operator.itemgetter(1))[::-1][:20]
-        print cluster
-        for s in sents:
-            if 'in the hospital' in s:
-                pass#print s
-        print topTen
+        #print cluster
+        string = str(len(sents)) + ' & \specialcell{'
+        for i in range(5):
+            string += '`' + topTen[i][0].replace('numnumnumnum', '\#') + '\'\\\\'
+        string = string[:-2]
+        string += '}\\\\\\hline'
+        print string
 
 def interpretPaths(pathsFile):
     docSents = defaultdict(list)
@@ -118,23 +121,6 @@ def interpretPaths(pathsFile):
         #    plt.plot([heightMap[s] for s in seq])
         #plt.savefig(str(length) + ".png")
         #plt.figure()
-
-
-def getClusterNamesOrdering():
-    returnDict = {}
-    returnDict[636] = ('Personal Description',1)
-    returnDict[1222] = ('You Can Help',7)
-    returnDict[588] = ('Thank You',11)
-    returnDict[76] = ('Lack of Ability',5)
-    returnDict[158] = ('Use of Money',9)
-    returnDict[633] = ('Introduction', 0)
-    returnDict[314] = ('Diagnosis', 4)
-    returnDict[156] = ('Request', 8)
-    returnDict[154] = ('Appreciation',9)
-    returnDict[309] = ('Personal Story',2)
-    returnDict[78] = ('Hospital/Emergency Room',3)
-    returnDict[-1] = ('ETC',6)
-    return returnDict
     
 def getNGrams(stringIn, n=2):
     tokens = stringIn.split()
@@ -142,10 +128,9 @@ def getNGrams(stringIn, n=2):
     for i in range(len(tokens)-n+1): returnList.append(' '.join(tokens[i:i+n]))
     return returnList
 
-
 def main():
[…]

### 2014-12-19 AltruisticLanguage/EDA.py

@@ -53,10 +53,6 @@ def getProjectsOfCategory(category, allProjects):
 
     return returnList
 
-def getCategories(projects):
-    return set([x.category for x in projects])
-
-
 def printGroupStatistics(projects):
     cats = getCategories(projects)
     
@@ -73,6 +69,9 @@ def printGroupStatistics(projects):
                                                       len(catProjects),
                                                       succRatio,
                                                       aveRaised)
+
+def getCategories(projects):
+    return set([x.category for x in projects])
 
 def getSeedPhrases():
     return ['gratitude', 'your name', 'counts', 'access', 'personal', 'mention', 'thank you']
@@ -464,25 +463,7 @@ def extractTextFeatures(projects, minOccur = 50, nGram = 3, counts=False):
                   sorted(gramToVar.items(), key = operator.itemgetter(1))[:int(.9*len(gramToVar))]]
 
     
-    #print "Using {} n-grams".format(len(validGrams))
-    #with open('kickstarterSW.ngrams','w') as f:
-    #    words = ""
-    #    for v in validGrams:
-    #        words += v + "\n"
-    #    f.write(words[:-1])
-
-
-    #validGrams = [v for v in validGrams if not
-    #              set.issubset(set(v.split()), set(stopwords.words('english')))]
-
-    #print "Using {} n-grams".format(len(validGrams))
-    #with open('kickstarter.ngrams','w') as f:
-    #    words = ""
-    #    for v in validGrams:
-    #        words += v + "\n"
-    #    f.write(words[:-1])
-
-    #quit()
+    print "Using {} n-grams".format(len(validGrams))
 
     returnMatrix = np.zeros([len(projects),len(validGrams)], dtype = np.float32)
     for i in range(len(projects)):

### 2014-12-19 AltruisticLanguage/GoFundMe/GoFundMeParser.py

@@ -11,6 +11,7 @@ import string
 from collections import Counter, defaultdict
 from nltk.corpus import stopwords
 import numpy as np
+import operator
 
 class GFMProject:
     def __init__(self):
@@ -108,10 +109,11 @@ def loadProjects(pickleDir):
 
 def extractTextFeatures(projects, minOccur = 10, nGram = 3):
     '''Given a list of projects, a minimum number of occurances, and maximum sized n-gram of interest, return a |projects| x |features| n-gram count matrix and list of n-grams in the order represented, given that the selected features appear in a least minOccur projects and at least once in every category.'''
-    #dict mapping from category -> set of n grams in that category
-    catGramDict = defaultdict(set)
-    #counter mapping from n-gram -> count
+
+    gramCatCounter = defaultdict(lambda: Counter())
     nGramCounter = Counter()
+    catCounter = Counter()
+    catGramDict = defaultdict(set)
 
     myGramFun = lambda x,y: getNGrams(x, y, toLower = True, removePunct = True)
 
@@ -121,15 +123,42 @@ def extractTextFeatures(projects, minOccur = 10, nGram = 3):
             nGrams = myGramFun(p.text, n)
             for g in nGrams:
                 nGramCounter[g] += 1
+                gramCatCounter[p.category][g] += 1
             catGramDict[p.category].update(set(nGrams))
+            catCounter[p.category] += 1
 
-    validGrams = [x for x in proportionalIntersection(catGramDict.values(), proportion=.50)
+    validGrams = [x for x in proportionalIntersection(catGramDict.values(), proportion=1)
                   if nGramCounter[x] > minOccur]
     print len(validGrams)
+    print catCounter
+
+    gramToVar = {}
+    i = 1
+    print "Filtering..."
+    for v in validGrams:
+        if i % 1000 == 0: print i
+        perDocList = []
+        for cat, catCount in catCounter.iteritems():
+            perDocList.append((gramCatCounter[cat][v]*.1)/catCount)
+        gramToVar[v] = 1.0*(np.max(perDocList)-np.min(perDocList))/np.max(perDocList)
+
+    validGrams = [x[0] for x in
+                  sorted(gramToVar.items(), key = operator.itemgetter(1))[:int(.9*len(gramToVar))]]
+    
+    with open('gfm90SW.ngrams','w') as f:
+        words = ""
+        for v in validGrams:
+            words += v + "\n"
+        f.write(words[:-1])
+
[…]

### 2014-12-19 AltruisticLanguage/GoFundMe/GoFundMeScraper.py

@@ -56,7 +56,5 @@ def main():
             with open(curDir + str(i) + '.html', 'w') as f:
                 f.write(htmlText)
             
-            
-
 if __name__ == "__main__":
     main()

### 2014-12-19 AltruisticLanguage/failSucc.py

@@ -1,10 +1,156 @@
 from KickstarterParser import *
 from EDA import loadProjects
+from collections import defaultdict, Counter
+from scipy.stats import chi2_contingency
+import matplotlib.pyplot as plt
+from scipy.stats import ttest_ind as ttest
+import numpy as np
+
+def categoryValueTest(projects):
+    catDict = buildCategoryDictionary(projects)
+    #subcatDict = buildSubCategoryDictionary(projects)
+    #catDict = dict(catDict.items()) + subcatDict.items())
+    for cat, projectList in catDict.iteritems():
+        if len(cat) == 0: continue
+        success = [x for x in projectList if x.result and x.backers >= 10]
+        fail = [x for x in projectList if not x.result and x.backers >= 10]
+        sucAltRatio = [1.-(1.0*sum([y.numBackers for y in x.rewards]))/x.backers for x in success]
+        failAltRatio = [1.-(1.0*sum([y.numBackers for y in x.rewards]))/x.backers for x in fail]
+        sucAltRatioVals = [1.-(1.0*sum([y.numBackers*y.cost for y in x.rewards]))/x.raised
+                       for x in success]
+        failAltRatioVals = [1.-(1.0*sum([y.numBackers*y.cost for y in x.rewards]))/x.raised
+                       for x in fail]
+        bins = [(x*1.)/100 for x in range(1,100)]
+        plt.hist(sucAltRatio, bins, alpha=0.5,
+                 color = 'g', label='Success, N=' + str(len(sucAltRatio)),
+                 normed = True)
+        plt.hist(failAltRatio, bins, alpha=0.5,
+                 color = 'b', label='Failure, N='+str(len(failAltRatio)),
+                 normed = True)
+        plt.axvline(x=np.mean(sucAltRatio),linewidth=4, color='g', ls = '--')
+        plt.axvline(x=np.mean(failAltRatio),linewidth=4, color='b', ls = '--')
+        plt.legend(loc='upper right', fontsize=18)
+        plt.title(cat, fontsize=18)
+        plt.xlabel("Proportion Altruistic", fontsize=18)
+        plt.savefig("catGraphs/" + cat + "events.png")
+        plt.close()
+
+        plt.hist(sucAltRatioVals, bins, alpha=0.5,
+                 color = 'g', label='Success, N=' + str(len(sucAltRatio)),
+                 normed = True)
+        plt.hist(failAltRatioVals, bins, alpha=0.5,
[…]

### 2014-12-19 AltruisticLanguage/regressionFinal.R

@@ -4,18 +4,25 @@ library('glmnet')
 library('foreach')
 library('doParallel')
 registerDoParallel()
-
-topK <- 50
 rsort <- function(x) {
   sort(x, decreasing = TRUE)
 }
-
-data <- readMM("all90Filter.mtx")
-headers <- read.csv("allHeaders90Filter.csv")
+setwd("regressionData")
+dataSW <- readMM("all90Filter.mtx")
+headersSW <- read.csv("allHeaders90Filter.csv")
+dataNoSW <- readMM("all90FilternoSW.mtx")
+headersNoSW <- read.csv("allHeaders90FilternoSW.csv")
 dataControl <- readMM("allControls.mtx")
 headersControl <- read.csv("allControlHeaders.csv")
-colnames(data) <- colnames(headers)
+setwd("..")
+
+colnames(dataSW) <- colnames(headersSW)
+colnames(dataNoSW) <- colnames(headersNoSW)
 colnames(dataControl) <- colnames(headersControl)
+
+dataControlTest2 <- dataControl[which(dataControl[,c("numBackers")]>=20),]
+target2 <- dataControl[which(dataControl[,c("numBackers")]>=20),c("numBackers", "numAltruistic")]
+target2 <- target2[,2]/target2[,1]
 
 target <- dataControl[,c("numBackers", "numAltruistic")]
 target <- target[,2]/target[,1]
@@ -27,26 +34,39 @@ control <- cv.glmnet(dataControl[,-which(colnames(dataControl) %in% c("numBacker
               type.measure = "class",
               alpha = 1, parallel = T)
 
-all <- cv.glmnet(data[,-which(colnames(data) %in% c("numBackers","numAltruistic", "Osuccess"))], target,
+noSW <- cv.glmnet(dataNoSW[,-which(colnames(dataNoSW) %in% c("numBackers","numAltruistic", "Osuccess"))], target,
                 family = "binomial",
                 type.measure = "class",
                 alpha = 1, parallel = T)
 
+SW <- cv.glmnet(dataSW[,-which(colnames(dataSW) %in% c("numBackers","numAltruistic", "Osuccess"))], target,
+                family = "binomial",
+                type.measure = "class",
+                alpha = 1, parallel = T)
 
-holdoutAll <- cv.glmnet(data[1:40000,-which(colnames(data) %in% c("numBackers","numAltruistic", "Osuccess"))],
[…]

### 2014-12-19 AltruisticLanguage/writing/paper.tex
more writing

@@
 \newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
+\newenvironment{blockquote}{%
+  \par%
+  \setlength{\parskip}{.5em}
+  \small
+  \medskip
+  \leftskip=3em\rightskip=3em%
+  \noindent\ignorespaces}{%
+  \par\medskip}
 \newcommand{\specialcell}[2][l]{%
@@
 Are there any discernable patterns among these n-grams?
-\begin{figure*}[hb]
+An examination of the most positive-predicting linguistic features reveals that the advertisement of academic affiliation is a strong predictor of recieving a higher-than-average number of altruistic donations.
+The usage of ``universitys'' and ``my senior,'' in particular illustrate this point.
+\begin{blockquote}
+The AcaBelles are Florida State \textbf{University's} premier all-female a cappella group\ldots\par\noindent
+This is \textbf{my senior} thesis film at Pacific Union College\ldots\par\noindent
+\end{blockquote}
+Based on this analysis, it's reasonable to state that the Kickstarter community is more likely to give to students without requesting any rewards in return.
+
+Furthermore, positive sentiment and language that indicates the author's excitement about the project (``so exciting,'' ``the challenge of,'' ``taken off'') appears to positively predict donation.
+\begin{blockquote}
+This is about to get \textbf{so exciting} for the IBP! \par\noindent
+We developed more recipes and got excited about \textbf{the challenge of} using whole foods\ldots\par\noindent
+Podcasting has really \textbf{taken off} in the past year\ldots
+\end{blockquote}
+
+There are also some interesting patterns in the negatively-predicting n-grams.
+For instance, self-describing language appears to be a consistently negative predictor of altruistic donation.
+Though the usage of any short sequence of words can vary considerably, common usage of linguistic features like ``people that are,'' ``we going,'' ``so we know,'' and ``my website at'' demonstrate this phenomenon.
+\begin{blockquote}
+We are all likable and professional \textbf{people that are} trying to build something\ldots\par\noindent
+How Are \textbf{We Going} to Pull This Off?\ldots\par\noindent
+We have 7 or so years of experience building art ... \textbf{so we know} that we can make this project happen.\ldots\par\noindent
+Please visit \textbf{my website at}\ldots
+\end{blockquote}
+Furthermore, it seems that lingustic features that make commands of backers (``get in on,'' ``must make'') are negative predictors of donations.
+\begin{blockquote}
+Participants \textbf{must make} their own travel/lodging arrangements\ldots\par\noindent
+We only have room for 4, so \textbf{get in on} this quickly\ldots
+\end{blockquote}
+
+Finally, the portrayal of backer interaction with rewards also appears to have a significant effect on donations.
+For instance, ``recipient of'' is a strong positive predictor, whereas ``can walk'' is a strong negative predictor.
+\begin{blockquote}
+Depending on how much money you pledge you \textbf{can walk} away with something as small as a print\ldots\par\noindent
+You will be the \textbf{recipient of} TWO different designs
+\end{blockquote}
+
+Overall, there are lots of interesting linguistic and psychological observations that can be made based on the most significant positive and negative language-based predictors.
+A full ordered list of n-grams along with associated regression coefficients is provided\footnote{PUT LINK HERE} if the reader is interested in performing their own analysis.
+\begin{figure*}[t]
 \centering
@@
 \subfloat{
-  \includegraphics[width=.3\textwidth]{figures/Artevents.png}
+  \includegraphics[width=.3\textwidth]{figures/Gamesevents.png}
 }
@@
 \subfloat{
-  \includegraphics[width=.3\textwidth]{figures/Artvals.png}
+  \includegraphics[width=.3\textwidth]{figures/Gamesvals.png}
 }
@@
 For both rows, dotted lines indicate means for successful and unsuccessful projects.
-The three columns represent projects from the most popular categories, ``Music,'' ``Film and Video,'' and ``Art,'' though similar patterns often emerge in categories like ``Technology'' and ``Games.''}
-\label{fig:failsuccgraphs}
+The first two columns represent projects from the two most popular categories, ``Music'' and ``Film and Video,'' while the third ``Games,'' is included for topical contrast.
+All differences between the means in the graphs presented are significant at the 5\% level except for the ``Games'' and ``Music'' graphs in the second row.}
+\label{fig:failsucc}
 \end{figure*}
@@
 For instance, in the two most popular Kickstarter categories, ``Music'' and ``Film and Video,'' we observe a that failed projects recieve, on average, significantly more altruistic donation events (Student's t-test, $p<<.001$ in both cases).
-Sample plots of the event distributions are presented in the first row of Figure FIG.
+Sample plots of the event distributions are presented in the first row of Figure \ref{fig:failsucc}.
 
@@
 In the ``Music'' category, the test statistic is close to zero,  In fact, over all categories all statistically significant results ( state that successful projects.
-Sample plots of the dollar value distributions are presented in the second row of Figure FIG.
+Sample plots of the dollar value distributions are presented in the second row of Figure \ref{fig:failsucc}.
 
@@
 Are there community-derived benefits to making altruistic donations on Kickstarter?
-These specific questions would be best answered by Kickstarter users themselves; interesting future work might include questionaires sent out to a specifically targeted user base.
+These specific questions would be best answered by Kickstarter users themselves; interesting future work might include questionaires sent out to a specifically targeted subset of users.
 
@@
 
+\section{Acknowledgements}
+
+We would like to thank Eric Gilbert and Tanushree Mitra for providing their HTML scrape of Kickstarter, and all members of the Fall 2014 iteration of Cornell's CS6742 for their helpful conversations.
+
 \bibliographystyle{aaai} \bibliography{refs}

### 2014-12-19 AltruisticLanguage/writing/paper.tex
updates

@@
 
-Furthermore, in our dataset consisting of 45810 completed Kickstarter projects, we are able to quantify the number of purely altruistic donation events and the total value given above and beyond the amount required for all reward claims.
+Furthermore, in our dataset consisting of 45K completed Kickstarter projects, we are able to quantify the number of purely altruistic donation events and the total value given above and beyond the amount required for all reward claims.
 Of the roughly 3.4M donation events, about 360K (10.59\%) resulted from users who selected no reward.
@@
 
+Our dataset consists of 45810 completed Kickstarter projects, the URLs of which were originally collected by AppsBlogger.com.
+The projects in our data were all active sometime between April 2009, the earliest start date, and August 2012, the latest end date.
+Every Kickstarter project has an associated HTML page, which we parse using the popular HTML parsing library Beautiful Soup 4\footnote{\url{http://www.crummy.com/software/BeautifulSoup/}}.
+Each project's page contains information about the project such as its title, its description, the rewards (with associated cost, number of backers who have claimed that reward, and a description), the FAQ section, the total number of backers, and the total amount of money raised.
+This information served as the basis of our analysis.
+
+Kickstarter projects are also associated with a single category.
+The category of a Kickstarter project is used by the site to index projects and to help users find projects of a specific type.
+While some of these categories (13) are ``main'' categories, most are ``subcategories'' that have a corresponding main category.
+In most cases, we treat all categories as equivalent, irrespective of whether or not it is a sub or a main.
+
+In all of our analyses as a preprocessing step for text data, we remove punctuation from strings and convert all characters to lower case, but do not discard stop words.
+In general, we are interested in unigrams, bigrams, and trigrams, and tokenize after these preprocessing steps.
+
 \section{Kickstarter vs. GoFundMe and Amazon}
@@
 For instance, a popular category on GoFundMe is ``Medical,'' wherein users create pages to raise money for medical expenses for family and friends.
-Our dataset consists of 7.7K GoFundMe project descriptions.
+Our dataset consists of 7.7K GoFundMe project descriptions scraped in November 2014.
 In contrast to Kickstarter, in a vast majority of cases GoFundMe contributors don't have the option to select compensentory rewards, and we therefore regard our GoFundMe data as requests for purely altruistic actions.
-As a general preprocessing step, in all of our analyses we remove punctuation from strings, and convert all characters to lower case.
 
@@
 \hline
-Number of Sentences & Top 5 trigrams \\\hline
-178 & \specialcell{`would be greatly appreciated'\\`as you can imagine'\\`donation is too small'\\`no donation is too'\\`you can to help'}\\\hline
-254 & \specialcell{`thank you for your'\\`thank you so much'\\`for taking the time'\\`the time to read'\\`taking the time to'}\\\hline
-356 & \specialcell{`to be able to'\\`not be able to'\\`will be able to'\\`be able to work'\\`will not be able'}\\\hline
-192 & \specialcell{`to go to the'\\`to the er and'\\`back to the hospital'\\`rushed to the hospital'\\`go to the hospital'}\\\hline
-275 & \specialcell{`we are asking for'\\`are asking for help'\\`our friends and family'\\`my family and i'\\`help raise money for'}\\\hline
-243 & \specialcell{`in the middle of'\\`the middle of the'\\`a \# year old'\\`in the hospital and'\\`middle of the night'}\\\hline
-272 & \specialcell{`was diagnosed with stage'\\`diagnosed with stage \#'\\`she was diagnosed with'\\`has been diagnosed with'\\`was diagnosed with a'}\\\hline
-255 & \specialcell{`is one of the'\\`one of the most'\\`find it in your'\\`for all of the'\\`it in your heart'}\\\hline
-181 & \specialcell{`will be greatly appreciated'\\`will be a long'\\`long road to recovery'\\`update NAME had chemo'\\`him and his family'}\\\hline
-224 & \specialcell{`to help with medical'\\`will go directly to'\\`to raise money for'\\`during this difficult time'\\`if you would like'}\\\hline
-104 & \specialcell{`he is able to'\\`he is in a'\\`fighting for his life'\\`a good fight and'\\`of you may not'}\\\hline
+Number of Sentences & Top 3 4-grams \\\hline
+178 & \specialcell{`would be greatly appreciated'\\`as you can imagine'\\`donation is too small'}\\\hline
+254 & \specialcell{`thank you for your'\\`thank you so much'\\`for taking the time'}\\\hline
+356 & \specialcell{`to be able to'\\`not be able to'\\`will be able to'}\\\hline
+192 & \specialcell{`to go to the'\\`to the er and'\\`back to the hospital'}\\\hline
+275 & \specialcell{`we are asking for'\\`are asking for help'\\`our friends and family'}\\\hline
+243 & \specialcell{`in the middle of'\\`the middle of the'\\`a \# year old'}\\\hline
+272 & \specialcell{`was diagnosed with stage'\\`diagnosed with stage \#'\\`she was diagnosed with'}\\\hline
+255 & \specialcell{`is one of the'\\`one of the most'\\`find it in your'}\\\hline
+181 & \specialcell{`will be greatly appreciated'\\`will be a long'\\`long road to recovery'}\\\hline
+224 & \specialcell{`to help with medical'\\`will go directly to'\\`to raise money for'}\\\hline
+104 & \specialcell{`he is able to'\\`he is in a'\\`fighting for his life'}\\\hline
 \end{tabular}
@@
 \end{table}
+
+\begin{figure}
+\centering
+\includegraphics[width=.45\textwidth]{figures/docpos.png}
+\caption{The average document position of sentences in the ``Introduction'' and ``Thank you'' clusters.
+It's clear that, in general, sentences related diagnoses occur at the beginning of documents, where as thank you's are expressed at the end.
+Similar histograms for all other clusters are superimposed in black for comparison.}
+\label{fig:docpos}
+\end{figure}
 
@@
 Finally, we retrain each of the language models based on the new clustering.
-This process of re-clustering, computing Viterbi paths, and re-training language models in an expectation maximization like fashion is executed until convergence or a maximum number of iterations is made.
+This process of re-clustering, computing Viterbi paths, and re-training language models in an expectation
+maximization like fashion is executed until convergence or a maximum number of iterations is made.
+
+In accordance with the reccomendations of the original authors, we attempt to map all named entities to a ``NAME'' token and all numbers to a ``NUM'' token.
+We use the default NLTK\footnote{\url{http://www.nltk.org/}} named entity recognizer to identify tokens to be mapped to ``NAME,'' and we map any token that parses to a float without error to ``NUM.''
 
@@
 After our expectation maximization converged after nine iterations, we were left with the order-aware sentence clusters displayed in Table \ref{tab:contentmodel} (etcetera cluster omitted).
+
+.
+For the remaineder of this analysis, we are going to focus on the cluster containing 254 sentences (dubbed the ``Thank you'' cluster) and the cluster containing 272 sentences (dubbed the ``Introduction'' cluster).
+
+Content models carry with them the advantage that sentences with disjoint bigram features may be clustered together based on the order of sentences.
+For instance, ``your contributions big or small are greatly appreciated,'' ``as a family we thank you,'' and ``god bless you have a wonderful day'' are clustered together in the ``Thank you'' cluster.
+Despite the three sentences having disjoint bigram features and being entirely dissimilar according to the basic intialization scheme, the content model is able to discern that the three likely have similar meaning based on their placement in documents relative to other sentences.
+
+There are many interesting things that can be learned from the transition probabilities output by the content model, the most interpretable of which is illustrated in Figure \ref{fig:docpos}.
+This figure illustrates the distribution of normalized sentence position in .
+While this result is somewhat unsurprising (situations are introduced before authors thank readers) it demonstrates that the content model is able to learn useful information about ordering in an unsupervised fashion.
 
@@
 
-We would like to thank Eric Gilbert and Tanushree Mitra for providing their HTML scrape of Kickstarter, and all members of the Fall 2014 iteration of Cornell's CS6742 for their helpful conversations.
+We would like to thank Eric Gilbert and Tanushree Mitra for providing their HTML scrape of Kickstarter, and all members of the Fall 2014 iteration of Cornell's CS6742 for the helpful conversations.
 

### 2014-12-19 AltruisticLanguage/writing/paper.tex
more writing

@@
 \newenvironment{blockquote}{%
+  \setlength{\parskip}{.5em}
   \par%
-  \setlength{\parskip}{.5em}
   \small
@@
 \begin{quote}
-Abstract
+In this study we conduct several experiments related to altruistic behavior on Kickstarter and other crowdfunding sites.
+This realm has been relatively unexplored in previous work, which is surprising given that roughly 20\% of all backing money on Kickstarter is donated.
+Because previous work sugguests that lingustic features are very important to requests made online, language is a focal point of our analysis.
+We first find that Kickstarter exists in a lingustic realm somewhere between pure altruism and pure commericalism.
+Next, we find that useful information about the sequential nature of requests can be learned in an unsupervized fashion.
+Also, we find that linguistic features on Kickstarter are able to predict whether or not projects recieve above-average levels of prosocial activity.
+Finally, and most surprisingly, we find that failing projects are acutally more likely to recieve altruistic donations, sugguesting the existance of a subset of users who frequently give small amounts of money to failing projects and request no rewards in return.
 \end{quote}
@@
 
-(PARAGRAPH ABOUT ACADEMIC INTEREST WITH CITATIONS)
-
 We argue that crowdfunding sites similar to Kickstarter occupy a unique space between a realm of pure salespersonship and a realm of pure altruism.
@@
 Users voluntarily paying more for an identical product sugguests that Kickstarter is not a community solely focused on commercialism.
+This observation matches previous work which sugguests that people use crowdfunding tools for reasons other than personal gain \cite{van2011fighting}.
 
@@
 Of the roughly \$246M pledged in our dataset, over \$53M (21.59\%) was given altruistically.
-Compared to previous analyses of altruism in online communities THIS IS A LOT OF MONEY.
 
@@
 Even using post-launch information, however, does not improve accuracy as much as accounting for language; 85\% accuracy is achieved using information available after 15\% of the duration of the campaign has expired \cite{etter2013launch}.
+Furthermore, lingustic factors have been shown to effect the quality and time-to-response of questions posed in an online community \cite{teevan2011factors}.
 These findings sugguest that language is very important on Kickstarter, which is a primary motivation for making it a focus of our analysis.
@@
 An advantage of their dataset is that all altruistic requests are made for the same service.
-MORE MORE MORE
+Previous work on Kickstarter has also demonstrated that users are more likely to donate to campigns as time is winding down and the project has not yet met its goal, which is an arguably altruistic behavior \cite{kuppuswamy2013crowdfunding}.
 
@@
 \section{Primary Dataset}
-
 Our dataset consists of 45810 completed Kickstarter projects, the URLs of which were originally collected by AppsBlogger.com.
@@
 
-To analyze the sequential structure of requests, we run a case study on a subset of data utilizing a content model \cite{barzilay2004catching} to produce a sentence clustering.
+To analyze the sequential structure of requests in a crowdfunding setting, we run a case study on a subset of data utilizing a content model \cite{barzilay2004catching} to produce a sentence clustering.
 A content model is an unsupervized learning algorithm that operates on the sentence level, takes information order into account, and learns transition probabilities between sentence types.
@@
 
-.
-For the remaineder of this analysis, we are going to focus on the cluster containing 254 sentences (dubbed the ``Thank you'' cluster) and the cluster containing 272 sentences (dubbed the ``Introduction'' cluster).
+Clearly, there are clusters of all sorts that represent different pieces of a plea for help with medical expenses.
+One interesting cluster is the ``Ability'' cluster, which contains 356 sentences.
+Describing in detail a lack of ability is likely to elicit empathetic feelings from a reader, and, according to the well-supported empathy-altruism hypothesis, empathetic feelings are very likely to lead one to purely altruistic behavior, such as donating on a crowdfunding site \cite{batson1988five}.
 
@@
 
-There are many interesting things that can be learned from the transition probabilities output by the content model, the most interpretable of which is illustrated in Figure \ref{fig:docpos}.
-This figure illustrates the distribution of normalized sentence position in .
-While this result is somewhat unsurprising (situations are introduced before authors thank readers) it demonstrates that the content model is able to learn useful information about ordering in an unsupervised fashion.
+For the remaineder of this analysis, we are going to focus on the cluster containing 254 sentences (dubbed the ``Thank you'' cluster) and the cluster containing 272 sentences (dubbed the ``Introduction'' cluster).
+Though there are many interesting things that can be learned from the transition probabilities output by the content model, the most interpretable fact is illustrated in Figure \ref{fig:docpos}.
+This figure shows the distribution of normalized sentence position of each cluster in the sentences in the dataset.
+For a given cluster $c$, this statistic is defined as
+
+\begin{equation} \label{eq:sentpos}
+\sum\limits_{k \in \text{Occurances of $c$}} \frac{\text{Position of $k$ in containing sentence}}{\text{Length of sentence containing $k$}}
+\end{equation}
+
+While this result is somewhat unsurprising (situations are introduced before authors thank readers) it demonstrates that the content model is able to learn useful information about ordering in an unsupervised fashion, and that aspects of the sequential nature of altruistic requests are learnable by this method.
 
@@
 Based on this analysis, it's reasonable to state that the Kickstarter community is more likely to give to students without requesting any rewards in return.
-
 Furthermore, positive sentiment and language that indicates the author's excitement about the project (``so exciting,'' ``the challenge of,'' ``taken off'') appears to positively predict donation.
@@
 \end{blockquote}
-
 There are also some interesting patterns in the negatively-predicting n-grams.
@@
 \end{blockquote}
-
 Finally, the portrayal of backer interaction with rewards also appears to have a significant effect on donations.
@@
 Here, we presented several analyses relating to altruistic behavior on crowdfunding sites with a focus on language.
+Our first analysis positioned Kickstarter between purely altruistic and purely commercial linguistic regimes.
+Next, as we examined the sequential structure of purely altruistic requests on GoFundMe and found that a content model was capable of learning an interpretable set of content-aware clusters that illustrate some of the stratigies authors use to ellicit donations.
+Then, noting that both event-based and amount-based altruistic activities can be determined based on the information presented on a Kickstarter page, we were able to extract the important linguistic features responsible for prediction of above-average donation levels.
+Finally, we made the surprising observation that failing projects tend to recieve more donation events, even after accounting for a wide range of control variables.
+This increased donation does not carry over to our amount-based analysis, however, sugguesting that failing projects recieve a large number of low-valued donations.
+
+Overall, much more work could be done to analyze the dynamics of altruistic behavior on crowdfunding sites, and in ``mixed-altruism'' domains in general.
+As previously sugguested, one possible avenue for future research would be to identify a subset of Kickstarter users that are likely to be responsible for frequent, low-valued donations given to failing projects.
+Another interesting avenue for exploration might be to identify and find similarities between other communities like Kickstarter.
+
+Finally, our study has several limitations that could be overcome in future work.
+Many Kickstarter projects have very low valued ``dummy'' rewards that are functionally equivalent to altruistic donation (for instance, such a reward might cost 1\$ and have the description ``Thanks!'').
+Its likely such rewards obscured some signal in our dataset.
+Furthermore, there are ``pie-in-the-sky'' type rewards that constitute altruism, as well (for instance, such a reward might cost 10,000\$ and have the description ``Thank you!
+You will get a producer credit in our movie and our eternal gratitude'').
+In any case, a more careful consideration of rewards would be a well-suited topic for future work.
 

### 2014-12-19 AltruisticLanguage/writing/paper.tex
editing done

@@
 This realm has been relatively unexplored in previous work, which is surprising given that roughly 20\% of all backing money on Kickstarter is donated.
-Because previous work sugguests that lingustic features are very important to requests made online, language is a focal point of our analysis.
+Because previous studies sugguest that lingustic features are very important to requests made online, language is a focal point of our analysis.
 We first find that Kickstarter exists in a lingustic realm somewhere between pure altruism and pure commericalism.
 Next, we find that useful information about the sequential nature of requests can be learned in an unsupervized fashion.
-Also, we find that linguistic features on Kickstarter are able to predict whether or not projects recieve above-average levels of prosocial activity.
+Also, we find that linguistic features of Kickstarter campaigns are able to predict whether or not projects attract above-average levels of prosocial activity.
 Finally, and most surprisingly, we find that failing projects are acutally more likely to recieve altruistic donations, sugguesting the existance of a subset of users who frequently give small amounts of money to failing projects and request no rewards in return.
@@
 \end{tabular}
-\caption{Summary of Bayesian analysis of language comparing Kickstarter to GoFundMe and Amazon. Negative Z-scores correspond to Kickstarter. Top ten most significant n-grams are presented.}
+\caption{Summary of Bayesian analysis of language comparing Kickstarter to GoFundMe and Amazon.
+Negative Z-scores correspond to Kickstarter.
+Top ten most significant n-grams are presented.
+A full list of n-grams and z-scores is provided.\footnote{PUT LINK HERE}}
 \label{tab:pairwise}
@@
 Furthermore, in our dataset consisting of 45K completed Kickstarter projects, we are able to quantify the number of purely altruistic donation events and the total value given above and beyond the amount required for all reward claims.
-Of the roughly 3.4M donation events, about 360K (10.59\%) resulted from users who selected no reward.
+Of the roughly 3.4M donation events, about 360K (10.59\%) resulted from users who willingly opted to recieve no reward.
 Of the roughly \$246M pledged in our dataset, over \$53M (21.59\%) was given altruistically.
@@
 Mitra and Gilbert analyze the language that predicts successful Kickstarter projects \cite{mitra2014language}.
-When compared their baseline regression trained on language-indepedent project features, their final classifier, which includes n-gram counts, is able to classify projects 15\% more accurately, resulting in a 97.8\% correct prediction rate in a 10-fold cross validation setting.
+When compared their baseline regression trained on a set of language-indepedent set of project features, their final classifier, which includes binary n-gram indicator variables, is able to classify projects 15\% more accurately, resulting in a 97.8\% correct prediction rate in a 10-fold cross validation setting.
 Similar analyses that do not take language fully into account are not able to achieve such predictive accuracy.
@@
 Furthermore, lingustic factors have been shown to effect the quality and time-to-response of questions posed in an online community \cite{teevan2011factors}.
-These findings sugguest that language is very important on Kickstarter, which is a primary motivation for making it a focus of our analysis.
+These findings sugguest that language is very important on Kickstarter and, more generally, in online communities as a whole, which is a primary motivation for making it a focus of our analysis.
 
-Altruism in online communities has also been studied as well.
+Altruism in online communities has also been previously studied.
 Althoff et al.
-examine a purely altruistic community wherein users request free pizza from other members \cite{althoff2014ask}.
-An advantage of their dataset is that all altruistic requests are made for the same service.
+examine a purely altruistic community wherein users request and provide free pizza to and from other community members \cite{althoff2014ask}.
+An advantage of their dataset is that all their request are purely altruistic, and are made for the same service, though the total donation value of their dataset is lower than that presented here.
 Previous work on Kickstarter has also demonstrated that users are more likely to donate to campigns as time is winding down and the project has not yet met its goal, which is an arguably altruistic behavior \cite{kuppuswamy2013crowdfunding}.
@@
 Our dataset consists of 45810 completed Kickstarter projects, the URLs of which were originally collected by AppsBlogger.com.
-The projects in our data were all active sometime between April 2009, the earliest start date, and August 2012, the latest end date.
+The projects in our data were all active between April 2009, the earliest start date, and August 2012, the latest end date.
 Every Kickstarter project has an associated HTML page, which we parse using the popular HTML parsing library Beautiful Soup 4\footnote{\url{http://www.crummy.com/software/BeautifulSoup/}}.
@@
 Kickstarter projects are also associated with a single category.
-The category of a Kickstarter project is used by the site to index projects and to help users find projects of a specific type.
-While some of these categories (13) are ``main'' categories, most are ``subcategories'' that have a corresponding main category.
+The category of a Kickstarter project is used by the site to index campaigns and to help users find projects of a specific type.
+While some of these categories are ``main'' categories (13/49) most are ``subcategories'' that have a corresponding main category.
 In most cases, we treat all categories as equivalent, irrespective of whether or not it is a sub or a main.
 
-In all of our analyses as a preprocessing step for text data, we remove punctuation from strings and convert all characters to lower case, but do not discard stop words.
+In all of our analyses that use text data, we preprocess by removing punctuation from strings and converting all characters to lower case, though we do not discard stop words.
 In general, we are interested in unigrams, bigrams, and trigrams, and tokenize after these preprocessing steps.
@@
 Our dataset consists of just over 1M Amazon product descriptions \cite{mcauley2013hidden}.
-We believe that Amazon product descriptions can be considered as purely commercial.
+We consider Amazon product descriptions as a gold standard purely commercial dataset.
+
 On the other hand, GoFundMe is a crowdfunding site similar to Kickstarter, but campaigns are generally more focused on charitable/personal ventures.
@@
 To compare the language used on Kickstarter to purely commercial and purely altrustic pitches, we adopt a Bayesian approach that has previously been successful in comparing the language used by two political parties on a specific issue \cite{monroe2008fightin}.
-This model has been used to compare word usage between two corpora in a princpled way.
+In a general sense, this model has been used to compare word usage between two related corpora in a princpled way.
 Under the model, language is modeled as a ``bag of words'' represented by a multinomial distribution over vocabulary items.
-For the two corpora in question, we assume that their language vectors are drawn from a Dirichlet prior.
+For the two corpora in question, we assume that their language distributions are drawn from a Dirichlet prior.
 Though it is possible in this scenario to encode useful information in the prior, we find it sufficient to utilize an uninformative prior and set our Dirichlet hyperparameter to be $\alpha=.01$.
@@
 In order to use this model, one must first define a vocabulary.
-Because we are interested in language rather than specific subject matter, we apply a cross-categorical filtering scheme in an attempt to control for topic.
+Because we are interested in general language rather than specific subject matter, we apply a cross-categorical filtering scheme in an attempt to control for topic.
 Recall that in each of our datasets, documents are associated with one or more categories.
-In a first attempt to control for topic, we first apply a filter that removes all n-grams that don't appear in all categories at least once.
+In a first attempt to control for topic, we first applied a filter that removed all n-grams that didn't appear in all categories at least once.
 We found this simple filtration scheme to be inadequate -- the words ``book,'' ``publisher,'' and ``author,'' for instance, appear very frequently in the Amazon dataset because about 78\% of the products in the Amazon dataset are tagged under the Book category.
 
-To apply a more stringent topic controlling filter after removing n-grams that don't appear in all categories, for each n-gram $n$, we compute the intra-category document frequency denoted $f_n^c$ for all categories $c$.
+To apply a more stringent topic controlling filter, after removing n-grams that don't appear in all categories, for each n-gram $n$, we compute the intra-category document frequency denoted $f_n^c$ for all categories $c$ where $f^n_c$ is the average number of times $n$ appears in documents within category $c$.
 We then compute the ``normalized width'' $w_n$ for n-gram $n$ as...
@@
 If a word appears very frequently in a single category, the normalized width will be large.
-After computing all normalized widths, we filter out the 10\% of n-grams with highest normalized width.
-
-After this two-part filtration scheme is applied to all three datasets, we take an intersection of the resulting n-grams to form our final vocabulary, which contains 2077 n-grams.
+After computing this statistic for all n-grams, we discard the 10\% of n-grams with highest normalized width.
+This two-part filtration scheme is applied to all three datasets, and to derive our final vocabulary we take a 3-way intersection of the resulting topic-controlled features from Kickstarter, Amazon, and GoFundMe.
+The final vocabulary contains 2077 n-grams.
 The results of these analyses are summarized in Table \ref{tab:pairwise}.
@@
 The intuition behind this comparsion is as follows: if Kickstarter is more altruistic than Amazon, but less altruistic than GoFundMe, then we would expect altruistically-associated n-grams to be on opposite ends of each ranking.
-This phenomenon occurs
+This phenomenon occurs for the z-scores of n-grams like ``friends and family'' (-48.86 to 27.24) ``thank you for'' (-112.63 to 20.38) and ``love'' (-75.63 to 23.83) as one might expect, but does it happen in general?
 
@@
 
-To analyze the sequential structure of requests in a crowdfunding setting, we run a case study on a subset of data utilizing a content model \cite{barzilay2004catching} to produce a sentence clustering.
+To analyze the sequential structure of altruistic requests in a crowdfunding setting, we run a case study on a subset of data utilizing a content model \cite{barzilay2004catching} to produce a sentence clustering.
 A content model is an unsupervized learning algorithm that operates on the sentence level, takes information order into account, and learns transition probabilities between sentence types.
@@
 After sentences are clustered into these groups, we merge all clusters smaller than some threshold into an ``etcetera'' cluster.
-This etcetera cluster is a unique feature of the content model that allows it the flexibility to sort sentences that otherwise don't fit into an ``other'' cluster.
+This etcetera cluster is a unique feature of the content model that allows it the flexibility to assign sentences that otherwise don't fit into an ``other'' cluster.
 After this merging process, we are left with $m$ clusters.
@@
 This process of re-clustering, computing Viterbi paths, and re-training language models in an expectation
-maximization like fashion is executed until convergence or a maximum number of iterations is made.
+maximization-like fashion is executed until convergence or a maximum number of iterations is made.
 
@@
 
-Clearly, there are clusters of all sorts that represent different pieces of a plea for help with medical expenses.
+Clearly, there are clusters of all sorts that represent different pieces of a generalized plea for help with medical expenses.
 One interesting cluster is the ``Ability'' cluster, which contains 356 sentences.
@@
 
-Content models carry with them the advantage that sentences with disjoint bigram features may be clustered together based on the order of sentences.
-For instance, ``your contributions big or small are greatly appreciated,'' ``as a family we thank you,'' and ``god bless you have a wonderful day'' are clustered together in the ``Thank you'' cluster.
-Despite the three sentences having disjoint bigram features and being entirely dissimilar according to the basic intialization scheme, the content model is able to discern that the three likely have similar meaning based on their placement in documents relative to other sentences.
+Content models carry with them the advantage that sentences with disjoint bigram features may be clustered together based on the order of sentences after EM is applied.
+For instance, ``your contributions big or small are greatly appreciated,'' ``as a family we thank you,'' and ``god bless you have a wonderful day'' are clustered together.
+Despite the three sentences having disjoint bigram features and being entirely dissimilar according to the original, order-unaware clustering scheme, the content model is able to discern that the three likely have similar meaning based on their placement in documents relative to other sentences.
 
@@
 For a given cluster $c$, this statistic is defined as
-
 \begin{equation} \label{eq:sentpos}
@@
 \end{equation}
-
 While this result is somewhat unsurprising (situations are introduced before authors thank readers) it demonstrates that the content model is able to learn useful information about ordering in an unsupervised fashion, and that aspects of the sequential nature of altruistic requests are learnable by this method.
@@
 When a user backs a project on Kickstarter (which is impossible to do anonymously) they are prompted to select a backer reward of value less than or equal to their donation amount.
-If a user does not want to claim a reward but, rather, donate altruistically, there exists an option that allows them to claim no rewards.
-Because the total number of claims for each non-altruistic reward are displayed publicly on the project page, along with the total number of backers (altruistic and non-altruistic alike) we are able to compute the total number of purely altruistic donation events for each project.
+If a user does not want to claim a reward but, rather, donate altruistically, there exists an option that allows them to claim no reward.
+Because the total number of claims for each non-altruistic reward are displayed publicly on the project page along with the total number of backers (altruistic and non-altruistic alike) we are able to compute the total number of purely altruistic donation events for each project.
 Furthermore, the site allows for users to give an amount exceeding the cost of a given reward, so we are able to compute the total amount donated to a project above and beyond the amount required for all the posted reward claims.
@@
 glmnet is a software package that implements cyclic coordinate decent and is capable of performing penalized regression tasks on highly sparse datasets.
-For our experiments, we utilize an $L_1$ (lasso) regularization term in an attempt to enforce sparsity and derive a parsimonious model, and set glmnet to perform 10-fold cross validation to search for the optimal regularization coefficient and prevent overfitting.
-In addition to training a model on all the data, as a seperate measure we also report test accuracy when spliting our data into a 40k project training set and a 5k project test set.
+For our experiments, we utilize an $L_1$ (lasso) regularization term in an attempt to enforce sparsity and derive a parsimonious model.
+Furthermore, we set glmnet to perform 10-fold cross validation to search for the optimal regularization coefficient and prevent overfitting.
+In addition to training a model on all the data using cross-validation, as a seperate measure of model generalizability we also report test accuracy when spliting our data into a 40k project training set and a 5k project test set.
 Notably, glmnet purposefully does not report standard errors on resulting feature coefficients because the regularization process intorudces substantial bias into the regression process.
@@
 Using a model consisting of controls only, we achieve a cross-validation accuracy of 64.53\% (6.19\% improvement over constant prediction) and a testing set accuracy of 63.80\% (5.46\% improvement).
-The most important positive and negative predictive features were all Kickstarter category control variables.
+The most important positive and negative predictive features were all Kickstarter categorical control variables.
 Dance, theater, public art, performance art, and classical music ($\vec{\beta} = \langle 1.84, 1.56, 1.24, 1.04, .930 \rangle$, respectively) were the categorical variables which were the strongest positive predictors, whereas board/card games, games, comics, video games, and product design ($\vec{\beta} = -\langle 1.64, 1.23, 1.02, .862, .795 \rangle$, respectively) were the strongest negative predictors.
@@
 Our textual features consist of binary indicator variables for unigrams, bigrams, and trigrams in the project descriptions, FAQ question/answers, and reward descriptions of our Kickstarter projects.
-We apply the same two-part filter that we use in our previous analysis to determine a set of topic-free n-grams, which forces selected n-grams to appear in every Kickstarter category and be relatively uniformly distributed between them (see Equation \ref{eq:width}).
+We apply the same two-part normalized width filter that we use in our previous analysis to determine a set of topic-free n-grams, which forces selected n-grams to appear in every Kickstarter category and be relatively uniformly distributed between them (see Equation \ref{eq:width}).
 Applying this two-part filtration process on our Kickstarter dataset exclusively, we end up with 31281 filtered n-grams.
 
-When we incorporate these particular lingustic features, our cross-validation accuracy increases to 67.02\% (2.49\% improvement over controls-only baseline) and our testing accuracy increases to 66.68\% (2.88\% improvement).
+When we incorporate these particular lingustic features as binary indicator variables, our cross-validation accuracy increases to 67.02\% (2.49\% improvement over controls-only baseline) and our testing accuracy increases to 66.68\% (2.88\% improvement).
 The inclusion of lingustic features, therefore, causes our predictive accuracy to increase slightly but significantly.
@@
 
-To address this question, we first run a new lasso penalized regression task where predictive variables consist of the control variables highlighted in Table \ref{tab:controls} plus two additional binary variables ``success,'' which indicates whether or not the funding goal of the project was reached, and ``numBackers,'' the total number of backers for a given project.
+To address this question, we first run a new lasso penalized regression task where predictive variables consist of the control variables highlighted in Table \ref{tab:controls} plus two additional binary variables, namely ``success,'' which indicates whether or not the funding goal of the project was reached, and ``numBackers,'' the total number of backers for a given project.
 The target of this new regression is the proportion of altruistic donations a project recieves.
@@
 Surprisingly, our resulting regression assigns negative weights to both our new predictive variables.
-With respect to the number of backers, the negative weight assigned to this variable indicates that more popular projects are less likely to recieve altruistic donations, in general.
+With respect to the number of backers, the negative weight indicates that more popular projects are less likely to recieve altruistic donations, in general.
 More surprising, however, is that after controling for all variables in Table \ref{tab:controls} and project size, successful projects recieve \emph{less} altruistic donations than unsuccessful projects.
@@
 In the ``Film and Video'' category, for instance, we observe a total reversal, a significant result ($p << .001$) that states successful projects receive more dollars altruistically than failed projects.
-In the ``Music'' category, the test statistic is close to zero,  In fact, over all categories all statistically significant results ( state that successful projects.
+In fact, over all categories all statistically significant results state that successful projects recieve more funding.
+In the ``Music'' category, however, the test statistic is close to zero, and the difference is no longer significant as it was in the event-based analysis.
 Sample plots of the dollar value distributions are presented in the second row of Figure \ref{fig:failsucc}.
@@
 Here, we presented several analyses relating to altruistic behavior on crowdfunding sites with a focus on language.
-Our first analysis positioned Kickstarter between purely altruistic and purely commercial linguistic regimes.
+Our first analysis positioned Kickstarter somewhere between purely altruistic and purely commercial linguistic regimes.
 Next, as we examined the sequential structure of purely altruistic requests on GoFundMe and found that a content model was capable of learning an interpretable set of content-aware clusters that illustrate some of the stratigies authors use to ellicit donations.
@@
 Overall, much more work could be done to analyze the dynamics of altruistic behavior on crowdfunding sites, and in ``mixed-altruism'' domains in general.
-As previously sugguested, one possible avenue for future research would be to identify a subset of Kickstarter users that are likely to be responsible for frequent, low-valued donations given to failing projects.
+As previously sugguested, one possible avenue for future research would be to identify and reach out to a subset of Kickstarter users that are likely to be responsible for frequent, low-valued donations given to failing projects.
 Another interesting avenue for exploration might be to identify and find similarities between other communities like Kickstarter.
@@
 Finally, our study has several limitations that could be overcome in future work.
-Many Kickstarter projects have very low valued ``dummy'' rewards that are functionally equivalent to altruistic donation (for instance, such a reward might cost 1\$ and have the description ``Thanks!'').
+Many Kickstarter projects have very low valued ``dummy'' rewards that are functionally equivalent to altruistic donation (for instance, such a reward might cost \$1 and have the description ``Thanks!'').
 Its likely such rewards obscured some signal in our dataset.
-Furthermore, there are ``pie-in-the-sky'' type rewards that constitute altruism, as well (for instance, such a reward might cost 10,000\$ and have the description ``Thank you!
+Furthermore, there are ``pie-in-the-sky'' type rewards that constitute altruism, as well (for instance, such a reward might cost \$10,000 and have the description ``Thank you!
 You will get a producer credit in our movie and our eternal gratitude'').

### 2014-12-19 AltruisticLanguage/writing/paper.tex
spell check

@@
 This realm has been relatively unexplored in previous work, which is surprising given that roughly 20\% of all backing money on Kickstarter is donated.
-Because previous studies sugguest that lingustic features are very important to requests made online, language is a focal point of our analysis.
-We first find that Kickstarter exists in a lingustic realm somewhere between pure altruism and pure commericalism.
-Next, we find that useful information about the sequential nature of requests can be learned in an unsupervized fashion.
+Because previous studies suggest that linguistic features are very important to requests made online, language is a focal point of our analysis.
+We first find that Kickstarter exists in a linguistic realm somewhere between pure altruism and pure commercialism.
+Next, we find that useful information about the sequential nature of requests can be learned in an unsupervised fashion.
 Also, we find that linguistic features of Kickstarter campaigns are able to predict whether or not projects attract above-average levels of prosocial activity.
-Finally, and most surprisingly, we find that failing projects are acutally more likely to recieve altruistic donations, sugguesting the existance of a subset of users who frequently give small amounts of money to failing projects and request no rewards in return.
+Finally, and most surprisingly, we find that failing projects are actually more likely to receive altruistic donations, suggesting the existence of a subset of users who frequently give small amounts of money to failing projects and request no rewards in return.
 \end{quote}
@@
 In recent years, crowdfunding websites have emerged as a popular method of fundraising for individuals looking to promote their ventures to online communities.
-The most popular of these sites, Kickstarter, provides a venue for entrepreneurs to connect with individuals who might be interested in financially supporting their project ideas, which range from artistic endevours to technology startups.
+The most popular of these sites, Kickstarter, provides a venue for entrepreneurs to connect with individuals who might be interested in financially supporting their project ideas, which range from artistic endeavours to technology startups.
 To date, over \$1.4B has been invested in Kickstarter projects from more than 7.4M unique backers resulting in over 73K successfully funded projects.
@@
 We argue that crowdfunding sites similar to Kickstarter occupy a unique space between a realm of pure salespersonship and a realm of pure altruism.
-A project that illustrates that Kickstarter is not purely altruistic nor purely commerical is ``Juicies.''\footnote{\url{http://tinyurl.com/juiciesproject}} In this project, the creators successfully attempted to create a company that sells multi-colored charging cables for various mobile devices, and offered cable preorders as rewards.
+A project that illustrates that Kickstarter is not purely altruistic nor purely commercial is ``Juicies.''\footnote{\url{http://tinyurl.com/juiciesproject}} In this project, the creators successfully attempted to create a company that sells multi-colored charging cables for various mobile devices, and offered cable preorders as rewards.
 The basic cable was associated with two rewards, one costing the suggested retail price of \$20, and the other charging users to ``pay what you can'' for the same cable costing \$1.
 While over 1K pay-what-you-can rewards were claimed, the \$20 reward was claimed 280 times.
-Users voluntarily paying more for an identical product sugguests that Kickstarter is not a community solely focused on commercialism.
-This observation matches previous work which sugguests that people use crowdfunding tools for reasons other than personal gain \cite{van2011fighting}.
+Users voluntarily paying more for an identical product suggests that Kickstarter is not a community solely focused on commercialism.
+This observation matches previous work which suggests that people use crowdfunding tools for reasons other than personal gain \cite{van2011fighting}.
 
@@
 Furthermore, in our dataset consisting of 45K completed Kickstarter projects, we are able to quantify the number of purely altruistic donation events and the total value given above and beyond the amount required for all reward claims.
-Of the roughly 3.4M donation events, about 360K (10.59\%) resulted from users who willingly opted to recieve no reward.
+Of the roughly 3.4M donation events, about 360K (10.59\%) resulted from users who willingly opted to receive no reward.
 Of the roughly \$246M pledged in our dataset, over \$53M (21.59\%) was given altruistically.
@@
 Mitra and Gilbert analyze the language that predicts successful Kickstarter projects \cite{mitra2014language}.
-When compared their baseline regression trained on a set of language-indepedent set of project features, their final classifier, which includes binary n-gram indicator variables, is able to classify projects 15\% more accurately, resulting in a 97.8\% correct prediction rate in a 10-fold cross validation setting.
+When compared their baseline regression trained on a set of language-independent set of project features, their final classifier, which includes binary n-gram indicator variables, is able to classify projects 15\% more accurately, resulting in a 97.8\% correct prediction rate in a 10-fold cross validation setting.
 Similar analyses that do not take language fully into account are not able to achieve such predictive accuracy.
@@
 Even using post-launch information, however, does not improve accuracy as much as accounting for language; 85\% accuracy is achieved using information available after 15\% of the duration of the campaign has expired \cite{etter2013launch}.
-Furthermore, lingustic factors have been shown to effect the quality and time-to-response of questions posed in an online community \cite{teevan2011factors}.
-These findings sugguest that language is very important on Kickstarter and, more generally, in online communities as a whole, which is a primary motivation for making it a focus of our analysis.
+Furthermore, linguistic factors have been shown to effect the quality and time-to-response of questions posed in an online community \cite{teevan2011factors}.
+These findings suggest that language is very important on Kickstarter and, more generally, in online communities as a whole, which is a primary motivation for making it a focus of our analysis.
 
@@
 An advantage of their dataset is that all their request are purely altruistic, and are made for the same service, though the total donation value of their dataset is lower than that presented here.
-Previous work on Kickstarter has also demonstrated that users are more likely to donate to campigns as time is winding down and the project has not yet met its goal, which is an arguably altruistic behavior \cite{kuppuswamy2013crowdfunding}.
+Previous work on Kickstarter has also demonstrated that users are more likely to donate to campaigns as time is winding down and the project has not yet met its goal, which is an arguably altruistic behavior \cite{kuppuswamy2013crowdfunding}.
 
@@
 Our dataset consists of 7.7K GoFundMe project descriptions scraped in November 2014.
-In contrast to Kickstarter, in a vast majority of cases GoFundMe contributors don't have the option to select compensentory rewards, and we therefore regard our GoFundMe data as requests for purely altruistic actions.
+In contrast to Kickstarter, in a vast majority of cases GoFundMe contributors don't have the option to select compensatory rewards, and we therefore regard our GoFundMe data as requests for purely altruistic actions.
 
-To compare the language used on Kickstarter to purely commercial and purely altrustic pitches, we adopt a Bayesian approach that has previously been successful in comparing the language used by two political parties on a specific issue \cite{monroe2008fightin}.
-In a general sense, this model has been used to compare word usage between two related corpora in a princpled way.
+To compare the language used on Kickstarter to purely commercial and purely altruistic pitches, we adopt a Bayesian approach that has previously been successful in comparing the language used by two political parties on a specific issue \cite{monroe2008fightin}.
+In a general sense, this model has been used to compare word usage between two related corpora in a principled way.
 Under the model, language is modeled as a ``bag of words'' represented by a multinomial distribution over vocabulary items.
@@
 
-These rankings clearly illustrate the commecial language used on Amazon and the altruistic language used on GoFundMe, when compared to Kickstarter.
+These rankings clearly illustrate the commercial language used on Amazon and the altruistic language used on GoFundMe, when compared to Kickstarter.
 For instance, the most Amazon-like unigrams, ``easy,'' ``includes,'' ``with,'' ``has,'' and ``perfect,'' are highly sales oriented, whereas the most Kickstarter-like n-grams are more focused on personal appeals and promise of future improvement.
-Conversely, even a coursory examinination of the trigrams in the GoFundMe versus Kickstarter analysis reveals clear differences in lingustic content.
+Conversely, even a cursory examination of the trigrams in the GoFundMe versus Kickstarter analysis reveals clear differences in linguistic content.
 Project curators in the more altruistic setting are clearly more focused on personal appeals when compared to Kickstarter.
 
-To emperically analyze these n-gram comparisons, we first rank the n-grams in each experiment by their z-scores and compute Kendall's tau correlation between the Kickstarter vs.
+To empirically analyze these n-gram comparisons, we first rank the n-grams in each experiment by their z-scores and compute Kendall's tau correlation between the Kickstarter vs.
 Amazon and Kickstarter vs.
 GoFundMe analyses.
-The intuition behind this comparsion is as follows: if Kickstarter is more altruistic than Amazon, but less altruistic than GoFundMe, then we would expect altruistically-associated n-grams to be on opposite ends of each ranking.
+The intuition behind this comparison is as follows: if Kickstarter is more altruistic than Amazon, but less altruistic than GoFundMe, then we would expect altruistically-associated n-grams to be on opposite ends of each ranking.
 This phenomenon occurs for the z-scores of n-grams like ``friends and family'' (-48.86 to 27.24) ``thank you for'' (-112.63 to 20.38) and ``love'' (-75.63 to 23.83) as one might expect, but does it happen in general?
@@
 For all 2077 n-grams, we observe a statistically significant negative correlation between the rankings ($\tau = -.035, p = .016$).
-In addition, we compute rankings and correlation statistics for our 1119 unigrams, 1101 bigrams, and trigrams seperately.
+In addition, we compute rankings and correlation statistics for our 1119 unigrams, 1101 bigrams, and trigrams separately.
 As we shift our focus from unigrams ($\tau = -.024, p = .23$) to bigrams ($\tau = -.038, p = .061$) to trigrams ($\tau = -.041, p < .01$) the negative correlation between the rankings both becomes greater and more significant.
-This is likely because more lingustic signal can be carried by phrases of increasing length.
+This is likely because more linguistic signal can be carried by phrases of increasing length.
 
-Overall, we argue this analysis demonstrates that discourse on Kickstarter is neither entirely Amazon-like, nor entirely GoFundMe-like, but rather lies in its own lingustic regime at the intersection of altruism and commercialism.
+Overall, we argue this analysis demonstrates that discourse on Kickstarter is neither entirely Amazon-like, nor entirely GoFundMe-like, but rather lies in its own linguistic regime at the intersection of altruism and commercialism.
 \section{What do Altruistic Requests Look Like?}
@@
 To analyze the sequential structure of altruistic requests in a crowdfunding setting, we run a case study on a subset of data utilizing a content model \cite{barzilay2004catching} to produce a sentence clustering.
-A content model is an unsupervized learning algorithm that operates on the sentence level, takes information order into account, and learns transition probabilities between sentence types.
+A content model is an unsupervised learning algorithm that operates on the sentence level, takes information order into account, and learns transition probabilities between sentence types.
 Here we provide a brief overview of the content model algorithm; for a fuller description, consult the original paper.
@@
 For each of the resulting non-etcetera clusters, we train a smoothed bigram language model which is able to assign probabilities to input sentences.
-For the etcetera cluster, we train a ``complentary'' language model which assigns high probability to sentences that all other language models assign low probability to.
+For the etcetera cluster, we train a ``complementary'' language model which assigns high probability to sentences that all other language models assign low probability to.
 
@@
 
-In accordance with the reccomendations of the original authors, we attempt to map all named entities to a ``NAME'' token and all numbers to a ``NUM'' token.
+In accordance with the recommendations of the original authors, we attempt to map all named entities to a ``NAME'' token and all numbers to a ``NUM'' token.
 We use the default NLTK\footnote{\url{http://www.nltk.org/}} named entity recognizer to identify tokens to be mapped to ``NAME,'' and we map any token that parses to a float without error to ``NUM.''
@@
 We utilize 11 content clusters and 1 etcetera cluster in our model.
-Though the original literature sugguests a larger number of clusters (30+) we opt for a smaller, interpretable analysis because our resulting model was not used for any information ordering or information extraction tasks, as in \cite{barzilay2004catching}.
+Though the original literature suggests a larger number of clusters (30+) we opt for a smaller, interpretable analysis because our resulting model was not used for any information ordering or information extraction tasks, as in \cite{barzilay2004catching}.
 After our expectation maximization converged after nine iterations, we were left with the order-aware sentence clusters displayed in Table \ref{tab:contentmodel} (etcetera cluster omitted).
@@
 
-For the remaineder of this analysis, we are going to focus on the cluster containing 254 sentences (dubbed the ``Thank you'' cluster) and the cluster containing 272 sentences (dubbed the ``Introduction'' cluster).
+For the remainder of this analysis, we are going to focus on the cluster containing 254 sentences (dubbed the ``Thank you'' cluster) and the cluster containing 272 sentences (dubbed the ``Introduction'' cluster).
 Though there are many interesting things that can be learned from the transition probabilities output by the content model, the most interpretable fact is illustrated in Figure \ref{fig:docpos}.
@@
 \begin{equation} \label{eq:sentpos}
-\sum\limits_{k \in \text{Occurances of $c$}} \frac{\text{Position of $k$ in containing sentence}}{\text{Length of sentence containing $k$}}
+\sum\limits_{k \in \text{Occurrences of $c$}} \frac{\text{Position of $k$ in containing sentence}}{\text{Length of sentence containing $k$}}
 \end{equation}
@@
 In a similar vein to \cite{mitra2014language} we define a binary altruistic response variable and train several logistic regression classifiers to predict that variable.
-The response variable is defined as follows: if a project recieves any donations and the proportion of altruistic donations it recieves exceeds $10\%$, we assign it to the altruistic group, otherwise, it is assigned to the non-altruistic group.
-We can interpret this binary variable as ``recieved more than an average number of altruistic donations.'' Defining this control variable partitions the dataset into 26733 altruistic projects and 19077 non-altruistic projects giving a constant prediction baseline of 58.34\% accuracy.
+The response variable is defined as follows: if a project receives any donations and the proportion of altruistic donations it receives exceeds $10\%$, we assign it to the altruistic group, otherwise, it is assigned to the non-altruistic group.
+We can interpret this binary variable as ``received more than an average number of altruistic donations.'' Defining this control variable partitions the dataset into 26733 altruistic projects and 19077 non-altruistic projects giving a constant prediction baseline of 58.34\% accuracy.
 
@@
 Furthermore, we set glmnet to perform 10-fold cross validation to search for the optimal regularization coefficient and prevent overfitting.
-In addition to training a model on all the data using cross-validation, as a seperate measure of model generalizability we also report test accuracy when spliting our data into a 40k project training set and a 5k project test set.
-Notably, glmnet purposefully does not report standard errors on resulting feature coefficients because the regularization process intorudces substantial bias into the regression process.
+In addition to training a model on all the data using cross-validation, as a separate measure of model generalizability we also report test accuracy when splitting our data into a 40k project training set and a 5k project test set.
+Notably, glmnet purposefully does not report standard errors on resulting feature coefficients because the regularization process introduces substantial bias into the regression process.
 
@@
 Dance, theater, public art, performance art, and classical music ($\vec{\beta} = \langle 1.84, 1.56, 1.24, 1.04, .930 \rangle$, respectively) were the categorical variables which were the strongest positive predictors, whereas board/card games, games, comics, video games, and product design ($\vec{\beta} = -\langle 1.64, 1.23, 1.02, .862, .795 \rangle$, respectively) were the strongest negative predictors.
-This result indicates that product category is the most important factor in determining if a project will recieve altruistic donations, and perhaps that projects in artistic categories are more likely to recieve such Kickstarter backing.
-This result is fairly unsurprising -- artistic endevours are generally regarded as intrinsically valuable to society, as evidenced by the existance of organizations like the National Endowment of the Arts which has, to date, awarded more than 5B dollars for artistic endevours\footnote{\url{http://arts.gov/about-nea}}.
+This result indicates that product category is the most important factor in determining if a project will receive altruistic donations, and perhaps that projects in artistic categories are more likely to receive such Kickstarter backing.
+This result is fairly unsurprising -- artistic endeavours are generally regarded as intrinsically valuable to society, as evidenced by the existence of organizations like the National Endowment of the Arts which has, to date, awarded more than 5B dollars for artistic endeavours\footnote{\url{http://arts.gov/about-nea}}.
 The negatively predictive categories tend to have concretely associated products with their projects (a video game, for instance) and backers likely pre-order instead of donate, in general.
@@
 The most important non-categorical positive predictor was having a video (binary variable, $\beta = .45$).
-On the other hand, being featured (binary variable, $\beta = -.183$) and having many comments on a project (interger variable, $\beta = -.00168$) were associated with less altruistic donations.
+On the other hand, being featured (binary variable, $\beta = -.183$) and having many comments on a project (integer variable, $\beta = -.00168$) were associated with less altruistic donations.
 
@@
 \end{tabular}
-\caption{The top 15 positive and negative lingustic predictors of the binary variable ``did this project recieve an above average proportion of altruistic donations'' in the controls + n-grams model.}
+\caption{The top 15 positive and negative linguistic predictors of the binary variable ``did this project receive an above average proportion of altruistic donations'' in the controls + n-grams model.}
 \label{tab:regression}
@@
 
-When we incorporate these particular lingustic features as binary indicator variables, our cross-validation accuracy increases to 67.02\% (2.49\% improvement over controls-only baseline) and our testing accuracy increases to 66.68\% (2.88\% improvement).
-The inclusion of lingustic features, therefore, causes our predictive accuracy to increase slightly but significantly.
+When we incorporate these particular linguistic features as binary indicator variables, our cross-validation accuracy increases to 67.02\% (2.49\% improvement over controls-only baseline) and our testing accuracy increases to 66.68\% (2.88\% improvement).
+The inclusion of linguistic features, therefore, causes our predictive accuracy to increase slightly but significantly.
 
 Which n-grams are most predictive of greater-than-average donation frequency?
-The top 15 most significant positive and negative predictive lingustic features along with their corresponding regression coefficients are displayed in Table \ref{tab:regression}.
+The top 15 most significant positive and negative predictive linguistic features along with their corresponding regression coefficients are displayed in Table \ref{tab:regression}.
 
-Are there any discernable patterns among these n-grams?
-An examination of the most positive-predicting linguistic features reveals that the advertisement of academic affiliation is a strong predictor of recieving a higher-than-average number of altruistic donations.
+Are there any discernible patterns among these n-grams?
+An examination of the most positive-predicting linguistic features reveals that the advertisement of academic affiliation is a strong predictor of receiving a higher-than-average number of altruistic donations.
 The usage of ``universitys'' and ``my senior,'' in particular illustrate this point.
@@
 \end{blockquote}
-Furthermore, it seems that lingustic features that make commands of backers (``get in on,'' ``must make'') are negative predictors of donations.
+Furthermore, it seems that linguistic features that make commands of backers (``get in on,'' ``must make'') are negative predictors of donations.
 \begin{blockquote}
@@
 \section{Failing Projects, More Donations?}
-What is the relationship between project success and the proportion of altruistic donations a project recieves?
+What is the relationship between project success and the proportion of altruistic donations a project receives?
 One might reasonably expect that successful projects, having higher quality pitches and commanding more donations on average, would also have a higher proportion of altruistic donations.
-In fact, the conclusions based on the analysis in this section find the \emph{opposite} to be true -- we find that, in fact, that there is a consistent negative association between project success and proportion of altruistic donations recieved.
+In fact, the conclusions based on the analysis in this section find the \emph{opposite} to be true -- we find that, in fact, that there is a consistent negative association between project success and proportion of altruistic donations received.
 
 To address this question, we first run a new lasso penalized regression task where predictive variables consist of the control variables highlighted in Table \ref{tab:controls} plus two additional binary variables, namely ``success,'' which indicates whether or not the funding goal of the project was reached, and ``numBackers,'' the total number of backers for a given project.
-The target of this new regression is the proportion of altruistic donations a project recieves.
+The target of this new regression is the proportion of altruistic donations a project receives.
 Because our target is a ratio that is highly sensitive to noise if the number of project backers is small, we restrict our consideration to the 30858 projects in our dataset with 10 or more backers (though the results presented here are robust to reasonable changes in this threshold).
@@
 Surprisingly, our resulting regression assigns negative weights to both our new predictive variables.
-With respect to the number of backers, the negative weight indicates that more popular projects are less likely to recieve altruistic donations, in general.
-More surprising, however, is that after controling for all variables in Table \ref{tab:controls} and project size, successful projects recieve \emph{less} altruistic donations than unsuccessful projects.
+With respect to the number of backers, the negative weight indicates that more popular projects are less likely to receive altruistic donations, in general.
+More surprising, however, is that after controlling for all variables in Table \ref{tab:controls} and project size, successful projects receive \emph{less} altruistic donations than unsuccessful projects.
 
@@
 
-For the event donation frequencies, there is a clear pattern: in 12 of the 13 Kickstarter categories (the exception being ``Food'') failing projects recieve a higher proportion of altruistic donations, on average.
+For the event donation frequencies, there is a clear pattern: in 12 of the 13 Kickstarter categories (the exception being ``Food'') failing projects receive a higher proportion of altruistic donations, on average.
 In seven of the thirteen categories, this result is significant at the 5\% level.
 For categories with large numbers of projects, this result is often highly significant.
-For instance, in the two most popular Kickstarter categories, ``Music'' and ``Film and Video,'' we observe a that failed projects recieve, on average, significantly more altruistic donation events (Student's t-test, $p<<.001$ in both cases).
+For instance, in the two most popular Kickstarter categories, ``Music'' and ``Film and Video,'' we observe a that failed projects receive, on average, significantly more altruistic donation events (Student's t-test, $p<<.001$ in both cases).
 Sample plots of the event distributions are presented in the first row of Figure \ref{fig:failsucc}.
@@
 In the ``Film and Video'' category, for instance, we observe a total reversal, a significant result ($p << .001$) that states successful projects receive more dollars altruistically than failed projects.
-In fact, over all categories all statistically significant results state that successful projects recieve more funding.
+In fact, over all categories all statistically significant results state that successful projects receive more funding.
 In the ``Music'' category, however, the test statistic is close to zero, and the difference is no longer significant as it was in the event-based analysis.
@@
 
-What does this discrepency between events and dollar value mean?
-We suspect that the many significant results for our event-based analysis indicate that, indeed, failing projects recieve, on average, more altruistic donation events.
+What does this discrepancy between events and dollar value mean?
+We suspect that the many significant results for our event-based analysis indicate that, indeed, failing projects receive, on average, more altruistic donation events.
 However, the value of these donations is likely small, as many of these results don't hold when actual dollar values are considered.
 
-We believe that this result sugguests the following scenario is common across many categories: a Kickstarter user observes that a project is failing and makes a small donation, but requests no reward.
-It has been shown that feelings of sympathy can elicit prosocial behavior, even if the interaction can be easily avoided, as it would be by anonymously closing a browswer window \cite{eisenberg1989relation}.
+We believe that this result suggests the following scenario is common across many categories: a Kickstarter user observes that a project is failing and makes a small donation, but requests no reward.
+It has been shown that feelings of sympathy can elicit prosocial behavior, even if the interaction can be easily avoided, as it would be by anonymously closing a browser window \cite{eisenberg1989relation}.
 If the cost of such an altruistic action is too high, however, it has a lower probability of being taken \cite{batson1983influence}.
-Though an assignment of altruistic donations to values directly would be valuable to our analysis, given the data that Kickstarter makes public, there is no way to directly compute the value of the altruistic donation events themselves, and we leave a more detailed analysis to future work on a seperate dataset.
+Though an assignment of altruistic donations to values directly would be valuable to our analysis, given the data that Kickstarter makes public, there is no way to directly compute the value of the altruistic donation events themselves, and we leave a more detailed analysis to future work on a separate dataset.
 
 Our hypothesis regarding low-cost donations fits very well into the framework established by previous psychological studies, assuming that feelings of sympathy are the driving force behind donation to failing projects.
-The existance and popularity of website entitled KickEnded\footnote{\url{http://kickended.com/about}} lends crediability to this theory.
+The existence and popularity of website entitled KickEnded\footnote{\url{http://kickended.com/about}} lends credibility to this theory.
 On KickEnded, finished Kickstarter projects with zero backers are archived so that they may ``live a second life...
-free from the pressure of money raising.'' The notion that commercial success does not equate to societial value is a highly sympathetic one.
+free from the pressure of money raising.'' The notion that commercial success does not equate to societal value is a highly sympathetic one.
 Though this evidence is rather indirect, it is a fairly strong indicator of the dynamics underlying our data.
@@
 Assuming our hypothesis is correct, several interesting questions arise.
-Who are these low-cost altruistic donators?
-Are their motiviations sympathetic, as the psychology literature and Kickended's popularity sugguest?
+Who are these low-cost altruistic donors?
+Are their motivations sympathetic, as the psychology literature and Kickended's popularity suggest?
 Are there sub-communities of altruistic users?
 Are there community-derived benefits to making altruistic donations on Kickstarter?
-These specific questions would be best answered by Kickstarter users themselves; interesting future work might include questionaires sent out to a specifically targeted subset of users.
+These specific questions would be best answered by Kickstarter users themselves; interesting future work might include questionnaires sent out to a specifically targeted subset of users.
 
@@
 Our first analysis positioned Kickstarter somewhere between purely altruistic and purely commercial linguistic regimes.
-Next, as we examined the sequential structure of purely altruistic requests on GoFundMe and found that a content model was capable of learning an interpretable set of content-aware clusters that illustrate some of the stratigies authors use to ellicit donations.
+Next, as we examined the sequential structure of purely altruistic requests on GoFundMe and found that a content model was capable of learning an interpretable set of content-aware clusters that illustrate some of the strategies authors use to elicit donations.
 Then, noting that both event-based and amount-based altruistic activities can be determined based on the information presented on a Kickstarter page, we were able to extract the important linguistic features responsible for prediction of above-average donation levels.
-Finally, we made the surprising observation that failing projects tend to recieve more donation events, even after accounting for a wide range of control variables.
-This increased donation does not carry over to our amount-based analysis, however, sugguesting that failing projects recieve a large number of low-valued donations.
+Finally, we made the surprising observation that failing projects tend to receive more donation events, even after accounting for a wide range of control variables.
+This increased donation does not carry over to our amount-based analysis, however, suggesting that failing projects receive a large number of low-valued donations.
 
 Overall, much more work could be done to analyze the dynamics of altruistic behavior on crowdfunding sites, and in ``mixed-altruism'' domains in general.
-As previously sugguested, one possible avenue for future research would be to identify and reach out to a subset of Kickstarter users that are likely to be responsible for frequent, low-valued donations given to failing projects.
+As previously suggested, one possible avenue for future research would be to identify and reach out to a subset of Kickstarter users that are likely to be responsible for frequent, low-valued donations given to failing projects.
 Another interesting avenue for exploration might be to identify and find similarities between other communities like Kickstarter.

### 2014-12-19 AltruisticLanguage/ContentModel/Interpret.py
updates

@@ -28,7 +28,7 @@ def interpretClusters(clusterFileName):
         topTen = sorted(counts.iteritems(), key=operator.itemgetter(1))[::-1][:20]
         #print cluster
         string = str(len(sents)) + ' & \specialcell{'
-        for i in range(5):
+        for i in range(3):
             string += '`' + topTen[i][0].replace('numnumnumnum', '\#') + '\'\\\\'
         string = string[:-2]
         string += '}\\\\\\hline'
@@ -44,6 +44,7 @@ def interpretPaths(pathsFile):
             tokens[-1] = tokens[-1][:-1]
             for t in tokens:
                 tokens2 = t.split(',')
+                #if int(tokens2[1]) == -1: continue
                 docSents[curDoc].append((tokens2[0][1:-1], int(tokens2[1])))
             curDoc += 1
     lengths = Counter()
@@ -56,9 +57,11 @@ def interpretPaths(pathsFile):
     seqDict = defaultdict(list)
     clusterPosDict = defaultdict(list)
     for doc, sents in docSents.iteritems():
+        #seqDict[len([s for s in sents if s[1] != -1])].append([s[1] for s in sents if s[1] != -1])
         seqDict[len(sents)].append([s[1] for s in sents])
         for i in range(len(sents)):
-            clusterPosDict[s[1]].append(1.*i/len(sents))
+            s = sents[i]
+            clusterPosDict[s[1]].append((1.*i)/len(sents))
             clusterCounts[s[1]] += 1
     stateSet = set()
     for length, sequences in seqDict.iteritems():
@@ -66,29 +69,26 @@ def interpretPaths(pathsFile):
     
     clusterAveragePosDict = {}
     for cluster, posList in clusterPosDict.iteritems():
-        clusterAveragePosDict[cluster] = sum(posList)/len(posList)
-
+        if cluster in [314, 588]:
+            plt.hist(posList, color = 'g' if cluster == 314 else 'b', alpha=.5,
+                     label = "Introduction" if cluster == 314 else "Thank you", normed = True)
+        else: plt.hist(posList, color = 'k', alpha = .1, normed = True)
+        clusterAveragePosDict[cluster] = (1.0*sum(posList))/len(posList)
+    plt.xlabel("Average Position in Document", fontsize=18)
+    plt.legend(loc='upper center')
+    plt.savefig("final.png")
+    plt.close()
+    plt.figure()
+    quit()
[…]

### 2014-12-19 AltruisticLanguage/EDA.py

@@ -642,6 +642,12 @@ def compareMineToTheirs(projects):
 def main():
     projects = loadProjects('output')
     projects = [p for p in projects if len(p.category) != 0]
+    minDate = min([p.startDate for p in projects])
+    maxDate = max([p.endDate for p in projects])
+    
+    print minDate
+    print maxDate
+
     #categoryAltruisticPropTest(projects)
     #basicStats(projects)
     #texts = [p.text for p in projects]
@@ -652,7 +658,7 @@ def main():
     #saveFeatureMatrixAndHeaders(projects, "dataBinaryTheirs.mtx",
     #                            "target.csv", "headersTheirs.csv", given="KS.predicts",
     #                            counts=False)
-    saveFeatureMatrixAndHeaders(projects, "all90Filter.mtx", "allHeaders90Filter.csv", control=False)
+    #saveFeatureMatrixAndHeaders(projects, "all90Filter.mtx", "allHeaders90Filter.csv", control=False)
 
     #target = np.zeros([len(projects), 1], dtype=np.int)
     

### 2014-12-19 AltruisticLanguage/failSucc.py

@@ -32,6 +32,7 @@ def categoryValueTest(projects):
         plt.legend(loc='upper right', fontsize=18)
         plt.title(cat, fontsize=18)
         plt.xlabel("Proportion Altruistic", fontsize=18)
+        plt.axes().get_yaxis().set_visible(False)
         plt.savefig("catGraphs/" + cat + "events.png")
         plt.close()
 
@@ -46,6 +47,7 @@ def categoryValueTest(projects):
         plt.legend(loc='upper right', fontsize=18)
         plt.title(cat, fontsize=18)
         plt.xlabel("Proportion Altruistic", fontsize=18)
+        plt.axes().get_yaxis().set_visible(False)
         plt.savefig("catGraphs/" + cat + "vals.png")
         plt.close()
         plt.figure()

### 2014-12-19 AltruisticLanguage/regressionFinal.R

@@ -86,9 +86,19 @@ topBottomK <- function(cvReg, k) {
   print("TOP")
   print(apply(myCoefMatrix, 2, rsort)[1:k,])
 }
+
+orderedCoefs <- function(cvReg) {
+  bestlambda<-cvReg$lambda.min
+  mse.min <- cvReg$cvm[cvReg$lambda == bestlambda]
+  print(1-mse.min)
+  myCoefs <- coef(cvReg, s=bestlambda)
+  myCoefMatrix <- as.matrix(myCoefs)
+  return(apply(myCoefMatrix, 2, sort))
+}
+
 topK <- 50
 topBottomK(control, topK)
 topBottomK(noSW, topK)
 topBottomK(SW, topK)
 topBottomK(test2, topK)
-# 
+write.table(orderedCoefs(SW), file = "testFile.csv")

### 2015-01-08 AltruisticLanguage/ContentModel/ContentModel.py
contentModel

@@ -13,16 +13,19 @@ from loadbar import LoadBar
 import numpy as np
 import random
 from collections import Counter, defaultdict
+import regexStore
+import os
 
 class ContentModel:
     def __init__(self, langModel = 'bigram',
-                 numClusters = 1275,
-                 minProportion = .007,
+                 numClusters = 5,#3000,
+                 minProportion = .002,
                  clusterTrainProp = 1, 
                  d1 = .00000005,
                  d2 = .001,
                  cleanSents = None,
-                 saveFile = None):
+                 saveFile = None,
+                 name = "success"):
         '''Params= numClusters, minimum cluster proportional size to not be absorbed
         into etc cluster, and (optionally) somewhere to load/save cleaned sentences from/to.'''
         self.langModel = langModel
@@ -35,7 +38,17 @@ class ContentModel:
         self.saveFile = saveFile
         self.wsTokenizer = WhitespaceTokenizer()
 
+        #model itself
+        self.name = name
+        self.lms = None
+        self.transProbs = None
+
     def train(self, documentsIn):
+        if not os.path.exists(self.name):
+            os.makedirs(self.name)
+        #os.system("cd " + self.name)
+        #os.system("rm -rf *")
+        #os.system("cd ..")
         if self.langModel is not 'bigram': warnings.warn("Language model unsupported, using bigram")
         bar = LoadBar(30)
         random.shuffle(documentsIn)
@@ -54,6 +67,7 @@ class ContentModel:
                 print "Saving cleaned sentences to " + self.saveFile
                 with open(self.saveFile, 'w') as f:
                     pickle.dump(self.cleanSents, f, -1)
+
         print "There were " + str(len(self.cleanSents)) + " sentences."
         self.cleanSents = self.cleanSents[:int(np.floor(len(self.cleanSents)*self.clusterTrainProp))]
         print "Counting vocab..."
@@ -84,7 +98,7 @@ class ContentModel:
             observedSeq = [x[1] for x in sents]
 
         #VITERBI OPTIMIZATION
-        for i in range(10):
+        for i in range(100):
             print "Iteration " + str(i)
             
             print "Training language models"
@@ -111,7 +125,7 @@ class ContentModel:
                 docDict[self.cleanSents[i][1]].append((self.cleanSents[i][0], clusters[i]))
 
             print "Estimating transition probabilities"
-            transProbs = self.getTransitionProbs(allClusters, docDict, m)
[…]

### 2015-01-08 AltruisticLanguage/writing/paper.tex
angry commit -- lost a lot of data

@@
 
-\begin{table}
+\begin{table}[t]
 \centering
@@
 While this result is somewhat unsurprising (situations are introduced before authors thank readers) it demonstrates that the content model is able to learn useful information about ordering in an unsupervised fashion, and that aspects of the sequential nature of altruistic requests are learnable by this method.
+We later use more complex content models for an order-aware classification task on Kickstarter.
 
@@
 
-Using a model consisting of controls only, we achieve a cross-validation accuracy of 64.53\% (6.19\% improvement over constant prediction) and a testing set accuracy of 63.80\% (5.46\% improvement).
+Using a model consisting of controls only, we achieve a cross-validation accuracy of 64.53\% (6.19\% improvement over constant prediction) and a testing set accuracy of 63.80\% (5.46\% improvement, .649 precision/.837 recall).
 The most important positive and negative predictive features were all Kickstarter categorical control variables.
@@
 \hline
-Positive Predictors & Negative Predictor \\
+Positive Predictors & Negative Predictors \\
 \hline
@@
 
-When we incorporate these particular linguistic features as binary indicator variables, our cross-validation accuracy increases to 67.02\% (2.49\% improvement over controls-only baseline) and our testing accuracy increases to 66.68\% (2.88\% improvement).
+When we incorporate these particular linguistic features as binary indicator variables, our cross-validation accuracy increases to 67.02\% (2.49\% improvement over controls-only baseline) and our testing accuracy increases to 66.68\% (2.88\% improvement, .676 precision/.831 recall).
 The inclusion of linguistic features, therefore, causes our predictive accuracy to increase slightly but significantly.
+An examination of the precision and recall of both models indicates that adding lingustic features causes the logistic regression to become more selective in assigning the positive class (increased precision, decreased recall).
 
@@
 Are there any discernible patterns among these n-grams?
+Though the usage of any short sequence of words can vary considerably, we present here an examination of common usage for some of the n-grams of interest.
+
 An examination of the most positive-predicting linguistic features reveals that the advertisement of academic affiliation is a strong predictor of receiving a higher-than-average number of altruistic donations.
@@
 There are also some interesting patterns in the negatively-predicting n-grams.
-For instance, self-describing language appears to be a consistently negative predictor of altruistic donation.
-Though the usage of any short sequence of words can vary considerably, common usage of linguistic features like ``people that are,'' ``we going,'' ``so we know,'' and ``my website at'' demonstrate this phenomenon.
+For instance, self-describing, rather than product describing, language appears to be a consistently negative predictor of altruistic donation.
+Common usage of linguistic features like ``people that are,'' ``we going,'' ``so we know,'' and ``my website at'' demonstrate this phenomenon.
 \begin{blockquote}
@@
 \end{blockquote}
+It's likely this negative response is a manifestation of psychological reactance.
+This phenomenon occurs when one is threatened with loss of freedom of action, which, in this case, takes the form of commanding language.
+In most cases, humans will quickly seek to reestablish their freedoms \cite{brehm1966theory}.
+Here, it seems one consequence of this reaction is that users are less likely to donate altruistically to projects with commanding language.
+
 Finally, the portrayal of backer interaction with rewards also appears to have a significant effect on donations.
@@
 \end{blockquote}
-
 Overall, there are lots of interesting linguistic and psychological observations that can be made based on the most significant positive and negative language-based predictors.
 A full ordered list of n-grams along with associated regression coefficients is provided\footnote{PUT LINK HERE} if the reader is interested in performing their own analysis.
+
+\subsection{Sequential Classification Task}
+In our previous experiment, we reduced the dimensionality of text by mapping every description to a ``bag of words'' style vector of binary indicator variables for a set of topic-controlled n-grams.
+This method of analysis carries with it several advantages, the most important of which is interpretability.
+However, as with all bag of words style analyses, we disregard potentially useful ordered information.
+Could we derive additional predictive accuracy by accounting for order?
+
+To address this question, we return to the previously described content model algorithm.
+Due to limited computational resources, we limit our consideration to a subset of Kickstarter consisting of 900 project descriptions from the ``Photography'' category.
+Considering all 1.5k projects of this category in our dataset reveals that 58.4\% of photography projects are altruistically successful, according to our previous definition.
+Our 900 project descriptions consist of 450 projects which recieved above average numbers altruistic donations and 450 projects which recieved below average numbers of altruistic donations.
+We split our dataset into a training set consisting of 600 evenly distributed projects, and a test set of the remaining 300 evenly distributed projects.
+Next, we train two similar content models, one for the positive class and one for the negative class.
+After training these content models, for each of the projects in the test set, we compute the emission probability of that document from the positive and negative models, and assign the test document the label corresponding to the model that assigned it higher probability.
+
+For a comparison, we execute an additional logistic regression
+
 \begin{figure*}[t]

### 2015-01-08 AltruisticLanguage/EDA.py

@@ -413,7 +413,7 @@ def getValidGrams(projects, minOccur = 50, nGram = 3):
 
     return validGrams
 
-def extractTextFeatures(projects, minOccur = 50, nGram = 3, counts=False):
+def extractTextFeatures(projects, minOccur = 10, nGram = 2, counts=False):
     '''Given a list of projects, a minimum number of occurances, and maximum sized n-gram of interest, return a |projects| x |features| n-gram count matrix and list of n-grams in the order represented, given that the selected features appear in a least minOccur projects and at least once in every category. If counts = True, then the return matrix has counts features, if counts=False, then the return matrix has binary indicators'''
     #dict mapping from category -> set of n grams in that category
     catGramDict = defaultdict(set)
@@ -459,8 +459,8 @@ def extractTextFeatures(projects, minOccur = 50, nGram = 3, counts=False):
         for cat, catCount in catCounter.iteritems():
             perDocList.append((gramCatCounter[cat][v]*.1)/catCount)
         gramToVar[v] = 1.0*(np.max(perDocList)-np.min(perDocList))/np.max(perDocList)
-    validGrams = [x[0] for x in
-                  sorted(gramToVar.items(), key = operator.itemgetter(1))[:int(.9*len(gramToVar))]]
+    #validGrams = [x[0] for x in
+    #              sorted(gramToVar.items(), key = operator.itemgetter(1))[:int(.9*len(gramToVar))]]
 
     
     print "Using {} n-grams".format(len(validGrams))
@@ -587,7 +587,8 @@ def saveFeatureMatrixAndHeaders(projects, matrixOut, headersOut,
     if not control:
         data = np.concatenate([featureMatrix1,
                                featureMatrix2,
-                               featureMatrix3, numBackers, 
+                               featureMatrix3,
+                               numBackers, 
                                numAltruistic],axis = 1)
     else:
         data = np.concatenate([featureMatrix2,
@@ -596,7 +597,8 @@ def saveFeatureMatrixAndHeaders(projects, matrixOut, headersOut,
     if not control:
         headers = np.concatenate([ngrams,
                                   cats,
-                                  controls, targets])
+                                  controls,
+                                  targets])
     else:
         headers = np.concatenate([cats,
[…]

### 2015-01-08 AltruisticLanguage/languageOnly.R
better clean this up now...

@@ -1,0 +1,94 @@
+setwd("/home/jack/Desktop/NLP/CS6742/AltruisticLanguage")
+library('Matrix')
+library('glmnet')
+library('foreach')
+library('doParallel')
+registerDoParallel()
+rsort <- function(x) {
+  sort(x, decreasing = TRUE)
+}
+
+###
+data <- readMM("photoSmall.mtx")
+headers <- read.csv("photoSmall.csv")
+colnames(data) <- colnames(headers)
+target <- data[,c("numBackers", "numAltruistic")]
+target <- target[,2]/target[,1]
+target[is.nan(target)] <- 0
+target <- target > .1
+setwd("ContentModel")
+posProbs <- t(read.csv("probA.csv", header=F))
+negProbs <- t(read.csv("probB.csv", header=F))
+setwd("..")
+colnames(posProbs) <- c("PosProb")
+colnames(negProbs) <- c("NegProb")
+data <- cBind(data, negProbs)
+data <- cBind(data, posProbs)
+trainData <- data[1:600, -which(colnames(data) %in% c("numBackers","numAltruistic", "Osuccess"))]
+trainData <- trainData[-which(posProbs==0),]
+trainTarget <- target[1:600]
+trainTarget <- trainTarget[-which(posProbs==0)]
+######
+control <- cv.glmnet(trainData[,c(-which(colnames(trainData) %in% c("PosProb", "NegProb")), -grep("^T", colnames(trainData)))],
+                     trainTarget , family = "binomial", type.measure = "class", alpha = 0, parallel = F)
+
+holdoutNoCM <- cv.glmnet(trainData[,-which(colnames(trainData) %in% c("PosProb", "NegProb"))],
+                        trainTarget , family = "binomial", type.measure = "class", alpha = 0, parallel = F)
+
+holdout <- cv.glmnet(trainData,
+                    trainTarget , family = "binomial", type.measure = "class", alpha = 0, parallel = F)
+
+holdoutNoText <- cv.glmnet(trainData[,-grep("^T", colnames(trainData))],
+                           trainTarget , family = "binomial", type.measure = "class", alpha = 0, parallel = F)
+######
+predControl <- predict(control,
+                       data[601:nrow(data), c(-which(colnames(data) %in% c("numBackers","numAltruistic", "Osuccess", "PosProb", "NegProb")),
[…]

### 2015-01-08 AltruisticLanguage/regressionFinal.R

@@ -3,6 +3,7 @@ library('Matrix')
 library('glmnet')
 library('foreach')
 library('doParallel')
+library('AUC')
 registerDoParallel()
 rsort <- function(x) {
   sort(x, decreasing = TRUE)
@@ -20,9 +21,9 @@ colnames(dataSW) <- colnames(headersSW)
 colnames(dataNoSW) <- colnames(headersNoSW)
 colnames(dataControl) <- colnames(headersControl)
 
-dataControlTest2 <- dataControl[which(dataControl[,c("numBackers")]>=20),]
-target2 <- dataControl[which(dataControl[,c("numBackers")]>=20),c("numBackers", "numAltruistic")]
-target2 <- target2[,2]/target2[,1]
+#dataControlTest2 <- dataControl[which(dataControl[,c("numBackers")]>=20),]
+#target2 <- dataControl[which(dataControl[,c("numBackers")]>=20),c("numBackers", "numAltruistic")]
+#target2 <- target2[,2]/target2[,1]
 
 target <- dataControl[,c("numBackers", "numAltruistic")]
 target <- target[,2]/target[,1]
@@ -44,7 +45,7 @@ SW <- cv.glmnet(dataSW[,-which(colnames(dataSW) %in% c("numBackers","numAltruist
                 type.measure = "class",
                 alpha = 1, parallel = T)
 
-test2 <- cv.glmnet(dataControlTest2[,-which(colnames(dataControlTest2) %in% c("numAltruistic"))], target2, family='gaussian', alpha=1, parallel = T)
+#test2 <- cv.glmnet(dataControlTest2[,-which(colnames(dataControlTest2) %in% c("numAltruistic"))], target2, family='gaussian', alpha=1, parallel = T)
 
 holdoutNoSW <- cv.glmnet(dataNoSW[1:40000,-which(colnames(dataNoSW) %in% c("numBackers","numAltruistic", "Osuccess"))],
                        target[1:40000], family = "binomial", type.measure = "class", alpha = 1, parallel = T)
@@ -63,17 +64,32 @@ sum(predict(holdoutNoSW,
     == target[40001:nrow(dataNoSW)])/(length(target[40001:nrow(dataNoSW)]))
 
 print("SW Holdout Accuracy")
-sum(predict(holdoutSW,
-            dataSW[40001:nrow(dataSW),-which(colnames(dataSW) %in% c("numBackers","numAltruistic", "Osuccess"))],
-            type='class')
[…]

### 2015-01-08 AltruisticLanguage/ContentModel/regexStore.py
added regexStore

@@ -1,0 +1,1 @@
+urlReg = '\S*\.(com|net|ly|be|edu)'

### 2015-01-08 AltruisticLanguage/ContentModel/ForwardAlg.py
added forward alg stuff

@@ -1,0 +1,56 @@
+import numpy as np
+
+def emissionProb(initProb, transProb, observation, lms):
+    '''Log-scale forward algorithm from
+    http://bozeman.genome.washington.edu/compbio/mbt599_2006/hmm_scaling_revised.pdf
+    Assumption: everything already comes in logscale.
+    initProb: {state -> initProb}
+    transProb: {(state1, state2) -> transProb}
+    observation: [sentence1, sentence2, ...]
+    lms: {state -> language model (with logProb function)}'''
+    def elnsum(elnx,elny):
+        if elnx == "LZ" or elny == "LZ":
+            if elnx == "LN":
+                return elny
+            else:
+                return elnx
+        else:
+            if elnx > elny:
+                return elnx + np.log(1 + np.exp(elny-elnx))
+            else:
+                return elny + np.log(1 + np.exp(elnx-elny))
+    def elnprod(elnx, elny):
+        if elnx == "LZ" or elny == "LZ":
+            return "LZ"
+        else:
+            return elnx + elny
+
+    states = lms.keys()
+    M = np.zeros(len(lms), len(observation))
+    for i in range(len(states)):
+        curState = states[i]
+        M[i,0] = elnprod(initProb[i], lms[curState].logProb(observation[0]))
+    for i in range(1, len(observation)):
+        for j in range(len(states)):
+            curObs = observation[i]
+            curState = states[j]
+            logalpha = "LZ"
+            for k in range(len(states)):
+                logalpha = elnsum(logalpha, elnprod(M[k, i-1], transProbs[(states[k],curState)]))
+            M[j,i] = elnprod(logalpha, states[j].logProb(curObs))
+    
+
+    finalAns = "LZ"
+    for i in range(len(states)):
+        finalAns = elnsum(finalAns, M[states[i], len(observation)-1])
+    return finalAns
+
+def getStartProbs(inFile, smooth = .01):
+    '''Given a paths file, return a dictionary {states -> logged init prob}'''
+    return -1
+
+def main():
+    pass
+
+if __name__ == "__main__":
+    main()

### 2015-01-10 AltruisticLanguage/ContentModel/ContentModel.py
rewrote the forward alg

@@ -16,9 +16,10 @@ from collections import Counter, defaultdict
 import regexStore
 import os
 
+#for music data, 3000, .002
 class ContentModel:
     def __init__(self, langModel = 'bigram',
-                 numClusters = 5,#3000,
+                 numClusters = 3000,
                  minProportion = .002,
                  clusterTrainProp = 1, 
                  d1 = .00000005,
@@ -46,9 +47,6 @@ class ContentModel:
     def train(self, documentsIn):
         if not os.path.exists(self.name):
             os.makedirs(self.name)
-        #os.system("cd " + self.name)
-        #os.system("rm -rf *")
-        #os.system("cd ..")
         if self.langModel is not 'bigram': warnings.warn("Language model unsupported, using bigram")
         bar = LoadBar(30)
         random.shuffle(documentsIn)
@@ -154,9 +152,14 @@ class ContentModel:
 
             print "Saving model..."
             for cluster, model in self.lms.iteritems():
-                with open(self.name + "/" + str(cluster) + ".lm", 'w') as f:
-                    print cluster
-                    pickle.dump(model, f, -1)
+                if cluster == -1:
+                    with open(self.name + "/etcWordToIndex.pickle",'w') as f:
+                        pickle.dump(model.wordToIndex, f, -1)
+                    with open(self.name + "/etcMatrix.npy", 'w') as f:
+                        np.save(f, model.oneMinusMaxPsiMatrix)
+                else:
+                    with open(self.name + "/" + str(cluster) + ".lm", 'w') as f:
+                        pickle.dump(model, f, -1)
             with open(self.name + '/' + "transProbs", 'w') as f:
                 pickle.dump(self.transProbs, f, -1)
             if newClusters == clusters:
@@ -167,13 +170,13 @@ class ContentModel:
         docDict = defaultdict(list)
         for i in range(len(self.cleanSents)):
             docDict[self.cleanSents[i][1]].append((self.cleanSents[i][0], clusters[i]))
-        with open(self.name + "docPathsOut.txt",'w') as f:
+        with open(self.name + "/docPathsOut.txt",'w') as f:
             for doc, sentsClusters in docDict.iteritems():
                 for sc in sentsClusters:
                     f.write(str(sc))
                 f.write("\n")
 
-        with open(self.name + "clustersOut.txt",'w') as f:
+        with open(self.name + "/clustersOut.txt",'w') as f:
             for i in range(len(self.cleanSents)):
                 clustSent = defaultdict(list)
                 for i in range(len(self.cleanSents)): 

### 2015-01-10 AltruisticLanguage/ContentModel/ForwardAlg.py

@@ -1,4 +1,10 @@
 import numpy as np
+import sys
+import os
+from LanguageModel import *
+import cPickle as pickle
+from collections import defaultdict
+from loadbar import LoadBar
 
 def emissionProb(initProb, transProb, observation, lms):
     '''Log-scale forward algorithm from
@@ -10,7 +16,7 @@ def emissionProb(initProb, transProb, observation, lms):
     lms: {state -> language model (with logProb function)}'''
     def elnsum(elnx,elny):
         if elnx == "LZ" or elny == "LZ":
-            if elnx == "LN":
+            if elnx == "LZ":
                 return elny
             else:
                 return elnx
@@ -26,31 +32,87 @@ def emissionProb(initProb, transProb, observation, lms):
             return elnx + elny
 
     states = lms.keys()
-    M = np.zeros(len(lms), len(observation))
+    M = np.zeros((len(lms), len(observation)))
     for i in range(len(states)):
         curState = states[i]
-        M[i,0] = elnprod(initProb[i], lms[curState].logProb(observation[0]))
+        M[i,0] = elnprod(initProb[states[i]], lms[curState].logProb(observation[0]))
     for i in range(1, len(observation)):
         for j in range(len(states)):
             curObs = observation[i]
             curState = states[j]
             logalpha = "LZ"
             for k in range(len(states)):
-                logalpha = elnsum(logalpha, elnprod(M[k, i-1], transProbs[(states[k],curState)]))
-            M[j,i] = elnprod(logalpha, states[j].logProb(curObs))
-    
+                logalpha = elnsum(logalpha, elnprod(M[k, i-1], transProb[(states[k],curState)]))
+            M[j,i] = elnprod(logalpha, lms[states[j]].logProb(curObs))
 
     finalAns = "LZ"
     for i in range(len(states)):
-        finalAns = elnsum(finalAns, M[states[i], len(observation)-1])
+        finalAns = elnsum(finalAns, M[i, len(observation)-1])
     return finalAns
 
-def getStartProbs(inFile, smooth = .01):
+def loadContentClusters(folder):
+    '''Given a folder, returns a dictionary mapping {cluster -> model} for the content
+    clusters.'''
+    returnDict = {}
+    for i in os.listdir(folder):
+        if i.endswith(".lm"):
+            with open(folder + "/" + i) as f:
[…]

### 2015-01-10 AltruisticLanguage/ContentModel/LanguageModel.py

@@ -25,6 +25,9 @@ class LanguageModel:
         pass
 
 class ETCBigramModel(LanguageModel):
+    def __init__(self):
+        '''Argumentless version for classification purposes.'''
+        pass
     def setParams(self, parameters):
         '''Here, we expect parameters in the form ([otherLM1, otherLM2, ...]) where
         the other LMs are REQUIRED to have the function bigramProb(bigram)'''
@@ -56,6 +59,8 @@ class ETCBigramModel(LanguageModel):
         self.loader.clear()
 
     def bigramProb(self, bigram):
+        if bigram[0] not in self.wordToIndex or bigram[1] not in self.wordToIndex:
+            return .000000000001
         numer = self.oneMinusMaxPsiMatrix[self.wordToIndex[bigram[0]],
                                           self.wordToIndex[bigram[1]]]
         denom = self.getDenom(bigram[0])

### 2015-01-10 AltruisticLanguage/ContentModel/ForwardAlg.py
this works I think

@@ -111,8 +111,9 @@ def main():
         if bar.test(docCount, len(docSents)): bar += 1
         numTokens = sum([len(s.split()) for s in curSents])
         probs.append(emissionProb(startProb, transProb, curSents, lms) / numTokens)
+        docCount += 1
     bar.clear()
     with open(outFile,'w') as f:
-        f.write(','.join(probs) + "\n")
+        f.write(','.join([str(p) for p in probs]) + "\n")
 if __name__ == "__main__":
     main()

### 2015-01-12 AltruisticLanguage/ContentModel/ContentModel.py
updates

@@ -17,10 +17,12 @@ import regexStore
 import os
 
 #for music data, 3000, .002
+#succ 1415, .004 -> 33 clusters
+#fail 1350, .004 -> 32 clusters
 class ContentModel:
     def __init__(self, langModel = 'bigram',
-                 numClusters = 3000,
-                 minProportion = .002,
+                 numClusters = 1350,
+                 minProportion = .004,
                  clusterTrainProp = 1, 
                  d1 = .00000005,
                  d2 = .001,
@@ -44,27 +46,11 @@ class ContentModel:
         self.lms = None
         self.transProbs = None
 
-    def train(self, documentsIn):
+    def train(self):
         if not os.path.exists(self.name):
             os.makedirs(self.name)
         if self.langModel is not 'bigram': warnings.warn("Language model unsupported, using bigram")
         bar = LoadBar(30)
-        random.shuffle(documentsIn)
-        if self.cleanSents is None:
-            print "Parsing/cleaning sentences"
-            self.cleanSents = []
-            bar.setup()
-            for i in range(len(documentsIn)):
-                if bar.test(i, len(documentsIn)): bar += 1
-                d = documentsIn[i]
-                sents = [( self.cleanSentence(x, properNames = "name"*4, numbers = "num"*4) , i)
-                         for x in self.stringToSentences(d)]
-                self.cleanSents.extend(sents)
-            bar.clear()
-            if self.saveFile is not None:
-                print "Saving cleaned sentences to " + self.saveFile
-                with open(self.saveFile, 'w') as f:
-                    pickle.dump(self.cleanSents, f, -1)
 
         print "There were " + str(len(self.cleanSents)) + " sentences."
         self.cleanSents = self.cleanSents[:int(np.floor(len(self.cleanSents)*self.clusterTrainProp))]
@@ -280,31 +266,18 @@ class ContentModel:
         return [y for y in x if len(y.split()) >= 1] 
 
 def main():
-    if len(sys.argv) == 1:
-        print "must have argument"
+    if len(sys.argv) != 3:
+        print "must have arguments of form [clean load file] [model name]"
         quit()
-    elif len(sys.argv) == 2:
-        loadFile = sys.argv[1]
-        loadFileClean = None
-    elif len(sys.argv) == 3:
-        loadFile = sys.argv[1]
-        loadFileClean = sys.argv[2]
-    else:
[…]

### 2015-01-12 AltruisticLanguage/ContentModel/ForwardAlg.py

@@ -55,7 +55,7 @@ def loadContentClusters(folder):
     clusters.'''
     returnDict = {}
     for i in os.listdir(folder):
-        if i.endswith(".lm"):
+        if i.endswith(".lm") and i.split(".")[0] != '-1':
             with open(folder + "/" + i) as f:
                 returnDict[int(i.split(".")[0])] = pickle.load(f)
         else:

### 2015-01-12 AltruisticLanguage/ContentModel/LanguageModel.py

@@ -25,9 +25,9 @@ class LanguageModel:
         pass
 
 class ETCBigramModel(LanguageModel):
-    def __init__(self):
-        '''Argumentless version for classification purposes.'''
-        pass
+    #def __init__(self):
+    #    '''Argumentless version for classification purposes.'''
+    #    pass
     def setParams(self, parameters):
         '''Here, we expect parameters in the form ([otherLM1, otherLM2, ...]) where
         the other LMs are REQUIRED to have the function bigramProb(bigram)'''

### 2015-01-12 AltruisticLanguage/ContentModel/cleanCompress.py

@@ -1,0 +1,25 @@
+import sys
+import cPickle as pickle
+
+def main():
+    toCombine = sys.argv[1:-1]
+    out = sys.argv[-1]
+    sents = []
+    for c in toCombine:
+        with open(c) as f:
+            sents.append(pickle.load(f))
+    curId = sents[0][1]
+    writeId = 0
+    finalSents = []
+    for s in sents:
+        for i in s:
+            newId = i[1]
+            if newId != curId:
+                writeId += 1
+                curId = newId
+            finalSents.append((i[0], writeId))
+    with open(out, 'w') as f:
+        pickle.dump(finalSents, f, -1)
+        
+if __name__ == "__main__":
+    main()

### 2015-01-12 AltruisticLanguage/EDA.py
more updates

@@ -413,7 +413,7 @@ def getValidGrams(projects, minOccur = 50, nGram = 3):
 
     return validGrams
 
-def extractTextFeatures(projects, minOccur = 10, nGram = 2, counts=False):
+def extractTextFeatures(projects, minOccur = 5, nGram = 2, counts=False):
     '''Given a list of projects, a minimum number of occurances, and maximum sized n-gram of interest, return a |projects| x |features| n-gram count matrix and list of n-grams in the order represented, given that the selected features appear in a least minOccur projects and at least once in every category. If counts = True, then the return matrix has counts features, if counts=False, then the return matrix has binary indicators'''
     #dict mapping from category -> set of n grams in that category
     catGramDict = defaultdict(set)
@@ -434,11 +434,11 @@ def extractTextFeatures(projects, minOccur = 10, nGram = 2, counts=False):
         print "Extracting " + str(n) + "-grams"
         for p in projects:
             nGrams = myGramFun(p.text, n)
-            for r in p.rewards:
-                nGrams.extend(myGramFun(r.text,n))
-            for f in p.faqs:
-                nGrams.extend(myGramFun(f.question,n))
-                nGrams.extend(myGramFun(f.answer,n))
+            #for r in p.rewards:
+            #    nGrams.extend(myGramFun(r.text,n))
+            #for f in p.faqs:
+            #    nGrams.extend(myGramFun(f.question,n))
+            #    nGrams.extend(myGramFun(f.answer,n))
             for g in nGrams:
                 nGramCounter[g] += 1
                 gramCatCounter[p.category][g] += 1
@@ -646,8 +646,10 @@ def main():
     #minDate = min([p.startDate for p in projects])
     #maxDate = max([p.endDate for p in projects])
     
+    train = 400
+    test = 600
     catDict = buildCategoryDictionary(projects)
-    music = catDict["Music"]
+    music = catDict["Photography"]
     succ = [p for p in music if p.backers != 0
             and
             1.*(p.backers - sum([y.numBackers for y in 
@@ -656,15 +658,18 @@ def main():
             or
             1.*(p.backers - sum([y.numBackers for y in 
                                  p.rewards]))/(1.0*p.backers)<=.1 if len(p.text) > 0]
[…]

### 2015-01-12 AltruisticLanguage/languageOnly.R

@@ -9,6 +9,7 @@ rsort <- function(x) {
 }
 
 ###
+train <- 600
 data <- readMM("photoSmall.mtx")
 headers <- read.csv("photoSmall.csv")
 colnames(data) <- colnames(headers)
@@ -17,22 +18,22 @@ target <- target[,2]/target[,1]
 target[is.nan(target)] <- 0
 target <- target > .1
 setwd("ContentModel")
-posProbs <- t(read.csv("probA.csv", header=F))
-negProbs <- t(read.csv("probB.csv", header=F))
+posProbs <- t(read.csv("succ.csv", header=F))
+negProbs <- t(read.csv("fail.csv", header=F))
 setwd("..")
 colnames(posProbs) <- c("PosProb")
 colnames(negProbs) <- c("NegProb")
 data <- cBind(data, negProbs)
 data <- cBind(data, posProbs)
-trainData <- data[1:600, -which(colnames(data) %in% c("numBackers","numAltruistic", "Osuccess"))]
-trainData <- trainData[-which(posProbs==0),]
-trainTarget <- target[1:600]
-trainTarget <- trainTarget[-which(posProbs==0)]
+trainData <- data[1:train, -which(colnames(data) %in% c("numBackers","numAltruistic", "Osuccess"))]
+#trainData <- trainData[-which(posProbs==0),]
+trainTarget <- target[1:train]
+#trainTarget <- trainTarget[-which(posProbs==0)]
 ######
 control <- cv.glmnet(trainData[,c(-which(colnames(trainData) %in% c("PosProb", "NegProb")), -grep("^T", colnames(trainData)))],
                      trainTarget , family = "binomial", type.measure = "class", alpha = 0, parallel = F)
 
-holdoutNoCM <- cv.glmnet(trainData[,-which(colnames(trainData) %in% c("PosProb", "NegProb"))],
+holdoutNoCM <- cv.glmnet(trainData[,],#-which(colnames(trainData) %in% c("PosProb", "NegProb"))],
                         trainTarget , family = "binomial", type.measure = "class", alpha = 0, parallel = F)
 
 holdout <- cv.glmnet(trainData,
@@ -42,22 +43,40 @@ holdoutNoText <- cv.glmnet(trainData[,-grep("^T", colnames(trainData))],
                            trainTarget , family = "binomial", type.measure = "class", alpha = 0, parallel = F)
 ######
 predControl <- predict(control,
[…]

### 2015-01-14 AltruisticLanguage/regressionFinal.R
final regression script updated for non-content language features.

@@ -3,93 +3,62 @@ library('Matrix')
 library('glmnet')
 library('foreach')
 library('doParallel')
-library('AUC')
 registerDoParallel()
 rsort <- function(x) {
   sort(x, decreasing = TRUE)
 }
 setwd("regressionData")
-dataSW <- readMM("all90Filter.mtx")
-headersSW <- read.csv("allHeaders90Filter.csv")
-dataNoSW <- readMM("all90FilternoSW.mtx")
-headersNoSW <- read.csv("allHeaders90FilternoSW.csv")
-dataControl <- readMM("allControls.mtx")
-headersControl <- read.csv("allControlHeaders.csv")
+data <- readMM("all.mtx")
+headers <- read.csv("all.csv")
 setwd("..")
 
-colnames(dataSW) <- colnames(headersSW)
-colnames(dataNoSW) <- colnames(headersNoSW)
+colnames(data) <- colnames(headers)
 colnames(dataControl) <- colnames(headersControl)
 
-#dataControlTest2 <- dataControl[which(dataControl[,c("numBackers")]>=20),]
-#target2 <- dataControl[which(dataControl[,c("numBackers")]>=20),c("numBackers", "numAltruistic")]
-#target2 <- target2[,2]/target2[,1]
-
-target <- dataControl[,c("numBackers", "numAltruistic")]
+target <- data[,c("numBackers", "numAltruistic")]
 target <- target[,2]/target[,1]
 target[is.nan(target)] <- 0
 target <- target > .1
 
-control <- cv.glmnet(dataControl[,-which(colnames(dataControl) %in% c("numBackers","numAltruistic", "Osuccess"))], target,
+control <- cv.glmnet(data[,c(-grep("^T|^L", colnames(data)), -which(colnames(data) %in% c("numBackers","numAltruistic", "Osuccess")))], target,
               family = "binomial",
               type.measure = "class",
               alpha = 1, parallel = T)
 
-noSW <- cv.glmnet(dataNoSW[,-which(colnames(dataNoSW) %in% c("numBackers","numAltruistic", "Osuccess"))], target,
+langControl <- cv.glmnet(data[,c(-grep("^T", colnames(data)), -which(colnames(data) %in% c("numBackers","numAltruistic", "Osuccess")))], target,
+                         family = "binomial",
+                         type.measure = "class",
+                         alpha = 1, parallel = T)
+
[…]

### 2015-01-14 AltruisticLanguage/regressionFinal.R
final regression script updated for non-content language features.

@@ -57,7 +57,7 @@ predLangControl <- predict(holdoutLangControl,
                            type='class')
 
 predTotal <- predict(holdoutTotal,
-                     data[(train+1):nrow(data), -which(colnames(data) %in% c("numBackers","numAltruistic", "Osuccess")))],
+                     data[(train+1):nrow(data), -which(colnames(data) %in% c("numBackers","numAltruistic", "Osuccess"))],
                      type='class')
 
 topBottomK <- function(cvReg, k) {

### 2015-01-15 AltruisticLanguage/writing/paper.tex
updates:

@@
 The most popular of these sites, Kickstarter, provides a venue for entrepreneurs to connect with individuals who might be interested in financially supporting their project ideas, which range from artistic endeavours to technology startups.
-To date, over \$1.4B has been invested in Kickstarter projects from more than 7.4M unique backers resulting in over 73K successfully funded projects.
-\footnote{ \url{www.kickstarter.com/help/stats}} Each project is associated with a set of creator-defined rewards that donors can choose from.
+To date, over \$1.4B has been invested in Kickstarter projects from more than 7.4M unique backers resulting in over 73K successfully funded projects\footnote{ \url{www.kickstarter.com/help/stats}}.
+Each project is associated with a set of creator-defined rewards that donors can choose from.
 Often, these rewards constitute pre-orders of a product that the project aims to bring to market.
@@
 \scriptsize
-\begin{tabular}{|*{12}{c|}}  % repeats {c|} 18 times
+\begin{tabular}{|*{12}{c|}}
 \hline
@@
 \caption{Summary of Bayesian analysis of language comparing Kickstarter to GoFundMe and Amazon.
-Negative Z-scores correspond to Kickstarter.
+Negative Z-scores correspond to n-grams most strongly associated with Kickstarter.
 Top ten most significant n-grams are presented.
@@
 
-Furthermore, in our dataset consisting of 45K completed Kickstarter projects, we are able to quantify the number of purely altruistic donation events and the total value given above and beyond the amount required for all reward claims.
+Furthermore, in a dataset consisting of 45K completed Kickstarter projects, we are able to quantify the number of purely altruistic donation events and the total value given above and beyond the amount required for all reward claims.
 Of the roughly 3.4M donation events, about 360K (10.59\%) resulted from users who willingly opted to receive no reward.
-Of the roughly \$246M pledged in our dataset, over \$53M (21.59\%) was given altruistically.
+Of the roughly \$246M pledged in the dataset, over \$53M (21.59\%) was given altruistically.
 
 The community and language of Kickstarter have been studied previously.
-Mitra and Gilbert analyze the language that predicts successful Kickstarter projects \cite{mitra2014language}.
-When compared their baseline regression trained on a set of language-independent set of project features, their final classifier, which includes binary n-gram indicator variables, is able to classify projects 15\% more accurately, resulting in a 97.8\% correct prediction rate in a 10-fold cross validation setting.
+Mitra and Gilbert (2014) analyze the language that predicts successful Kickstarter projects.
+When compared to their baseline regression trained on a set of language-independent project features, their final classifier, which includes binary n-gram indicator variables, is able to classify projects 15\% more accurately, resulting in a 97.8\% correct prediction rate in a 10-fold cross validation setting.
 Similar analyses that do not take language fully into account are not able to achieve such predictive accuracy.
@@
 Even using post-launch information, however, does not improve accuracy as much as accounting for language; 85\% accuracy is achieved using information available after 15\% of the duration of the campaign has expired \cite{etter2013launch}.
+
 Furthermore, linguistic factors have been shown to effect the quality and time-to-response of questions posed in an online community \cite{teevan2011factors}.
-These findings suggest that language is very important on Kickstarter and, more generally, in online communities as a whole, which is a primary motivation for making it a focus of our analysis.
+Viewing the time taken to craft a quality response as an altruistic behavior, these findings suggest that language is very important in online communities where altruistic requests are being issued.
+These aresults are a primary motivation for making it a focus of our analysis.
 
@@
 Althoff et al.
-examine a purely altruistic community wherein users request and provide free pizza to and from other community members \cite{althoff2014ask}.
-An advantage of their dataset is that all their request are purely altruistic, and are made for the same service, though the total donation value of their dataset is lower than that presented here.
+(2014) examine a purely altruistic community wherein users request and provide free pizza to and from other community members.
+An advantage of their dataset is that all their requests are purely altruistic and are made for the same service, though the total donation value of their dataset is lower than that presented here.
 Previous work on Kickstarter has also demonstrated that users are more likely to donate to campaigns as time is winding down and the project has not yet met its goal, which is an arguably altruistic behavior \cite{kuppuswamy2013crowdfunding}.

### 2015-01-15 AltruisticLanguage/EDA.py

@@ -413,7 +413,7 @@ def getValidGrams(projects, minOccur = 50, nGram = 3):
 
     return validGrams
 
-def extractTextFeatures(projects, minOccur = 5, nGram = 2, counts=False):
+def extractTextFeatures(projects, minOccur = 10, nGram = 3, counts=False):
     '''Given a list of projects, a minimum number of occurances, and maximum sized n-gram of interest, return a |projects| x |features| n-gram count matrix and list of n-grams in the order represented, given that the selected features appear in a least minOccur projects and at least once in every category. If counts = True, then the return matrix has counts features, if counts=False, then the return matrix has binary indicators'''
     #dict mapping from category -> set of n grams in that category
     catGramDict = defaultdict(set)
@@ -434,11 +434,11 @@ def extractTextFeatures(projects, minOccur = 5, nGram = 2, counts=False):
         print "Extracting " + str(n) + "-grams"
         for p in projects:
             nGrams = myGramFun(p.text, n)
-            #for r in p.rewards:
-            #    nGrams.extend(myGramFun(r.text,n))
-            #for f in p.faqs:
-            #    nGrams.extend(myGramFun(f.question,n))
-            #    nGrams.extend(myGramFun(f.answer,n))
+            for r in p.rewards:
+                nGrams.extend(myGramFun(r.text,n))
+            for f in p.faqs:
+                nGrams.extend(myGramFun(f.question,n))
+                nGrams.extend(myGramFun(f.answer,n))
             for g in nGrams:
                 nGramCounter[g] += 1
                 gramCatCounter[p.category][g] += 1
@@ -459,8 +459,8 @@ def extractTextFeatures(projects, minOccur = 5, nGram = 2, counts=False):
         for cat, catCount in catCounter.iteritems():
             perDocList.append((gramCatCounter[cat][v]*.1)/catCount)
         gramToVar[v] = 1.0*(np.max(perDocList)-np.min(perDocList))/np.max(perDocList)
-    #validGrams = [x[0] for x in
-    #              sorted(gramToVar.items(), key = operator.itemgetter(1))[:int(.9*len(gramToVar))]]
+    validGrams = [x[0] for x in
+                  sorted(gramToVar.items(), key = operator.itemgetter(1))[:int(.9*len(gramToVar))]]
 
     
     print "Using {} n-grams".format(len(validGrams))
@@ -512,7 +512,6 @@ def extractGivenTextFeatures(projects, inFile, counts=False):
                     else:
[…]

### 2015-01-15 AltruisticLanguage/regressionFinal.R

@@ -35,6 +35,8 @@ total <- cv.glmnet(data[,-which(colnames(data) %in% c("numBackers","numAltruisti
                 type.measure = "class",
                 alpha = 1, parallel = T)
 
+
+######
 train <- 40000
 
 holdoutControl <- cv.glmnet(data[1:train,c(-grep("^T|^L", colnames(data)), -which(colnames(data) %in% c("numBackers","numAltruistic", "Osuccess")))],
@@ -43,7 +45,7 @@ holdoutControl <- cv.glmnet(data[1:train,c(-grep("^T|^L", colnames(data)), -whic
 holdoutLangControl <- cv.glmnet(data[1:train,c(-grep("^T", colnames(data)), -which(colnames(data) %in% c("numBackers","numAltruistic", "Osuccess")))],
                         target[1:train], family = "binomial", type.measure = "class", alpha = 1, parallel = T)
 
-holdoutTotal <- cv.glmnet(dataControl[1:train,-which(colnames(data) %in% c("numBackers","numAltruistic", "Osuccess"))],
+holdoutTotal <- cv.glmnet(data[1:train,-which(colnames(data) %in% c("numBackers","numAltruistic", "Osuccess"))],
                               target[1:train], family = "binomial", type.measure = "class", alpha = 1, parallel = T)
 
 
@@ -82,7 +84,7 @@ checkModel <- function(pred) {
   perc <- posCor/(posCor + negFail)
   rec <- posCor/(posCor + posFail)
   f <- 2 * perc * rec / (perc + rec)
-  print("Percision")
+  print("Precision")
   print(perc)
   print("Recall")
   print(rec)
@@ -102,10 +104,8 @@ orderedCoefs <- function(cvReg) {
 
 checkModel(predControl)
 checkModel(predLangControl)
+checkModel(predTotal)
 
 topK <- 50
-topBottomK(control, topK)
-topBottomK(langControl, topK)
-topBottomK(SW, topK)
-topBottomK(test2, topK)
-write.table(orderedCoefs(SW), file = "testFile.csv")
+topBottomK(total, topK)
+write.table(orderedCoefs(total), file = "orderedCoefs")

### 2015-01-15 AltruisticLanguage/writing/paper.tex
did lots of writing updates

@@
  \begin{document}
-% The file aaai.sty is the style file for AAAI Press 
-% proceedings, working notes, and technical reports.
-%
 \title{Pre-orders or Philanthropy: An Analysis of Altruism on Kickstarter and Other Crowdfunding Sites}
@@
 
+Furthermore, in a dataset consisting of 45K completed Kickstarter projects, we are able to quantify the number of purely altruistic donation events and the total value given above and beyond the amount required for all reward claims.
+Of the roughly 3.4M donation events, about 360K (10.59\%) resulted from users who willingly opted to receive no reward.
+Of the roughly \$246M pledged in the dataset, over \$53M (21.59\%) was given altruistically.
+
+The community and language of Kickstarter have been studied previously.
+Mitra and Gilbert (2014) analyze the language that predicts successful Kickstarter projects.
+When compared to their baseline regression trained on a set of language-independent project features, their final classifier, which includes binary n-gram indicator variables, is able to classify projects 15\% more accurately, resulting in a 97.8\% correct prediction rate in a 10-fold cross validation setting.
+Similar analyses that do not take language fully into account are not able to achieve such predictive accuracy.
+Studies that attempt to predict project success that use only minimal textual information fail to produce similarly accurate classifiers.
+Though it is difficult to compare accuracies directly because exact datasets differ from study-to-study, we note that Greenberg et al.
+\shortcite{greenberg2013crowdfunding} learn classifiers that reach 68\% accuracy using information available at launch time, utilizing minimal textual information in conjunction with baseline project features.
+
+Utilizing non-linguistic post-launch information seems to, in general, not improve accuracy as much as accounting for language.
+Etter et al.
+\shortcite{etter2013launch}, for instance, achieve 85\% accuracy using non-linguistic information available after 15\% of the duration of the campaign has expired.
+On the other hand, Xu et al.
+\shortcite{Xu:2014:SMM:2556288.2557045} demonstrate that ``specific uses'' of post-launch linguistic information in the form of project ``updates'' often ``had stronger associations with campaign success than the project's description.''
+
+The altruistic and non-altruistic motivations of crowdfunders have also been addressed in previous work.
+Lin et al.
+\shortcite{Lin+Boh+Goh:14a} examine the diverse motivations of crowdfunders, deriving several archetypical user types on Kickstarter including an ``Altruistic'' type.
+Their study, which doesn't address language directly, identifies a group of users not motivated by project rewards.
+Previous work on Kickstarter has also demonstrated that users are more likely to donate to campaigns as time is winding down and the project has not yet met its goal, which is an arguably altruistic behavior \cite{kuppuswamy2013crowdfunding}.
+Wash \shortcite{wash2013value} finds that donations on DonorsChoose.org that complete projects tend to be significantly larger than average donations, and speculates that, as projects near completion, existing donors ``might start to see the project goal as an individual goal [rather than a group goal]'' and feel compelled to increase the amount of their contribution.
+Other studies have also sugguested that users crowdfund for a variety of non-altruistic reasons as well, such as expanding one's social network\cite{Gerber:2013:CMD:2562181.2530540}.
+As noted by Kuppuswamy and Bayues \shortcite{kuppuswamy2013crowdfunding}, however, many users `` believe that [Kickstarter] is essentially an online retail storefront in which project creators are pre-selling products,'' so motivations are not always extrinsic and complex.
+
+Outside of crowdfunding, lingustic content in online communities has been shown to be central to eliciting altruistic behavior.
+Althoff et al.
+\shortcite{althoff2014ask} examine the language of a purely altruistic community wherein users request and provide free pizza to and from other community members.
+An advantage of their dataset is that all their requests are purely altruistic and are made for the same service, though the total donation value of their dataset is lower than that presented here.
+Furthermore, linguistic factors have been shown to effect the quality and time-to-response of questions posed in an online community \cite{teevan2011factors}.
+Viewing the time taken to craft a quality response as an altruistic behavior, these findings suggest that language is very important in online communities where altruistic requests are being issued.
+Herzenstein et al.
+\shortcite{herzenstein1775tell} examine how the claimed identity of a requester impacts whether or not a loan is issued on the peer-to-peer lending service Prosper.com.
+Their findings demonstrate the ``power of constructing a viable narrative when attempting to influence a decision maker.'' Finally, Galak et al.
+\shortcite{galak2011microfinance} utilize Amazon's Mechanical Turk to derive a set of ``subjective'' features (e.g.
+``Likely to pay back loan'') based on project descriptions on the Kiva.org microfinancing platform, and find a variety of cases where these features act as significant predictors of micro-loaning behavior.
+
+These observations and previous work motivate our research questions: how does the language used on Kickstarter differ from the language used in a purely commercial setting?
+Or a purely altruistic setting?
+What types of Kickstarter projects are donated to altruistically?
+Does the language of a project description predict the donation behavior of backers?
+\section{Primary Dataset}
+Our dataset consists of 45810 completed Kickstarter projects, the URLs of which were originally collected by AppsBlogger.com.
+The projects in the dataset were all active between April 2009, the earliest start date, and August 2012, the latest end date.
+Every Kickstarter project has an associated HTML page, which we parse using the popular HTML parsing library Beautiful Soup 4\footnote{\url{http://www.crummy.com/software/BeautifulSoup/}}.
+Each project's page contains information about the project such as its title, its description, the rewards (with associated cost, number of backers who have claimed that reward, and a description), the FAQ section, the total number of backers, and the total amount of money raised.
+This information served as the basis of our analysis.
+
+Kickstarter projects are also associated with a single category.
+The category of a Kickstarter project is used by the site to index campaigns and to help users find projects of a specific type.
+While some of these categories are ``main'' categories (13/49) most are ``subcategories'' that have a corresponding main category.
+In most cases, we treat all categories as equivalent, irrespective of whether or not it is a sub or a main.
+
+In all of our analyses that use text data, we preprocess by removing punctuation from strings and converting all characters to lower case, though we do not discard stop words.
+In general, we are interested in unigrams, bigrams, and trigrams, and tokenize after these preprocessing steps.
+
+\section{Kickstarter vs. GoFundMe and Amazon}
 \begin{table*}[t]
@@
 Top ten most significant n-grams are presented.
-A full list of n-grams and z-scores is provided.\footnote{PUT LINK HERE}}
+A full list of n-grams and z-scores is provided.\footnotemark}
 \label{tab:pairwise}
 \end{table*}
-
-Furthermore, in a dataset consisting of 45K completed Kickstarter projects, we are able to quantify the number of purely altruistic donation events and the total value given above and beyond the amount required for all reward claims.
-Of the roughly 3.4M donation events, about 360K (10.59\%) resulted from users who willingly opted to receive no reward.
-Of the roughly \$246M pledged in the dataset, over \$53M (21.59\%) was given altruistically.
-
-The community and language of Kickstarter have been studied previously.
-Mitra and Gilbert (2014) analyze the language that predicts successful Kickstarter projects.
-When compared to their baseline regression trained on a set of language-independent project features, their final classifier, which includes binary n-gram indicator variables, is able to classify projects 15\% more accurately, resulting in a 97.8\% correct prediction rate in a 10-fold cross validation setting.
-Similar analyses that do not take language fully into account are not able to achieve such predictive accuracy.
-Studies that use of minimal textual information in conjunction with baseline project features are able to learn classifiers that reach 68\% accuracy using information available at launch time \cite{greenberg2013crowdfunding}.
-Even using post-launch information, however, does not improve accuracy as much as accounting for language; 85\% accuracy is achieved using information available after 15\% of the duration of the campaign has expired \cite{etter2013launch}.
-
-Furthermore, linguistic factors have been shown to effect the quality and time-to-response of questions posed in an online community \cite{teevan2011factors}.
-Viewing the time taken to craft a quality response as an altruistic behavior, these findings suggest that language is very important in online communities where altruistic requests are being issued.
-These aresults are a primary motivation for making it a focus of our analysis.
-
-Altruism in online communities has also been previously studied.
-Althoff et al.
-(2014) examine a purely altruistic community wherein users request and provide free pizza to and from other community members.
-An advantage of their dataset is that all their requests are purely altruistic and are made for the same service, though the total donation value of their dataset is lower than that presented here.
-Previous work on Kickstarter has also demonstrated that users are more likely to donate to campaigns as time is winding down and the project has not yet met its goal, which is an arguably altruistic behavior \cite{kuppuswamy2013crowdfunding}.
-
-These observations and previous work motivate our research questions: how does the language used on Kickstarter differ from the language used in a purely commercial setting?
-Or a purely altruistic setting?
-What types of Kickstarter projects are donated to altruistically?
-Does the language of a project description predict the donation behavior of backers?
-
-\section{Primary Dataset}
-Our dataset consists of 45810 completed Kickstarter projects, the URLs of which were originally collected by AppsBlogger.com.
-The projects in our data were all active between April 2009, the earliest start date, and August 2012, the latest end date.
-Every Kickstarter project has an associated HTML page, which we parse using the popular HTML parsing library Beautiful Soup 4\footnote{\url{http://www.crummy.com/software/BeautifulSoup/}}.
-Each project's page contains information about the project such as its title, its description, the rewards (with associated cost, number of backers who have claimed that reward, and a description), the FAQ section, the total number of backers, and the total amount of money raised.
-This information served as the basis of our analysis.
-
-Kickstarter projects are also associated with a single category.
-The category of a Kickstarter project is used by the site to index campaigns and to help users find projects of a specific type.
-While some of these categories are ``main'' categories (13/49) most are ``subcategories'' that have a corresponding main category.
-In most cases, we treat all categories as equivalent, irrespective of whether or not it is a sub or a main.
-
-In all of our analyses that use text data, we preprocess by removing punctuation from strings and converting all characters to lower case, though we do not discard stop words.
-In general, we are interested in unigrams, bigrams, and trigrams, and tokenize after these preprocessing steps.
-
-\section{Kickstarter vs. GoFundMe and Amazon}
 What language used on Kickstarter is altruistic?
 What language used on Kickstarter is commercial?
-To address these questions, it might be possible to derive stringent definitions of altruism and salespersonship.
-However, for our analysis, we resort to a more objective analysis by incorporating two additional data sets, one from Amazon and one from GoFundMe.
+To address these questions, it might be possible to derive first-principles definitions of altruism and salespersonship.
+However, for our analysis, we resort to a data-driven analysis by incorporating two additional data sets, one from Amazon and one from GoFundMe.
 
@@
 Our dataset consists of 7.7K GoFundMe project descriptions scraped in November 2014.
-In contrast to Kickstarter, in a vast majority of cases GoFundMe contributors don't have the option to select compensatory rewards, and we therefore regard our GoFundMe data as requests for purely altruistic actions.
+In contrast to Kickstarter, in a vast majority of cases GoFundMe contributors don't have the option to select compensatory rewards, and we therefore regard our GoFundMe data as exemplars of requests for purely altruistic actions.
 
@@
 To apply a more stringent topic controlling filter, after removing n-grams that don't appear in all categories, for each n-gram $n$, we compute the intra-category document frequency denoted $f_n^c$ for all categories $c$ where $f^n_c$ is the average number of times $n$ appears in documents within category $c$.
-We then compute the ``normalized width'' $w_n$ for n-gram $n$ as...
-
+We then compute the ``cross-category variation'' (CCV) $w_n$ for n-gram $n$ as...
 \begin{equation} \label{eq:width}
@@
 \end{equation}
-
-The intuition behind normalized width is as follows -- if a word appears in all categories with roughly the same frequency, the normalized width will be small.
-If a word appears very frequently in a single category, the normalized width will be large.
-After computing this statistic for all n-grams, we discard the 10\% of n-grams with highest normalized width.
+The intuition behind CCV is as follows -- if a word appears in all categories with roughly the same frequency, the CCV will be small.
+If a word appears very frequently in a single category, the CCV will be large.
+After computing this statistic for all n-grams, we discard the 10\% of n-grams with highest CCV.
 This two-part filtration scheme is applied to all three datasets, and to derive our final vocabulary we take a 3-way intersection of the resulting topic-controlled features from Kickstarter, Amazon, and GoFundMe.
@@
 Project curators in the more altruistic setting are clearly more focused on personal appeals when compared to Kickstarter.
+
+%FOOTNOTE FOR FIGURE CAPTION
+\footnotetext{Put Link Here.}
 
@@
 
-To analyze the sequential structure of altruistic requests in a crowdfunding setting, we run a case study on a subset of data utilizing a content model \cite{barzilay2004catching} to produce a sentence clustering.
+To analyze the sequential structure of altruistic requests in a crowdfunding setting, we run a case study on a subset of data utilizing a content model \cite{barzilay2004catching} to produce a document structure-aware sentence clustering.
 A content model is an unsupervised learning algorithm that operates on the sentence level, takes information order into account, and learns transition probabilities between sentence types.
-Here we provide a brief overview of the content model algorithm; for a fuller description, consult the original paper.
+Here we provide a brief overview of the algorithm and train an interpretable content model on a subset of our GoFundMe data in order to motivate our use of this approach on a later Kickstarter prediction task.
 
 The goal of a content model is to learn a set of sentence clusters utilizing ordering information.
-Given a set of $N$ documents where document $n$ has $s_n$ sentences, sentences are first clustered into $k$ groups according to bigram features using complete-link clustering with a cosine distance metric.
+Given a set of $N$ documents where document $d$ has $s_d$ sentences, sentences are first clustered into $k$ groups according to bigram features using complete-link clustering with a cosine distance metric.
 After sentences are clustered into these groups, we merge all clusters smaller than some threshold into an ``etcetera'' cluster.
-This etcetera cluster is a unique feature of the content model that allows it the flexibility to assign sentences that otherwise don't fit into an ``other'' cluster.
-After this merging process, we are left with $m$ clusters.
-
 For each of the resulting non-etcetera clusters, we train a smoothed bigram language model which is able to assign probabilities to input sentences.
 For the etcetera cluster, we train a ``complementary'' language model which assigns high probability to sentences that all other language models assign low probability to.
+After training these language models, we now treat each cluster as a state in a Hidden Markov Model, and all input documents as emissions from that Hidden Markov Model.
+We compute the Viterbi path for each document, and re-cluster sentences based on these most-likely paths.
+This path-based reclustering/language-model retraining is repeated in an expectation maximization-like fashion until convergence.
 
-After training these language models, we now treat each clustering as a state in a Hidden Markov Model, and all input documents as emissions from that Hidden Markov Model.
-We are able to compute the Viterbi path for each document, and we re-cluster sentences based on these most-likely paths.
-Finally, we retrain each of the language models based on the new clustering.
-This process of re-clustering, computing Viterbi paths, and re-training language models in an expectation
-maximization-like fashion is executed until convergence or a maximum number of iterations is made.
-
-In accordance with the recommendations of the original authors, we attempt to map all named entities to a ``NAME'' token and all numbers to a ``NUM'' token.
-We use the default NLTK\footnote{\url{http://www.nltk.org/}} named entity recognizer to identify tokens to be mapped to ``NAME,'' and we map any token that parses to a float without error to ``NUM.''
+In accordance with the recommendations of the original authors, we map all named entities to a ``NAME'' token and all numbers to a ``NUM'' token.
+We use the default NLTK\footnote{\url{http://www.nltk.org/}} named entity recognizer to identify tokens to be mapped to ``NAME,'' and we map any token that parses to a float without error to ``NUM''\footnote{In our later Kickstarter content model experiment, we also map URLs, though such a mapping wasn't deemed necessary here.}.
 
@@
 
-For the remainder of this analysis, we are going to focus on the cluster containing 254 sentences (dubbed the ``Thank you'' cluster) and the cluster containing 272 sentences (dubbed the ``Introduction'' cluster).
+For the remainder of this analysis, we focus on the cluster containing 254 sentences (dubbed the ``Thank you'' cluster) and the cluster containing 272 sentences (dubbed the ``Introduction'' cluster).
 Though there are many interesting things that can be learned from the transition probabilities output by the content model, the most interpretable fact is illustrated in Figure \ref{fig:docpos}.
@@
 \begin{equation} \label{eq:sentpos}
-\sum\limits_{k \in \text{Occurrences of $c$}} \frac{\text{Position of $k$ in containing sentence}}{\text{Length of sentence containing $k$}}
+\sum\limits_{k \in \text{Occurrences of\\sentences in $c$}} \frac{\text{Position of $k$ in containing sentence}}{\text{Length of sentence containing $k$}}
 \end{equation}
@@
 We later use more complex content models for an order-aware classification task on Kickstarter.
-
 \section{Prediction of Altruism on Kickstarter}
@@
 
-In a similar vein to \cite{mitra2014language} we define a binary altruistic response variable and train several logistic regression classifiers to predict that variable.
+In a similar vein to Mitra and Gilbert \shortcite{mitra2014language} we define a binary altruistic response variable and train several logistic regression classifiers to predict that variable.
 The response variable is defined as follows: if a project receives any donations and the proportion of altruistic donations it receives exceeds $10\%$, we assign it to the altruistic group, otherwise, it is assigned to the non-altruistic group.
@@
 Out first regression task consists of a controls-only baseline.
-The set of control variables, which mostly mirrors Mitra and Gilbert's control set, consists of 49 binary variables, one for each Kickstarter project category (``Theater,'' ``Indie Rock,'' ``Open Software,'' etc.) and an additional 10 variables summarized in Table \ref{tab:controls}.
+The set of control variables, which mostly\footnote{We exclude a variable they didn't find significant having to do with video duration.} mirrors Mitra and Gilbert's control set, consists of 49 binary variables, one for each Kickstarter project category (``Theater,'' ``Indie Rock,'' ``Open Software,'' etc.) and an additional 10 variables summarized in Table \ref{tab:controls}.
 
@@
 Our textual features consist of binary indicator variables for unigrams, bigrams, and trigrams in the project descriptions, FAQ question/answers, and reward descriptions of our Kickstarter projects.
-We apply the same two-part normalized width filter that we use in our previous analysis to determine a set of topic-free n-grams, which forces selected n-grams to appear in every Kickstarter category and be relatively uniformly distributed between them (see Equation \ref{eq:width}).
+We apply the same two-part CCV filter that we use in our previous analysis to determine a set of topic-free n-grams, which forces selected n-grams to appear in every Kickstarter category and be relatively uniformly distributed between them (see Equation \ref{eq:width}).
 Applying this two-part filtration process on our Kickstarter dataset exclusively, we end up with 31281 filtered n-grams.
@@
 There are also some interesting patterns in the negatively-predicting n-grams.
-For instance, self-describing, rather than product describing, language appears to be a consistently negative predictor of altruistic donation.
+For instance, self-referential, rather than product describing, language appears to be a consistently negative predictor of altruistic donation.
 Common usage of linguistic features like ``people that are,'' ``we going,'' ``so we know,'' and ``my website at'' demonstrate this phenomenon.
@@
 \end{blockquote}
-Furthermore, it seems that linguistic features that make commands of backers (``get in on,'' ``must make'') are negative predictors of donations.
+Furthermore, it seems that linguistic features that using imparitive language (``get in on,'' ``must make'') is negatively associated with donations.
 \begin{blockquote}
@@
 For categories with large numbers of projects, this result is often highly significant.
-For instance, in the two most popular Kickstarter categories, ``Music'' and ``Film and Video,'' we observe a that failed projects receive, on average, significantly more altruistic donation events (Student's t-test, $p<<.001$ in both cases).
+For instance, in the two most popular Kickstarter categories, ``Music'' and ``Film and Video,'' we observe a that failed projects receive, on average, significantly more altruistic donation events (Student's t-test, $p\ll.001$ in both cases).
 Sample plots of the event distributions are presented in the first row of Figure \ref{fig:failsucc}.
@@
 When we change the focus of our analysis from events to dollar values, however, this pattern becomes less apparent, or reverses altogether.
-In the ``Film and Video'' category, for instance, we observe a total reversal, a significant result ($p << .001$) that states successful projects receive more dollars altruistically than failed projects.
+In the ``Film and Video'' category, for instance, we observe a total reversal, a significant result ($p \ll .001$) that states successful projects receive more dollars altruistically than failed projects.
 In fact, over all categories all statistically significant results state that successful projects receive more funding.
@@
 We believe that this result suggests the following scenario is common across many categories: a Kickstarter user observes that a project is failing and makes a small donation, but requests no reward.
-It has been shown that feelings of sympathy can elicit prosocial behavior, even if the interaction can be easily avoided, as it would be by anonymously closing a browser window \cite{eisenberg1989relation}.
+It has been shown that feelings of sympathy can elicit prosocial behavior, even if the interaction can be easily avoided \cite{eisenberg1989relation} as it would be by anonymously closing a browser window.
 If the cost of such an altruistic action is too high, however, it has a lower probability of being taken \cite{batson1983influence}.
-Though an assignment of altruistic donations to values directly would be valuable to our analysis, given the data that Kickstarter makes public, there is no way to directly compute the value of the altruistic donation events themselves, and we leave a more detailed analysis to future work on a separate dataset.
+Though an assignment of altruistic donations to values directly would be valuable to our analysis, given the data that Kickstarter makes public, it would be very difficult to directly compute the value/timing of the altruistic donation events themselves, and we leave a more detailed analysis to future work on a separate dataset.
 
@@
 Are there community-derived benefits to making altruistic donations on Kickstarter?
-These specific questions would be best answered by Kickstarter users themselves; interesting future work might include questionnaires sent out to a specifically targeted subset of users.
+These specific questions might be best answered by Kickstarter users themselves; interesting future work might include questionnaires sent out to a specifically targeted subset of users.
 
